To give you some ideas about what to take out of the library, here are some recommendations from the committee members of books to borrow. 

\par\vspace{-1em}
\parbox{0.4\textwidth}{
\begin{tabbing}
Amelia Owens\\ \quad\=\quad \textbf{A Natural History of Dragons} by Marie Brennan\\ \quad\=\quad \textit{Pseudo-Victorian lady's memoir of dragon study.}\\[1ex]
Matthew Legg\\ \>\quad \textbf{The Hitchhiker's Guide to the Galaxy} by Douglas Adams\\ \quad\=\quad \textit{Don't panic, and remember your towel.}\\[1ex]
Eliza Karlowska\\ \>\quad \textbf{Mistborn} by Brandon Sanderson\\ \quad\=\quad \textit{Thieves topple God-Emperor via metal magic.}\\[1ex]
Henry Wild \\ \>\quad \textbf{Lies of Locke Lamora} by Scott Lynch\\ \quad\=\quad \textit{Con-artist crew working in fantasy Venice.}\\[1ex]
Edward Da Fonseca\\ \>\quad \textbf{The Star Fraction} by Ken MacLeod\\ \quad\=\quad \textit{Sci-fi revolution, political humour, privatised nukes.}\\[1ex]
Kai Lawrence\\ \>\quad \textbf{Prince of Thorns} by Mark Lawrence\\ \quad\=\quad \textit{Brutal fantasy, definition of an antihero.}\\[1ex]
Connor Winzar\\ \>\quad \textbf{Bioshock: Rapture} by John Shirley\\ \quad\=\quad \textit{The Ozymandias of the Ocean Floor.}\\[1ex]
Tim Davison\\ \>\quad \textbf{Tales of Known Space} by Larry Niven\\ \quad\=\quad \textit{Humanity's future: a short story collection.}\\[1ex]
Katherine Read\\ \>\quad \textbf{Ready Player One} by Ernest Cline\\ \quad\=\quad \textit{Virtual 80s themed Easter egg hunt.}\\
\end{tabbing}
}
