Hello everyone,

To all the freshers, congratulations on making it to Imperial and welcome to ICSF. To everyone else, congratulations on making it back!

I hope you all had a wonderful summer and are feeling refreshed and ready for an action-packed year of lectures, labs and other things you may wish to hide from occasionally. The good news is, the library exists, with a bunch of fun (at least, we think so) people there watching something, having daft discussions and generally whiling away time until we have to face the real world again. Newcomers are always welcome!

Obviously, a library wouldn't be a library without also having some books. In fact, we have over 9000 of them (!), along with about 2000 DVDs and a fair few comics, graphic novels and audio books. All these are available for our members to take out, and if an item you want is somehow not already included in our ridiculously large collection, you can always request it. Good luck trying to consume it all in your time here.

We're also an active social society with a whole variety of events over the course of the year. These include regular cinema trips and bar nights (popular with both drinkers and those less alcoholically inclined). Highlights of the year include a Halloween night with singing, costumes and pizza, a Christmas event with Christmassy singing, Christmassy costumes and Christmassy pizza, and a residential trip to Hay-on-Wye, the town with the highest ratio of bookshops to people. To top it all off, we also hold our very own convention, Picocon (yes you read that right, an actual real convention, with actual real guests whose names you will probably know).

So read on, learn more about the society and come and meet us all in person in the library... Live long and prosper!