\vspace{1mm} 

As you may have gathered by now, the sci-fi society runs loads of fun events over the year, involving everything from movie marathons to Cthulhu carols. We already have lots of exciting events planned for the first few weeks, which you can find out more about on the timetable on the next page. The fun continues over the year, so be sure to subscribe to the mailing list to stay updated. 

\vspace{2mm} {\Large Lunchtime Showings}

From 12 to 2pm nearly every weekday, you will find the library full of people watching the various TV shows and movies that ICSF has to offer. For the first couple of weeks of term, we'll be showing some of our favourite picks to give you an idea of the genre, but after that the selection is open to all.

\vspace{2mm} {\Large Literary Lucky Dip}

Did someone say free books? Yes, we did! But there's a catch - the books will be wrapped up with only a few words on the front to describe what's inside.

\vspace{2mm} {\Large Bar Nights}

Bar nights are a great opportunity to meet up over a few drinks (alcoholic or otherwise) and discuss science fiction, fantasy, or whatever else catches your interest!

\vspace{2mm} {\Large Book Crawl}

Where some societies have pub crawls, ICSF has book crawls! We'll be travelling around the best book and comic stores in London to find out what they have to offer.

\vspace{2mm} {\Large Halloween}

On Friday 27th October we will be having an all-singing all-dancing party with showings of horror classics like The Rocky Horror Picture Show and Dr Horrible's Sing-Along Blog. Also to look forward to are plenty of snacks, pizza, and a fancy dress competition!

\vspace{2mm} {\Large Cinema Trips}

Outings to see genre films are arranged throughout the year. This term we hope to go and see \textbf{Lego Ninjago}, \textbf{Bladerunner} and \textbf{Thor Ragnarok}.

Arrangements for events will be circulated using the \url{icsf-list} mailing list.
