Hi there! I'm Henry, the Head Librarian here, and as such I'd like to warmly welcome you to ICSF's science fiction and fantasy library! 

You can find us open from 12 to 2 every weekday down in the West Basement of Beit Quad, however if you need more detailed instructions you can find them on the map in this Wyrmtongue. The library currently contains over 10,000 books, 2000 DVDs, and 600 graphic novels, with more being added to our collection every day; and you can borrow anything from our collection as soon as you buy membership with us! If, by some miracle, we don't have what you're looking for, you can simply write it down on the request list in the library or post your request on the library Facebook page, and we'll get it for you as soon as possible.

However, the library itself is not just a place to borrow and read/watch books and DVDs, it's also a unique social space on campus. It's almost always full of people relaxing while watching genre TV and having nerdy discussions about life, the universe, and everything. So should you fancy pretending your course and all your other responsibilities don't exist, you can count on the library being there for an episode or two (or three...) of your favourite show over lunch. It also often stays open late into the evening as well, so you can stay and unwind past 2pm or even try to `work' in it too. To see if the library's open and see what's on, check the webcam on the front page of our website.

Lastly, should you want recommendations on where to start, check out some of the committee's favourite books on the next page.

I hope to see you all around the library this coming year!