\vspace{2mm} {\Large Mailing Lists}

ICSF maintains two mailing lists, which all members are welcome to subscribe to.
Like all official Imperial mailing lists, they use mailman.
%
\textbf{icsf-list} is the society's core mailing list, which contains
announcements of ICSF events and important news about the society.
This list gets quite a low volume of traffic, and \textit{is a must if
you want to hear about film trips and other events.}
%
\textbf{icsf-committee} is our `management' list --- but it gets used a
lot more widely that that. Here you'll be able to contribute your opinion
to the running of the society.
%
You can manage your subscriptions at \url{mailman.imperial.ac.uk/mailman}.

\vspace{5mm}

{\Large Social Networks}

For those who welcome our social network overlords, we also have a Facebook
group, which is pretty much a continuation of the library into the
realms of cyber space --- \url{facebook.com/groups/ICSF.Imperial} (or search for
`Imperial College Science Fiction').

Our library Facebook page, `ICSF Library', has all the latest updates on new additions and recommendations, as well as book reviews by our resident librarian. It can be found at \url{facebook.com/icsflibrary}.

Finally, we have a Twitter account dedicated to our very own convention, Picocon. Check out and follow @Picocon for all the latest news and information about this year's event.

\vspace{5mm}

{\Large EGM}

This year, we will be holding an EGM on Thursday 19th October to elect a Chair of Vice. The Chair of Vice is the brains and organisation behind all of ICSF's events, so the role is a big responsibility! If you'd like to run, vote or just hang out and meet the committee, then come along to the library at 6pm.

\vspace{-10mm}