\vspace{1mm} 

Hi Everybody! I’m your Chair of Vice for the SciFi society this year, which means I have the pleasure of organising all the events for you. We have a few exciting things coming up for the first term so make sure you keep checking! You can find the timetable of the first few weeks somewhere in this Wyrmtongue.

Me? I’m an EEE student in my fourth year, and have just come back from an industrial placement in Guildford. I’ve been in the SciFi society since my second year and last year had the pleasure of being Picocon Beanbag. Which is another thing. Come to Picocon in February, it’s great! Hope to see you around!

\vspace{1mm} {\Large Lunchtime Showings}

Most lunctimes (12 - 2pm) you will find the library full of people watching various TV shows and movies. 

\vspace{1mm} {\Large ICSF Barnights}

Barnights are a great opportunity to meet and discuss everything SFF related, and many other things too! The first Barnight this term will be announced via the mailing list.

\vspace{1mm} {\Large Back to the Future}

Get out your hoverboards everyone! To celebrate the day Marty and Doc land in 2015 in Back to the Future 2, Wednesday October 21st, we're holding a Back to the Future Marathon!

Come along to the library where we'll be putting on all three films to celebrate. 

\vspace{1mm} {\Large Halloween}

On Friday 30th October (a day early!) we will be having an all-singing all-dancing party in the library with showings of horror classics such The Rocky Horror Show and Dr Horrible's Sing-Along Blog. Also to look forward to are costumes and a table in the bar!

\vspace{1mm} {\Large Cinema Trips}

Outings to see genre films are arranged throughout the year. This term we hope to go and see \textbf{The Martian} and \textbf{Star Wars: The Force Awakens}.

Arrangements for tickets will be circulated using the \url{icsf-list} mailing list.
