Our vendors are located on the second floor of the Blackett foyer, and and would love to introduce themselves to you.

{\Large Porcupine books }

I am Brian Ameringen who is also Porcupine Books, and have been a reader and collector of Science Fiction, Fantasy and Horror books for many years. I started Porcupine Books in 1998, and my aim is to supply you with the rare, curious and unusual books you want, at modest prices. I have  been selling books at Picocons for longer than I care to remember, but am intending to semi-retire in November this year, so this will be my last Picocon as a seller. Come and browse my books - and if you have questions, please ask! Hope you have a great Convention!

{\Large Paul Couper }

A reader/collector of SF/Fantasy, selling at Picocon to clear duplicates built up whilst collecting and upgrading.
My collection is now over 12,000 paperbacks, but still many gaps. Most wanted at present? Probably E Pluribus Unicorn, Theodore Sturgeon, Timescape paperback (i.e. 4th Pocket printing) to complete my timescape collection. So if anyone has a copy of that (or other collectables) for sale, wants to buy or, indeed just wants a chat, stop by during the day.

{\Large  Clockwork Firebird Designs - Alex Locke }

Welcome to Clockwork Firebird Designs! I am a self-taught, ever-evolving tailor, leather worker and costume maker with a penchant for creating monsters. I attend Live Action Role-Play (LARP) events and Anime/Comic conventions as both a trader and attendee on a regular basis. I've been doing leather work since 2008, and selling since 2011. I recall learning to sew when I was 6 years old and I've not really stopped since. Within the shop you may find armour, masks, trinkets, painted artworks, soft toys... anything I bring to mind or feel like turning my hand to! I am still finding my feet, and I am always learning new techniques.

{\Large  Pufferfish designs }

I started crafting jewellery as a sideline to my day job making costumes for live roleplaying. I am often inspired by scifi and fantasy, and started making pieces in the colours of favourite characters from books, films or comics. I love bright colours and can make items in the colours of Pride or national flags, or your favourite sports team. If you don't see your colour scheme, please ask!

