\begin{center}
\begingroup
\ul{\sc ICSF's Top Twelve Doctor Who Episodes}
\endgroup
\vspace{1em}\\
\footnotesize
\begin{tabular}{r >{\tt}l l l l l l}
&{\normalfont episode}
&&Doctor&companion&showrunner&writer\\
\hline
1&S3E10&\emph{Blink}
&10&Martha&Davies&Moffat
\\
2&S4E08&\emph{Silence in the Library}
&10&Donna&Davies&Moffat
\\
3&S4E10&\emph{Midnight}
&10&Donna&Davies&Davies
\\
3&&\emph{The Day of The Doctor}
&10/11/War&Clara&Moffat&Moffat
\\
3&S9E11&\emph{Heaven Sent}
&12&Clara&Moffat&Moffat
\\
4&S1E09&\emph{The Empty Child}
&9&Rose&Davies&Moffat
\\
4&S4E09&\emph{Forest of the Dead}
&10&Donna&Davies&Moffat
\\
5&S1E06&\emph{Dalek}
&9&Rose&Davies&Shearman\\
\\
5&S2E13&\emph{Doomsday}
&10&Rose&Davies&Davies\\
\\
5&S3E11&\emph{Utopia}
&10&Martha&Davies&Davies\\
\\
5&S4E11&\emph{Turn Left}
&10&Donna&Davies&Davies\\
\\
5&&\emph{The Waters of Mars}
&10&Adelaide Brooke&Davies&Davies \& Ford
\end{tabular}
\end{center}
\vspace{2em}

A survey was carried out to find the top 10 \emph{Doctor Who} episodes from
2005 onwards. Due to draws, we were able to identify 12 episodes to represent
Science Fiction and Fantasy Society's favourite selection of new \emph{Who}. I
aim to explore a variety of factors and patterns that lead to these episodes
being chosen.

The most popular showrunner was Russell T Davies, but the most popular writer
was Steven Moffat. None of the Chibnall era episodes made the list. This could
also reflect the series split due to popularity of different Doctors. The Ninth
and Tenth Doctors were found to be the most popular in a separate question
asking the favourite Doctor(s). Russell T Davies was the showrunner for both.

\vspace{2em}

\begin{center}
\begingroup
\sc
\parbox{0.26\textwidth}{\centering \ul{Doctor Split}}
\parbox{0.32\textwidth}{\centering \ul{Series Split}}
\parbox{0.3\textwidth}{\centering \ul{Companion Split}}
\endgroup

\input{txt/allday.doctorsplit}
\input{txt/allday.seriessplit}
\input{txt/allday.companionsplit}
\end{center}

\clearpage

\begin{center}
\begingroup
\ul{\sc ICSF's Favourite Doctors}
\endgroup
\vspace{-1em}
\input{txt/allday.doctorfaves}
\end{center}

All of the episodes in the top 12 can be said to be notable plot-wise,
particularly due to characters. \emph{Blink} was one of the few episodes to
establish an alternative protagonist to the Doctor in Sally Sparrow. The
two-parter \emph{Silence in the Library} and \emph{The Forest of The Dead}
introduced River Song for the first time. \emph{Midnight} was a compainionless
episode, which took the opportunity to explore a variety of characters and
place the focus on the Doctor. \emph{The Day of the Doctor} featured three Doctors
in one episode. \emph{Heaven Sent} occurred immediately after the death of
Clara and dealt with the Twelfth Doctor's reaction to this. \emph{The Empty
Child} introduced Captain Jack Harkness. \emph{Dalek} was the first
appearance of the Dalek race in new \emph{Who,} and the same was true of
\emph{Utopia} with the Master. \emph{Turn Left} was the setup for \emph{The
Stolen Earth,} were all of the Tenth Doctor's companions and allies united.
The episode itself showed the return of Rose. \emph{The Waters of Mars}
introduced the concept of the Time Lord Victorious, which has been explored in
an alternative reality audio series.

Furthermore, many of the top 12 are subjectively considered some of the
scariest episodes, in particular \emph{Blink}. In fact, all of the episodes
that made the list can be grouped as either `scary' episodes, or parts of season finales.
The finales of the second, third, and fourth season, all written by Russell T
Davies, are included in the top 12. Steven Moffat's era as showrunner was
characterised by complex overarching plot lines, but contained fewer
stand-alone mystery episodes, whereas his episodes during Russell T Davies's
run stood out. Chris Chibnall wanted to make his series more widely
accessible, so reduced the scariness and mystery of his episodes.
