\newlength{\userwidth}
\userwidth=1em
\newcommand{\userthorn}{\parbox{\userwidth}{\TH}}
\newcommand{\usermu}{\parbox{\userwidth}{\textmu}}
\newcommand{\userdag}{\parbox{\userwidth}{\dag}}
\newcommand{\userddag}{\parbox{\userwidth}{\ddag}}
\newcommand{\userOmega}{\parbox{\userwidth}{\textOmega}}
\newcommand{\userSigma}{\parbox{\userwidth}{\textSigma}}
\newcommand{\userinfty}{\parbox{\userwidth}{$\infty$}}
\newcommand{\useromega}{\parbox{\userwidth}{\textomega}}
\newcommand{\pesterlog}[1]{\vspace{\parskip}\begingroup\tt\parskip=0.1ex#1\vspace{0.1ex}\endgroup}
\pesterlog{
[00:53:10] \userthorn: don't you just want to go out there, see what's going on?

[00:53:44] \userSigma: No, 'cause no one who goes actually comes back.

[00:54:02] \userdag: literally why

[00:55:39] \userinfty: uve lost it bro fr

[01:29:24] \useromega: Still interested?
}

\hsep

The waters swirl dangerously near the border. The sea spray stings your face, mordant. Your 'proofing is solid enough but you still have to quell several sensors that tell you it isn't; you're due a software upgrade soon. Hardware's easy to get, you and everyone else at the agency goes through it like nothing. Parts are cheap, and you're harder on them than most. Your left leg's still not right from the fall you took two weeks past, but you'd gotten your guy at the end, so it doesn't matter. If you were meat, they'd call you reckless. You always calculate your risks, you just have a higher margin of what's acceptable than some of the others. Might be that's a software glitch in itself, but you doubt it. You have a specific role to fill, and you've been told accordingly.

\pesterlog{
\usermu: Are you sure this is the right place?
}

You look at your assigned partner\textemdash they have their own role, too, and it seems to be putting up with you. Watching you, when you're being uncharitable about it. Not that you'd do that, but you weren't exactly made kind. Their eyes on you makes you itch, all bright cyan meant to be ``soothing''. Most of the time they look at you diffidently. But sometimes, you catch them staring, and it's the look of someone who wants to take you apart right down to the wires. Sets you on edge.

'Course, you get that often enough; you've been told you're abrasive when the teller's patient, and gotten cussed out when they're not. But that's why you've got this job, instead of nursing or dealing with search and rescue. They just clean up your mess, and most days, you're grateful for it.

Some days, you can't stand the sight of 'em, and you think they know that. Most'd see issue with it, this one's better that way. Or quieter about it. But if they're complaining to every last officebug about your bad attitude, you don't much care as long as they don't do the complaining where you can hear it. 

\pesterlog{
\userOmega: I'm sure. That's what the report says.
}

You're not one to doubt the report, so you just nod. You pull it up to skim through anyway. 

\pesterlog{
\usermu: Mind your step. It's wet here and neither of us are that waterproof. 

\userOmega: It was an easy corner to cut. 
}

You disagree, but you don't say anything. Your partner's more straight-laced than you are by far, and you're not that close. Criticism isn't something that's taken well, and you're allowed a certain amount per month on goodwill. You're decently sure that you used that all up last week, and your boss isn't the type to \emph{have} any goodwill. A real hardass.

The words on your HUD are easier to look at than the border itself, but it still swirls uneasily in the background. If you could feel sick, you would; you get real close to understanding what the organics mean by \emph{nausea} when you look at it for too long. It's uncomfortable. You don't come here often if you can help it; problem is that you've had to more than you'd like lately.

\pesterlog{
\usermu: Kid goes missing. Posts a message about wanting to leave in a private chat room, vanishes three days later.

\userOmega: Yes.

\usermu: Fifth time it's happened in as many months.

\userOmega: Yes.

\usermu: Are you going to keep saying that to everything I ask?

\userOmega: No.

\usermu: Right. 

\usermu: Logs are the same as the last ones. The last person that talked to him in the chat was the same.

\userOmega: And we haven't been able to trace them.

\usermu: Yeah. If these are the best minds, we need better. Not my division, though.

\usermu: So, he comes through here. Dead of night. We've got cameras catching the route he took.

\userOmega: Also the same as the others. 

\usermu: Home to these coordinates to here, following the same streets. It's not the fastest way.

\usermu: Would've been faster to just come here.

\usermu: He walked it too, same as the others.

\userOmega: Yes. At the same times too. Give or take a few minutes, of course. But humans are not as precise about this. 
\usermu: Nah. 

\usermu: Same route, same time. What are we missing?

\userOmega: I'm sure I wouldn't know.

\userOmega: We need to talk to the family today, too. They filed the original report as missing. 
}

You turn to stare out at the churning expanse of water that separates you from\textellipsis whatever's out there. You've never been interested in knowing; you'd have to try real hard to muster up a want to, and again. It doesn't feel \emph{right.} You figure that's another quirk in your software, what little you have that passes for a self-preservation instinct. You can do plenty, but swimming's not on that list.

The scant grey light of the early morning gleams against the dark wood beneath your feet. The docks are old, the oldest part of this city, and dangerous besides. There's a reason they're in such a sorry state. 

You won't get any more information just standing around here, though. Whatever clues there were, they're long gone. 

\pesterlog{
\usermu: Better do that. I'll check his room, too, then make the walk.

\userOmega: As you say.
}

You turn away from the edge decisively, and start walking. Your partner's footsteps soon come to echo your own.

You're on a case now, but this one\textemdash you're not sure about.

You aren't.

Doesn't mean you won't be doing your best to solve it, though. What else is there to do?

\hsep

The city pulses beneath your feet, and you pulse back with purpose.

Your partner has long since turned in for the evening. You didn't expect them to stay; they're built for supervision and office work. You don't feel guilty that you look down on them for it, at least a little, or that you're relieved to have some time for yourself. 

You don't like supervision, you don't like someone hovering over your shoulder and questioning your every decision. You've gone through a whole lot of partners as a result, and the boss insists you keep getting new ones. You have no idea where they keep coming from, it's not as if they're fresh off the press. Your current one's lasted the longest, probably; they've got a way about them that's usually unobtrusive. They look but they don't impose.

Today, they were imposing a hell of a lot. Either that or your temper's frayed because your leg's been acting up again. Has been since the fall, not that anyone's listened to your griping about it. Hardware's easy to get, but none of you'd go in for replacements if you don't need to. You'll badger the boss about it later for something to do anyway, but you won't be getting it until you close this case. 

It works, anyway. Carried you to one end of Obsidian and back, and then back around. You let your partner talk to the kid's friends\textemdash what few of them he had in person\textemdash and comfort them, and you'd let yourself into his room. Wasn't much there, just the usual organic detritus. What you were interested in was the computer; you let one of the techies in to clear it out.  They'll have the info back to you by the end of the night, they say. You're not sure about that, but after being told to keep your mouth shut around them and be decent, you didn't actually say that. 

You walk the same route that kid did, and the one before, and the one before that, and you linger outside the cafe that they'd all stopped at. All-night affair, lots of students, lots of neon signs advertising cheap brews. Seems to be working, but it's a joint that's only unusual because of what you know. On the outside? It's the same as any caf chain in this place.

You lean against the wall and pretend to be smoking. It's dark enough that with your collar flicked up and  the shadows around you, no one's going to notice that your features aren't quite right. You hope. There's not a lot of metal this side of town. You wonder if that's why they ended up here. It's not like any of 'em had a grudge, though. 

People come and go, the cherry at the end of your cigarette glows bright as the signs around. 

Say they were meeting with someone, then. Time'd put it late afternoon, not night like this, when you have to worry about being noticed. There might even be a rush then; there's a 'port right around the corner. You send off a request for the cams footage from around here, date and time the last kid dropped by; you don't expect to see anything. You didn't for the others; too many people moving around, or heads ducked to hide faces, or those damn masks that've come into fashion to stop the facial ID from working right away.

The ping comes, and this time, it's different. 

You let the outside world around you blur to nothing as you focus on the footage. It superimposes itself on where reality used to be, and you track the movements of all these ghosts without issue. You recognize some of them, where their names or codes are tagged. It's the two untagged ones that get your attention. One unmistakably your missing person, head dipped, but his hair's a shade of red that'd be hard to ignore. Thomas Helm, human, age 17. Turning 18 in a week's time. Missing, presumed dead. He doesn't look like the kinda crazy the others did, buying into every conspiracy theory they could get their hands on.

Sure, he was on those boards. But everyone is\textemdash they're like the morning paper.

You watch him weave through the cafe, awkward. He doesn't know what he's doing. He doesn't know how not to stand out; all the others had a record of some kind, no matter how small. They were better at blending in, they knew where to look to avoid the cameras. You watch him look around\textemdash you were right, he's waiting for someone, probably the same someone\textemdash and you pinpoint the moment he spots them, a silhouette masked at a corner table. The shape of them's familiar, slight and short, but it's not like there's any real unique builds left.

Swapping angles doesn't help you find anything else about them. They know what they're doing. You figure that if you're lucky, this is the same person that talked to the others, maybe even the same one who was in ol' Tommy's DMs after adding to his thread. You snap a picture, send it off to see what the bugs can do. Something, you hope. They're not getting paid for nothing. 

You add a note to get someone who can read lips to look at it, too. No audio, else they'd have sent it along too\textemdash again, you hope, sometimes they're real useless\textemdash but you don't have a single clue what's being said. You're willing to bet \emph{that's} where your break is. All you have to do is wait. 

Reality filters back in parts, as you watch the kid's phantom brush to the exit, until he walks right through you and vanishes. You keep watching the patch of street where it faded entirely, not registering much other than the names and faces of anyone who passes. It's information, sure, but none of it is what you need. You drag your gaze down to the ground instead, so sleek it's nearly reflective here. Everything's brand new, the glow of it distorts the faint shapes you make out beneath you. Red-pink signs, the neon greens and purples of shoes, the flickering blue that's oddly familiar.

You look up.

Your cigarette tumbles to the ground. You've never dropped anything before, not when you didn't mean to, but\textemdash

There they are, coming right into the cafe. To meet someone, you're willing to bet. You don't know if it's you. 

You're hailing them out before you mean to.

\pesterlog{
\usermu: Thought you were going to recharge. Glad to see you've tagged along, though.
}

But it isn't until they look up too, that familiar too-sleek silhouette, built for paperwork and not walking, and their eyes are wide behind the familiar pale cyan glow, frozen as they process what to do, that you \emph{know.}

You'd count it down to surprise, if they didn't turn and start running. If they didn't send another kid sprawling on the way, too young to be here at this hour. If they didn't have a mask in hand, ready to go on.

And you're off.

The city pulses with life under your feet, and with purpose, you slam right back into it.

\pesterlog{
\usermu: Was it you?

\usermu: The whole time, you, throwing those kids into the sea?
}

You hail them, again and again, as you two weave through the alleys and streets. You can't fire your weapons here, and they're being canny enough to stick to the crowds, where they get to slip through nice and easy, and you\textellipsis well. You're not built for that so much as you are to take hits and dish them out. You don't bother apologizing.

You know where they're leading you, by the fifth turn. 

You wonder if this happened too, if it was a chase like this. You know damn well you're not going to let them get what they want, and as soon as you break into an open space, you pick up speed. Your smaller frame slams right into theirs; you both go down. But they're the one who shoves you off, so hard you go sprawling, and something in your leg goes numb afterwards. Your sensors pick up red flags all over the place, but you've been hurt before and you ignore it, you know how to.

\pesterlog{
\usermu: What are you doing?

\usermu: Answer me already!
}

Nothing.

Just them, getting up, and running. You force yourself to get up and go after them. And now, you know exactly what they're doing\textemdash they want to be caught. That has to be it, with how they're just slow enough for you to keep up with, staying just that far ahead. You're furious at it; who do they think you are? You don't care if this is a trap, although you also have no clue what else it could be, why else they'd \emph{want} to be caught running away.

You go down again in an alleyway, narrower this time, far from all the bright lights. The wastebins clatter like gunshots as they scatter, one crumpling under your frame. 

They wait, at the edge, just barely where you can see it.

You get up again. You go, you keep going. Even if you weren't chasing them, you'd know the way; you memorized the route after walking it the first time, and this is your tenth, easily. 

Something grinds in your leg with every step you take, the false skin on your palms is torn out and the sensors under it scattered. Those, you doubt you'll be able to get replaced. 

It's only when you get to where you're going, where you'd stood not so long ago, that they bother to pull out the trump card. 

If a card was fifty thousand volts right to your chassis. You drop like a sack of rocks, so hard the wood creaks alarmingly under you. You think you scream; you can't be sure. Auditory processing's gone entirely. Your vision whites out, you're one wrong twitch away from rebooting entirely, and you feel your limbs twitch without your permission. You ache, right down to your microchips. 

\pesterlog{
\usermu: Ow.
}

You're surprised you can even send a message in this state. Local comms only, your backup channels to the office are fried. And even if they weren't, there's no one there but the bugs anyway. All \emph{they}'d do is pass on the message. Too little, too late.

You wait, let the world slowly start to reassert itself as the rest of your systems decide whether or not they;re coming back online. Some do\textemdash sensors, mostly. Touch, where they're still there, but there's dead spots where you can't feel a single thing. Your vision is still hazy, pixels glitch persistently white on the upper left corner of it; something's gotta be wrong with one of your eyes now. Audio's not back, but you don't need it. 

The sea stings at you and lances into the cuts on your arms. Your chassis is damaged, more badly than it has been in a while. You think, wryly, that you'll need a complete overhaul when you get out of this. If you get out of this. You can't move yet, you think. You need to stall.

\pesterlog{
\usermu: Well, then. You got me. Proud of yourself?
}

You think they're looking pretty damn smug, if you say so yourself. 

\pesterlog{
\userOmega: It didn't have to be this way.

\userOmega: You could have stopped looking after the first two came up as nothing. You should have stopped looking, but you didn't, did you? No. Anyone else would've. The two others would've classified these as dead ends, left them to go cold, as they should. They wouldn't have called it murder with no evidence, and then failed to get any evidence. 

\userOmega: I told them you wouldn't. I said, he's so stubborn, he won't. Not now that he's got a trace of it. I thought you eyes were all the same, but you're not\textemdash you're the worst of the bunch. 
}

This is the most you've heard them talk ever since they were assigned your partner. You bet they're real chatty when it comes to whoever they're plotting with, but you mostly want them to shut up already. Your HUD's glitching, too, you can barely make out the cyan blur of their words.

\pesterlog{
\usermu: You can't blame me for looking when it's my job.

\userOmega: I can.

\userOmega: You should've stopped.

\usermu: I'd ask if you were going to kill me for it, you know, but. The answer seems real clear.

\userOmega: It would be a waste. There's only three of you in the city. 

\userOmega: You could always join us.

\usermu: Us, them. You keep saying that, which is funny, since you're not also saying who they are. You expect me to join up with a bunch of strangers after you tried to fry me?

\userOmega: Suffice it to say that the people I'm working with have a vested interest in recruitment. 

\userOmega: I hate to say it, but you'd probably do well. You ask a lot of questions, they like that.

\usermu: As if. They made me reckless, they didn't make me a traitor. Come on, tell me. Does the boss know? Does anyone know? You said you've got a little group just now, plotting and planning. A whole bunch of traitors just lurking, waiting for a chance to strike. Cowards, the lot of you, as far as I can tell.

\userOmega: Are you trying to provoke me, here?

\userOmega: It won't work. I'm better than that. Though you're not better than making the attempt.

\usermu: I'm not the one who's been killing people.

\userOmega: What? Oh, of course. They're not dead, you know. We've simply liberated them.

\usermu: Sure, you keep telling yourself that. No one's going to survive a dip in that thing.

\userOmega: That's what you think now. Go on, look at it. You can't, right? Haven't you ever wondered why that is? Why none of us come here, why they warn us away every time we have business to attend to here?
}

You have. You're not going to give them the satisfaction of saying that. You also don't give them the satisfaction of looking, either. Instead, you snarl, and for all that you're in a sorry goddamn state, it's not half-hearted. 

\pesterlog{
\usermu: It doesn't matter.

\userOmega: Of course you'd say that. You don't have half a brain beyond what they gave you. Solve problems, solve mysteries, but you won't even look at the one right at our doorstep.

\userOmega: Or you wouldn't, before. But now? Now, you have to, don't you?

\userOmega: You don't have a choice here. 
}

You can't leave, and they know that. Not one way, and, as you cut a glance behind you, to the screaming water\textemdash not another. It's hard to look at it directly; always is, but now
it's worse, and you don't know why. But you've got more pressing things to worry about than if you can see the ocean right. You know it's there, that's good enough.

You run diagnostics. You hate that they're right. You won't be able to get away; one of your legs is throwing sparks like nobody's business. You don't have any weapons either, not unless you want to club them with a loose board around here. 
You drag yourself up anyway.

\pesterlog{
\usermu: Of course you'd say that.

\userOmega: You don't. You're cornered, and you know it. I'm offering you a way out.

\usermu: You're offering me nothing but a pack of lies. Didn't think you had it in you.

\usermu: But they'll be looking for me. And they know I found you, at the cafe. They'll know it was you.
}

You're being a hypocrite. You're also not going to let this bastard kill you, so you don't really care about that. If they buy into it, if they believe that you've got people on the way, it might spook them. You can bluff.

\pesterlog{
\usermu: It doesn't matter what happens here. 

\userOmega: You're right about that, at least.

\userOmega: But you're wrong about the second one. They won't know you found me. I've been paying attention, you see. Always cleaning up after you like I'm supposed to, so I know you well by now. And here's the thing: You'd never ask for backup, and now, it's going to be the end of you.
}

You can't bluff, it turns out. Not convincingly enough against someone who's been watching you that close\textemdash and you were right, weren't you, thinking how they wanted to break you apart. But you've bought yourself just enough time to muster your strength, and that's going to have to be good enough.

They take a step forward, one arm outstretched.

You do the only thing you can, the only thing you know how.

You jump.

The last thing you see is that blue glow, distinctly smug. Before the water takes you, you get the message:

\pesterlog{
\userOmega: I told you that you'd see things our way.

\userOmega: Good luck. 
}

\hsep

\pesterlog{
[18:53:01] \userddag: you guys hear about what happened to that eye the other day? didn't even make the news but there's guards and shit dockside now. 

[18:54:23] \userSigma: Yeah. Right after \userthorn, too. Apparently he was investigating it.

[18:54:30] \userinfty: fr?

[18:54:48] \userSigma: You can look it up, yeah. They don't do obits for the eyes,  just a retirement notice. I think there's footage somewhere too, but be careful about that.

[18:55:20] \userSigma: They were taking it all down last I heard. You're gonna have to do a lot of digging.

[18:55:32] \userinfty: idm

[18:55:48] \userinfty: ill dm u if i find smth

[18:55:59] \userSigma: Sure, I appreciate it. Same to you, but I don't know how much there is to find. Seems like it's being covered up. 

[18:58:31] \userddag: real shock there

[20:12:02] \useromega: I know all about that, actually. Same as \userinfty, I know someone who saw it happen. 

[20:12:03] \useromega: I can tell you, too. 

[20:12:03] \useromega: And then you can see for yourself. 

[20:12:10] \useromega: The guards are easy to slip past if you go a certain way, I'll give you a map of it.

[20:15:36] ADMIN NOTICE: THIS MESSAGE BOARD HAS BEEN SHUT DOWN. NO FURTHER POSTS ALLOWED. IF USERS ARE FOUND TRYING TO ENGAGE AGAIN, THERE WILL BE AN AUTOMATED STRIKE AGAINST THE ACCOUNT. IF YOU BELIEVE THE STRIKE WAS MISTAKENLY GIVEN, SEE FAQs FOR HOW TO APPEAL.
}

