The forest isn't a forest. Not anymore. Instead of trees, Red picks her way between pillars of silicon. They grow in rows, nothing like the wild freedom of the trees. If she looks in the right direction she can see a long way, space yawning away ahead of her until the light from her lantern fades.

Red doesn't look at the forest. She keeps her eyes on her fur-and-leather boots, lowering the lantern. Its flame flickers with the motion, but doesn't go out. There. The barest hint of a shadow, an impression in the concrete forest floor. Telling her where to go. She places her foot carefully, shifts her weight. 

The wicker handle of her basket shifts around her arm. She settles it, placing a hand softly over the red-and-white gingham fabric to keep it from rustling as she lowers the lantern again. She needs to be quiet for as long as she can.

There's a flicker of motion to one side, and Red's head snaps up. She lifts the light, as far as she dares, peering out into the gloom, but the endless columns are still and silent. 

Maybe it was nothing. Maybe it was another forest creature, a squirrel maybe.

Her breath fogs in front of her. Her throat is dry. 

There are no other creatures. They have gone. There is her, and the forest, and the wolf. 

She looks down. Picks her next step. Her heart is pounding. If she can just keep going, follow the path, get to its end, then\textellipsis

She takes another step. Another. She's rushing, she knows she is, but the path is so hard to find. She grits her teeth, and keeps searching. Her heart is pounding. 

She doesn't know what will happen if she reaches the end of the path. She doesn't know if there is an end to the path. She doesn't know why she is carrying the basket, or who it is for, or---

A growl fills the air. It sounds like metal, screeching as it tears. 

Red looks up. Her heart is pounding. 

The wolf isn't a wolf. Not anymore. Its fur is long gone, its teeth shattered glass, its eyes glaring red LEDs. They are locked on her. 

Red steps backward, shaking. The wolf steps forward. Its lip curls. Its teeth glint, reflecting the small flame of her lantern. 

She runs. The wolf is on her before she makes it two paces, knife-claws tearing into her back, teeth ripping at the hood of her cloak. She falls, the weight of its body slamming into her, and her hands rip against the rough concrete. Her lantern smashes against the ground, and goes out. The only light is red. The only colour is red. 

The wolf's breath is hot and wet and smells of oil. She sobs, and it sinks its teeth into her neck, and red blood spills over her furs, her basket, her cloak. She squeezes her eyes shut, and---

Red's eyes open. What used to be the forest stretches out before her. Nothing moves. She breathes in, and breathes out, and it catches in her throat. 

How long has she been doing this? 

She bends down, and picks up the basket. Hooks it around her arm. 

Earlier on, there was snow. She remembers that. It was pretty, fat flakes twirling around her, settling on the branches. It's long gone. 

She lifts the lantern. This time, its light is white and harsh. Electric.

It's the first time that the change has been in something she carries. It's always been the forest, or the wolf, or the path. 

Maybe the next change will be the basket. Maybe it will be her. Maybe she's already been changed, and just doesn't remember it. 

Red stares at the lantern, eyes throbbing from its light. 

The harsh, white light cuts further into the gloom. It could make it easier to see the path. It could make it easier for the wolf to see her. 

Without it, she won't be able to see the path. 

Red pulls her cloak tight around her, takes a deep breath, and starts walking. There isn't much else she can do.
