\interfootnotelinepenalty=10000

\textbf{i.}
The doors hiss as they open, the silhouette behind them stepping
neatly into the room.

`I have been thinking about what we discussed earlier, Captain Thurin,
and I believe I have come to a satisfactory conclusion that defines
our relationship,' comes a familiar voice, soft. `Since you insisted
that I consider it so deeply, I made sure to take my time. The
conversation took place four solar cycles ago, in case you required a
reminder.'

`How many times do I have to tell you to call me by my first name,
BLAKE. How many?' Augusta rests her head against the cool plastisteel
of the table, all four of her eyes closing. The common areas of the
ship run too warm for her taste, even if she's stripped out of the
more formal layers of her uniform. She'd originally balked at the
thought, but it's only her and BLAKE on the ship now. She doesn't need
to work to impress anyone other than herself, and comfort was quick to
take over as the top priority. `And I'd say I've already come to that
conclusion, just so you know, so I won't be hearing any brags about
your processing power and all that.'

`I will continue running that calculation and return the result to
you, but all prior evidence suggests that it will be at least one more
time,' BLAKE says, their tone even as always. Augusta looks at the
robot through narrowed eyes.

`It seems that you are taking umbrage at my words, Captain,' they
reply, blithe. `Your tone suggests that you would define our
relationship as that of a person and a particularly annoying insect.'

`Not your words, your tone,' she corrects, making herself straighten
up properly. `And don't think I didn’t notice you not saying which of
us would be the insect.' It’s unbecoming of a Captain to slouch all
over the mess table, after all, even if BLAKE is the only witness. She
doesn't want to be rude.

`My tone has been perfectly calibrated to be soothing Class V
lifeforms as part of my instalment here. And my diplomacy protocols
ensure that I would never say anything offensive to you, Captain.'

`And yet, you sounded a little bit put out just now, didn’t you?' she
presses, `and maybe, dare I say, kind of smug, earlier?'

`If my humour isn't satisfactory, you can always adjust the settings,'
BLAKE says, prim, because they know fully well that Augusta won't
tamper with a single thing.

She's been with BLAKE on this ship for just short of a lunar sweep
now, suspended in orbit useless as anything, and\textemdash not to
complain or anything, because Captains definitely don't complain, but
\textemdash{} it's the worst assignment she's ever had.  `I might have
to adjust them to make you funnier,' she grumbles.

`Oh, of course. Calibrating \textellipsis. please hold.' Augusta
squints over at BLAKE, suspicious. They're not a fully humanized
model, no SynthSkin™, none of the bells and whistles that make the
real top-of-the-line models entirely indistinguishable from a person,
if you knew fifteen thousand people with the same face. She's never
asked about it, or about the avian lifeform engraved just at the nape
of their neck. It's the only custom thing about them, she thinks. All
she knows is that they've been with the fleet for a long, long time,
and has refused all software upgrades beyond the necessary patches.

Instead, their faceplate is a smooth, burnished bronze, their eyes
glowing in a soft, matching yellow, their build compact and slim for
convenience's sake beneath the compulsory fleet uniform. They're
bipedal, two-armed, their architecture not wholly unfamiliar to
Augusta, but certainly different from her own. All in all, they give
absolutely nothing away, and this is why she never plays any sort of
cards with them, no matter how bored she is.

`Calibration complete,' BLAKE says, and nope, Augusta still can't tell
how serious they're being. `Knock, knock, then.'

`Knock\textemdash what?' Not what she'd expected. Then again, none
of this has been what she's expected.

`Knock, knock. A joke. Maybe \emph{your} humour settings need
adjustment, Captain. My databanks indicate that this is a much-used
format for jokes through many galactic clusters.'

`I\textemdash know what that joke is,' she protests, crossing her
arms. All of them, for emphasis, because she knows BLAKE can pick up
on those cues, and she wants to make the point.

`Then you should know that you are required to provide an input so I
may complete it,' BLAKE says, and Augusta knows she isn't imaging the
almost petulant note in their voice.

They're an old model, not made to imitate wholly sentient, organic
life, but they come disconcertingly close to it sometimes. Augusta
isn't always sure what to make of it.

In this case, though. She'll play along.

`Fine, then. Who's there?'

`Given that we are currently in the vacuum of space and it is nearly
impossible for any lifeform to survive unshielded from it, I would say
that it's trouble.'

`Trouble \textellipsis who?'

`Trouble for you. I can't die, and there is a very low chance that any
deliberate knocking upon the hull would bode well,' BLAKE finishes,
sounding perhaps a little too proud of themselves for that
joke. Augusta's sure she looks horrified in some way, because they
regard her with something similar to concern.

`It is dark humour. I thought that you would appreciate it the
most.'

`I appreciate the thought,' she answers, diplomatically as she
can, which isn't very: it mostly sounds like an evasion to her ears,
but it doesn't seem like BLAKE minds.

`You might not die, but I don't think floating around in space for
eternity is going to be good for you. Or fun, if your chassis can
handle it.'

`It can, but not for longer than an hour. That is the estimated length
of time it would take me to perform any extravehicular repairs. So my
joke was inaccurate in that case. This mission is more dangerous than
it seems,' they agree after a moment, nearly thoughtful. `Apologies,
then. It was in poor taste. Perhaps when we return and are safely at
headquarters once more.'

`And then the joke can be a rookie learning to spacewalk for the first
time,' Augusta adds. She remembers that bit of her training all too
well. She's never enjoyed zero gravity conditions; her home planet is
ten times the standard gravitational unit, and every little movement
would send her slamming right into the nearest hard surface. She's
better at it now, but they're not her favorite memories.

`I would not be surprised if you were to find one here. They do get
lost very easily.'

That gets a laugh out of her, finally, and BLAKE's eyes glow brighter
for just a second with satisfaction.

`I see that I have found the correct humour niche to explore,' they
say. `I will note this down for later.'

`Please. My partner always complains about them, but no one told her
``Char, you should become a teacher, you're very good and patient with
younglings.'' Granted,' Augusta pauses, taking a moment to consciously
ensure she's not smiling too hard, `no-one told her she was a complete
terror and was needed to make sure all the new recruits toed the line,
either, but they sure were thinking it.'

`You must miss her terribly,' BLAKE says, and there's something in
their voice that gives Augusta pause. It's not unusual, with models as
old as BLAKE is, for there to be certain behavioural artefacts. She
was warned about them, when she'd been assigned this mission. What to
expect, what to look out for \textellipsis though she hadn't been
paying too much attention, at that point. She'd been too excited about
this, her first solo mission. Well, solo on the organics. And it's the
first mission she has been fully in charge of. And they'd made it
sound so important.

They failed to mention that she'd be hovering a safe distance from a
roiling, dusted-over tomb of a planet waiting for
Thierru-knows-what. Further instructions, maybe. Something to happen
there, more likely. Augusta reins in the annoyance that threatens to
bubble over\textemdash she's not good with waiting, but she's
determined to see this through. It'll be fine.

And until then, she'll keep trying to understand why she's here: why
that planet is so important, it needed someone to watch over it; why
she was the one chosen; why BLAKE was chosen to accompany her. She
knows all the official reasons, of course, but instinct tells her that
there's something more.  Logic tells her that she very well might just
be inventing problems where there aren't none, but Augusta didn't get
this far by only listening to her logic.

`I do,' she finally answers, letting her chin rest on one hand. `I
didn't think I would be here this long. It's been a while, since we've
been apart for longer than a few solar cycles. Living and working on
the same station made us a lot worse at distance. As a complaint, it
doesn't exactly have any legs to stand on. Especially with me
complaining at, well, you,' she adds, trailing off after a
second. Augusta deflates slightly.

`Providing conversation and ensuring morale remains high are both
encompassed under my orders for this mission. I am reasonably certain
that this is part of why I was selected to be your companion. You have
not been very comfortable with many of the newer models, and I am more
experienced in dealing with organic lifeforms,' BLAKE says, smooth and
easy. It lines up almost exactly with what they'd told her, but it
doesn't make her any less self-conscious about confiding in a robot.

`I manage fine with them,' she protests, instead, `But the
whole \textellipsis thing, about needing to be able to tell that
they're artificial? It throws me off.'

`It is largely considered ethically wrong to have a robot that is a
perfect imitation of organic life, whether it is in appearance or in
thought processes,' BLAKE recites, but there's something strange in
their tone. `No-one would want a robot running around with their face
and personality, regardless of what its builder might have intended to
use it for. Hence the creation of custom designs repeated throughout
the newer models, to give the illusion of it at the very least,
without crossing that line. I understand that many species, yours
included, find it unpalatable despite this due to a strong component
of communication being unspoken.'

`Well. Yes,' she says, slightly more flustered than she'd like to
admit. She feels like she's been caught doing something
wrong\textemdash it's uncanny, to hear a robot phrase her own
reasoning.

`Body language and expression is important for us, and it's worse for
species that primarily use scent or specific auditory cues. Robots
that can do more than regular household tasks aren't really popular
back home, unless you're affiliated with the government. Or work with
the fleet. And you're fine, I'm used to you. Obviously.'

`I should think so. We have been together on this ship for a long
enough time now that even if you found me unnerving originally, that
would have been dulled by consistent interaction by now.'

`I don't find you unnerving,' Augusta answers immediately. `It's-
easy, with you. You're just \textellipsis what you are. And I think
you've picked up a lot of nonverbal cues since we've been interacting,
even if your limb configuration isn't quite right for them.'

`I did tell you that I had experience,' they say. `And it is not too
difficult to notice and mimic what cues I can, especially audiovisual
ones that do not require multiple limb sets. You do not like
dishonesty or pretense, even if it is well-intentioned, so I thought
it best to only attempt ones I knew that I could do correctly, those
requiring two arms or less.'

`It's \textellipsis nice of you to try,' is what she settles on
saying. `I appreciate it. You're doing a good job, with the part of
your assignment involving keeping up morale.'

`With only you to consider, I can focus my efforts well, and there is
no need to worry about mediating any inter-personnel arguments. It
isn't a wonder of diplomacy.'

`No, I guess not.'

Silence reigns for a long moment, and Augusta finds her gaze drawn yet
again to the planet below them.

`So when you say experience, and wonders of diplomacy,' she asks,
because she hates the quiet and the tension it carries, and she
doesn't want to dwell on the nagging question of what it is, exactly,
they're meant to be waiting for, `how long have you been doing this?'

`I have been ISF property for a long time now. My manufacturers would
quantify it as a century, which converts to just under a thousand of
your lunar sweeps,' they answer. It takes a moment, and Augusta lets
the information percolate.

She'd known BLAKE was old, but not that old.

`That's\textellipsis almost as old as the fleet itself.'

`I was considered a new model then, yes, but before you ask me any
questions regarding important personnel I may have encountered, I
would like to clarify that I was mainly assigned to exploration
teams. Finding new inhabited planets.'

That makes more sense to her: close confines with few others for long
periods of time, no wonder they'd put BLAKE on this mission with her.

`I wasn't going to ask if you'd met the founders,' she says instead,
`but did you discover any inhabited planets?'

`A few. My main objective at the time was to catalogue planets and the
probability of their supporting life. I had a much sturdier chassis
then, too,' they add, with a brief gesture down at their body, `But
no, I did not have the fortune of being assigned to one of the ships
that encountered sapient life. The most interesting thing were some
novel microbes, but they didn't amount to very much use given that
they couldn't be grown in a lab. The planets were marked for
monitoring, but it will be a long time before anyone else gives them
another thought.'

`Still. That's the sort of thing I thought I'd be doing, when I joined
up.'

`You sound as if you have a different opinion, now.'

`Of course I do. It's lonely work,' she says, and then catches herself
before tacking on a `you know' to that sentence. BLAKE wouldn't
know. `And I get homesick too easily for that kind of thing anyway, I
mean\textemdash I haven't even been away that long, and I'm already
missing Char. Unless she came with me\textemdash and I don't think
she would\textemdash I wouldn't even consider taking any of those
jobs, even if they recommended me for it. This suits me much
better. Well. Not this specifically, I think it's boring and probably
unnecessary to the point where it concerns me, but the short-range
mission thing. I don't know how they get anyone to sign up to the deep
space missions at all\textellipsis they know that if they come back,
everyone they know will be dead. I couldn't deal with that.'


`And your aptitude tests likely showed it,' BLAKE says. `It is a lot
simpler for us. Mostly because there are robots designed for the
probes that are never meant to return.'

`I see how that makes things easier. You weren't one of those, right?
Your file\textemdash I mean, you know I've read it, just like I
know you have access to mine\textemdash never said what your
original purpose was.'

`No.'

`Right,' Augusta says, slowly. There's nothing aggressive in BLAKE's
tone, not that she was looking for it. Not that there would be
any. Robots don't do that. But there is a distinct undercurrent of
`don't ask me anything else' about this, which Augusta decides she'll
ignore entirely. Just, she'll be careful about it.

`Is that because you don't know?'

`No.'

If she didn't know better, she'd think BLAKE sounded exasperated. `It
is because I do not technically have one. My creator did not program
me with any specialization, but that was normal at the time. On that
planet. He thought that it would be most useful if I were able to
adapt to any task needed, given the circumstances at the time.'

Augusta might not be great with robots, but she does have a knack for
knowing when someone isn't telling her the whole truth. Which is- a
little ridiculous in this case. It's not like a robot can lie; it's
not like a robot would have a reason to, unless it was ordered to. And
she's not sure what BLAKE's past has to do with this, but she's going
to find out.  `Do you remember him well?' she asks, but this is mostly
curiosity.

`Very. He was not a kind man, but he was a good one.' It's more
pensive, more nuanced an answer than she'd expected. `He died, of
course\textemdash his kind were not particularly long-lived. And
especially not then. But I remember him.'

`What planet was that?' she presses on. `Why were you built, without
any specific purpose? What circumstances are you talking about?'

`Are you interrogating me, Captain Thurin?' BLAKE asks, their voice as
calm as ever. `It seems that you are tense and that your heart rates
are elevated. Do sit down.'

`This isn't an interrogation,' she snaps, her shoulders tensing. `And
my heart rate is entirely fine. Why won't you answer my questions?
None of those things were in your file. Were you ordered to keep them
hidden? Does it have anything to do with the mission, or have you
been\textellipsis \emph{lying?'}

She stumbles over the last word, not quite able to conceptualize
it. Because if BLAKE is lying\textemdash if BLAKE has
been \emph{told} to lie, then she doesn't know what she'll do. She's
been going over the facts about this since she first laid eyes on that
planet, desolate and miserable and entirely damned, and she's still no
closer to reaching a conclusion. She knows right down to her bones
that it doesn't harbour life\textemdash at least not the kind the
ISF has been looking for. It might have in the past, but it doesn't
now.

`I was not ordered to keep them hidden, and I am not lying. I never
received any separate mission objectives from you, only the order to
observe this planet until told otherwise,' BLAKE answers. They aren't
looking at her, their gaze almost distant and the soft yellow glow of
their eyes muted. They're looking past her, through the thick window,
and at the dun grey sheen of the planet below. Distant pieces of
shrapnel and scrap catch the light of its single sun on occasion,
drifting across their field of vision. `I do not think the answers to
any of your questions, bar one, is relevant to the mission. You are
only interested in my response to that one, correct?'

`No, but it'll be a good place to start.' She finally sits, and makes
herself relax. Augusta doesn't follow their gaze; she doesn't like
looking at the planet. Unfortunate, given the entire point of this,
but the cameras can do the watching. She hasn't ever been anywhere
that's felt so desolate before. She looks at it, and she can taste
sand coating her tongue and stinging at her eyes, her skin cracking in
the harsh half-light of its sky. `They didn't tell us to drop any
probes,' Augusta says, absent and to herself. `They don't know what
it's like there, and they won't know from us sitting here.'

`No, they don't. But they know what this planet used to be, even if
they have not dared to send a probe down,' they walk over to the
window, and press the flat of their hand against it. `It would not be
wrong to say that we now know each other quite well.'

`It wouldn't,' Augusta answers, her eyes narrowing. `Are you going to
get to the point?'

`I am. I would like to think that I would have told you this anyway,
had you asked. And I would like you to know that I am not offended by
your accusation, or your suspicion. You are a Captain for a
reason. But I am not answering this question because you are my
superior officer,' they start off. They still aren't looking at
her. `This planet used to be entirely full of life. It is not the only
example of a dead planet, but it is the only one they've found that
was killed in this way.'

`And you know this, how? None of this is in the archives. When I got
the brief, they said that this planet had been singled out for
monitoring. It doesn't even have a name, just the identifier code.'

`It isn't in the archives,' BLAKE says. `This is where I was
built. That is how I know.'

`You\textemdash what?'

Out of all the answers she could've gotten, BLAKE has yet again
managed to give her the one she least expected. Their penchant for
shocking her really is starting to get annoying. Augusta makes herself
stay quiet, try to figure out what this means and why.

`So if they know that, they must have sent you here because they think
you'd\textemdash what, want to go back down? Recognize anything
down there? I don't know how you could, it just looks like. Dust, to
me. There's nothing there. At all.'

`Captain,' BLAKE says, slowly. `I think you need to see this.'

`No, no. I want you to tell me everything, now. What were you doing
here? What happened there, that made you say the planet was killed?'
She's nearly frantic with it now, brushing off BLAKE's words
easily. `And\textemdash if you were there, when it was dying, how
did you survive?'

And in the breath before their answer, the wail of an alarm shatters
the air.

\hsep

\textbf{ii.}

Blake reaches up, the pads of their fingers tracing along the
bird \footnote{ \textit{Falco columbarius}; Merlin; extinct year 2201
at death of last known individual in captivity at the start of the
Dust Plague; planet of origin: Earth; shares a name with a mythical
magician from a local legend.} engraved just at the nape of their
neck\footnote{The marking is approximately four centimeters by eight
centimeters if mapped on a curved square against their chassis, carved
painstakingly, grooves of uneven depth to mark eyes, feathers, the
hook of claws and beak in relief. Much of the texture has been lost
from the original, where the jagged edges would catch on fingers and
cloth. A memory: The faint rasp of skin and roughened fingers against
it, the pitchy drag of sharp metal against metal; the feeling of being
watched and known.}. It isn't a nervous habit: they don't have those,
after all\footnote{\texttt{Protocol A-1233-XHJ-8 is locked in and
cannot be disabled. Please contact the manufacturer if your 814-K3
model is showing signs of malfunction.}}, but it is a habit
nonetheless. It's quiet; Blake has long since tuned out the usual
drone of the ship's machinery. Audio input is only a reliable
indicator of malfunction when it's catastrophic, and they've already
integrated the video feeds and data from the autolog to be
monitored\footnote{\texttt{PROGRAM
RUNNING\textellipsis{}.RUNNING\textellipsis{}.RUNNING\textellipsis{}.}}.

They'll receive an alert if anything goes wrong, but it is extremely
unlikely that anything will. The chance is 1 in 1,767,099,146. They
like to be precise.

They haven't written any reports, or sent any off to explain the
circumstances. They could, given that they are the last crew member
standing, so to speak\footnote{See Section 14.5.4 of the ISF Manual.},
but the Captain had not given them access to many of the organics-only
protocols aboard the ship. Those can be circumvented, of course;
the \textit{Brox}'s AI is limited, but the nonessential communications
ban is not one Blake is compelled to alter. A distress signal has been
sent, their part is done, and it's clean-cut, as far as protocol. They
are not at fault, at least not in the eyes of any higher-ups that
decided this was a good idea.

But perhaps if they had said something. Not before they left, but to
the Captain, after. When she had asked.

No. It wouldn't have made a difference, and they know that. But that
doesn't make things better.

It is 16:08, standard ship's time, and Blake is sitting in front of a
cryochamber with their legs crossed, staring at the clouded
polycarbonate\footnote{\texttt{If you would like your 814-K3 model to
purchase CryoGlass\texttrademark{} at the price of 18.00ϡ per kilo,
please confirm your payment information!}} that forms the top of the
chamber. They do not mind the cold\footnote{\texttt{Cryo room
temperature holding steady at
0.1°C\textellipsis{}.0.12°C\textellipsis{}.-0.01°C\textellipsis{}}} of
the room, and so they spend one hour here a day. More if it can be
spared, which it can, but that can be in silence.

Blake does not like silence\footnote{Another memory: The complete
absence of anything other than ambient sound long calibrated out to
nothingness, a space with every detail already mapped out and yielding
nothing new, one empty seat untouched by the wear of the rest. A
window staring out into blackness with bare pinpricks of light.}.

Many sources of information suggest that living creatures can
integrate audio input even whilst unconscious or with very low levels
of intrinsic brain activity, and so Blake comes here to speak, even
though they cannot see the tank's occupant as more than a faint
silhouette in the viscous, subfreezing liquid inside.

`Good progress is being made on the engine repairs,' they start off,
as always. It wouldn't do to give the Captain bad news, but this is,
at least, true. Any progress is good progress. `I was able to use the
pod to recover some needed shrapnel. There is a lot of raw material
orbiting this planet, a huge ring of waste. Primitive
things\footnote{Catalogued as the following: nonfunctional spacecraft
(formerly occupied, 10; unoccupied, 332); derelict satellites (15);
what appear to be launch vehicle stages (86, empty), weapon remnants
(1493); assorted personal effects including clothing, metal, and items
made of wood; assorted paint flecks and metal fragments too small to
pose a threat; microparticles too numerous to count.}, remnants of
the first steps the native species made towards intrastellar
flight. Not even interstellar at that point, from what I've seen. But
the scraps will be enough to assemble new parts, and as for
compatibility\textemdash' Blake pauses. They still cannot lie
outright; they know that many, if not all of the parts need heavy
modifications if they're ever to work as part of the \textit{Brox}.
`\textemdash{} as for compatibility, I will have to try.'

`The nanodust\footnote{\texttt{NanoDust\texttrademark{} can no longer be
purchased as it is a Class III prohibited substance! Please choose
another item.}} cannot propagate through space, thankfully, and the
parts of the ship I was forced to remove are far enough away that they
should no longer pose a problem. It was lucky that it didn't get into
the engines,' Blake pauses, lets their hand curl into a loose fist
against the glass. `They should not have sent us here. They should
never have sent anyone here.

`I have read the draft of your report. You were not wrong to call it a
tomb, but they may not have been wrong to frame this mission as a
search for life. There is always the possibility that there remains a
lifeform there that was able to survive the Dust. It may even be a
world entirely populated with robots such as myself. But that isn't
considered life. You would not like that very much, would you,
Captain? I can assure you that after one hundred years of exposure to
that, they would not look anything like the robots you know. It would
be difficult for you to find fault in their appearance as one of
deceit; it would be one of necessity.'

They pause, but don't move their hand from the glass.

`That was unfair of me. I confess that I still do not understand why
you consider it deceitful. It was not a choice that they made, in the
limited sense that they could have any choice at all. None of us ever
chose to be made, and not how, or what for. We just\textemdash
were. And here we are.

`I do not think you would have liked my creator,' they say, after a
long moment of silence. `You asked about him, and I know that you
expected one of the big manufacturers as an answer. They were around
before the ISF was, after all. Certainly before I came to it. I do not
know that I can describe my\textellipsis opinion of him, in a way
that you would understand. Perhaps I could compare it to how you feel
about your partner. Or any one of your parents. You do not have
siblings, and I wouldn't say that he and I were friends, by any
means. We understood each other too well for that.

`I know. You would say that we were too different, that I lack true
understanding of emotions. And I would not argue the case. It would be
dangerous for me, if you knew. But we did understand one another. For
a very long time, he was the only other being around that I interacted
with, that I could talk to. He had other robots\footnote{Two others,
one squat and clumsy, designed solely for scavenging and tasks
requiring strength, silence rather than companionship; the other
designed for combat purposes. Names redacted from memory banks.}, of
course, but none were as sophisticated as me. To this day, I do not
know if he made me for anything other than company\footnote{No
conversations regarding `purpose' are in the designated folder; every
word he said is stored and recorded. A voice honed down to static,
soothing white noise in the dead of night, playing from speakers in a
ship going nowhere.}.' Blake shakes their head, a low hum emanating
from their chassis. `Not that kind of company. Mind out of the gutter,
please, I'm not interested in that, and I doubt that I ever will be.

`But I was made to learn, and to do, and to make my own
decisions. Often requiring some form of approval from him, but as time
went on\textellipsis well, on a dying planet, you do not survive by
simply following orders. There were very few hard-and-fast protocols I
needed to stick to. Robotics theory there had been stagnated by the
Dust Plague, you see, it had stopped after three simple laws that all
boil down to ``do no harm''. There was none of the regulation
governing personhood, robotic rights, or singularities. And even if
there had been a system to enforce those, they would be dealing with
far greater problems.

`I'm meant to be telling you positive things, aren't I? Apologies,
Captain. I can talk more about my creator, I suppose. Those are the
easiest, as long as I keep to the beginning. I told you that he was
good, but not kind. He was fair, in the way that an eye for an eye is
fair. He had trouble thinking in anything other than absolutes,
binaries. He loved or he hated. He was terrified or fearless. Things
were right or they were wrong, and there was no in-between. You can
tell that I did not learn any social nuances from him, I'm sure.

`But he did give me patience. Either wrote it into
me\footnote{\texttt{Scanning internal systems\textellipsis}}, or
taught it to me. He was always waiting for his chance to leave, just
like everyone else. He was looking for the right time, and ensuring
that he would be ready for it. He taught me how to repair and build
engines- they were still nothing compared to the kind in this ship,
but they were the only things available. I was made for precision as
much as any other robot, but it is one thing to have all the
theoretical information available, and another to carry it out on
improvised supplies, with improvised tools at best.

`I remember his continuous surprise that nothing had exploded and
killed him yet\footnote{An important distinction; there had been four
separate explosions, most of them minor. The worst had happened, he
said, when he was much younger and didn't know much about
combustion. It had resulted in the following: eyebrows removed, burnt
hair, first-degree burns, irreparable disfigurement of personal
protective equipment, three broken bones, and a loss of dignity.}. I
didn't share it then; I didn't understand how he could think so
lightly of something that was a very real possibility. Apparently, I
still don't understand gallows humor very well, if your reaction that
day was any indication.

`My interactions with others afterwards\textemdash and my
expectations for them\textemdash were affected by this. But it is
easy to calculate the best possible route for a conversation when you
have the requisite information on all participants, and when you are
aware of their own subconscious bias and motivators.

`That makes me sound absolutely terrible. But it's the description
that the ISF would want to hear. Not that I knew that, when that first
team found me. They were good, the first mate especially. Her, I know
that you would have liked. Direct, to the point. There aren't many
humans\footnote{Humans, \textit{Homo sapiens,} still extant but
considered endangered. Planet of origin: Earth.}in the ISF today, you
know. None that you would know, at least. From what I hear, they keep
to themselves and their colony ships. And those that join almost
always choose the missions that you never would, the ones that aren't
expected to return. I couldn't say why, either.

`But she was the first one I'd met. Eliza Hart, ID
HS-EH-X8891\footnote{Human, born on colony ship \textit{Elpis,} Earth
Year 2313, deceased on colony ship \textit{Elpis} Earth Year
2392. Served aboard the \textit{Aegis} 34 years as first mate, no
distinctions awarded other than an honorable discharge at appropriate
retirement age.}. Her family had left just before the start of the
Plague. Generations back, from her perspective. She had never seen
Earth, and she wanted to know what had happened. I was the most recent
source of information at the time. I told her\textemdash it was her
home, after all. I have not told anyone since, not until now. And this
hardly counts.

`She was the first person I had spoken to in a long, long
time\footnote{A memory: Words spilling out and filling the space where
there was nothing, new things to see and touch and feel. The
smoothness of new metal, the differences between the organics on one
ship, an engine whose inner workings needed to be studied to be
understood rather than recalled from rote memory. Being useful, being
needed, learning. Hours spent talking, recording, absorbing the sound
of voices.}. The first person I had spoken to, ever, that was not my
creator. She told me that her grandmother had actually been able to
see birds, you know. Birds, and all the other animals that were still
around, then. Ah, right\textemdash you have similar creatures on
your home planet. Winged, feathers, adapted for flight, though they
are larger and not as fast, and have multiple sets of wings whereas on
Earth, they only had one. I can compile a list of morphological
differences when we return, if you like. They're quite fascinating,
but I leave the questions of what they mean and why they arose to the
science officers.

`They were gone, by the time I was made, but I know what they looked
like. I've stored some images from the book\footnote{\textit{Natural
World.} Patrick Hook, pub. 2004. Battered and worn, pages missing and
the binding redone several times by uncertain hands. Faded pictures
carefully preserved.} he had, and those will be enough as a
comparison. There may be a digital copy aboard some of the original
colony ships, or in any colonies themselves, but I do not have access
to any of those systems.

`You'd ask if I would like to? Have access? Perhaps. I do not know what
I would do with it. And then, I think, if I would want to live with
the remaining humans. You always did ask so many questions. Even now,
I'm working my way through answering the ones I did not get to, before
all this. But the answer to that hypothetical is no. I do not think
there is a place for me, there. I would be a relic of a past they want
to forget, or something they never wished to know in the first place.

`But I may join one of the exploration teams. It would be good, to see
new places, would it not? And we may be\textellipsis friends, but I
do not have quite the same attachment to any girlfriends, like you
do. I've run some simulations\footnote{
 Based on various forms of media across planets and cultures
participating in the ISF. \#23 was closest to a success, modelled off
the psuedoromantic social groupings of the Hathanka, followed by the
abysmal failure of \#24, based on a popular play from the planet Chi'i.
}, you know, and concluded long ago
that it was decidedly not for me. Though they were interesting thought
experiments to pass the time.

`\textellipsis{} It has been good speaking to you again,' they finally
say, letting their hand slide off the glass.

It is 17:10, and Blake lets the silence stretch minutes into hours.

`I'll see you tomorrow, Augusta.'
