Good to see you, how are you today?

You may be feeling a bit uncertain, so let me assure you that
everything will be fine. This is a simple and well understood
procedure that has been undertaken many, many times and we have an
outstanding success rate, and always a positive outcome.

Not to worry, no questions are stupid.

Please ask whatever you wish and I will of course explain things to
you as we go along.

Ah yes, how does it work?

The cap here is fitted with many little acoustic emitters that are
capable of focusing down to a tiny spot as small as a grain of sand,
at any place we chose within the head.

The emitters can also operate as receivers to measure the reflections,
so we can dynamically switch modes and build up a very detailed
representation of your head.

For convenience we have asked you to remove any bulky clothing so you
can put on this smock which is just to keep everything tidy and make
sure nothing catches on anything as you get into or out of the chair.

The pedestal is indeed a bit awkward, so the attendants will help to
make sure you are comfortably seated.

The arm and body straps are just to ensure the head is stable.

The focus point is very precisely targeted and dynamically controlled
so don’t worry about small movements like blinking.

We are going to do a preliminary scan to characterise your cranial
topology, this is to calibrate for the procedure to ensure optimal
parameters to take into account the varying bone thickness and
density.  The sounds in your head?

Just like a short bust of music, the tones are just beam overlaps as
the scanning patterns fold around themselves.

The calibration is complete and the system is processing a
personalised treatment program, it will only take a few moments.

You may be feeling a bit flushed, there is a small increase of
temperature around the treatment site and that can sometimes be felt,
it won’t be uncomfortable and will pass in a few moments.  Yes, the
treatment is complete.

Sorry, didn't you realise that the whole process would only take a
short time?

As I said, this process has been used many times and is highly refined
and quick to turn round, which is good for everyone as it minimises
any anxiety.  How are you feeling?

Happy.

That is good.

You will no longer suffer personal or social anxiety, or the feelings
of distress at not fitting in or worries about your job performance or
security.

Yes, indeed, you will always be happy and furthermore no longer
troubled by worries about the social ills of the world.

This is all for the greater good; another positive outcome or, as we
like to say, a `win-win' for both The Individual and The State.

Thank you.

Have a nice day.
