\newenvironment{flashback}{\em}{}
\newcommand{\varending}[2]{\textbf{Ending #1.} #2}

\begin{center}
\textit{If you expect to read a story about a hero, skip these pages
right now.}
\end{center}

\hsep

The amount of chocolate in my stomach is astounding. The control room
in my spaceship, my beloved Sanitar-150B, is heating up to melting
temperatures. The alarms are piercing all of space and time, but the
past version of me is probably blocking out the noise with some rock
music blasting through her headphones, screaming out the words to
\textit{Black Wedding} and still making the same awful decisions. The
combination of my stomach churning, the heat, an
alarm-induced-migraine and sour regret send me into a panic cycle. Oh
no, this is a serious one too. The hallucinations begin and all
control is lost.

\hsep

\begin{flashback}
`What does the B in Sanitar-150B stand for?' Violeen asks
as she sticks her pretty head through the pilot cabin entrance.

\emph{`Badass,'} I offer, while trying to concentrate on the control
panel covered in chocolate wrappers instead of staring at her denim
skirt riding up as she tries to push her legs through the narrow
opening.

\emph{`Bitch} would be more suitable, knowing you,' she cackles,
finally squeezing herself inside.

Something or some\emph{one} clunks in the back of the spaceship. The
cooling pads burst open above me and the scalding liquid pours out
like a firefall I've just passed three planets ago. My antimatter
shieldgun activates delaying the burning of the witch, but it doesn't
stop the panorama window from fogging up. I gaze at my
reflection. Imagine a white wall staring at a mirror. The feeling it
leaves you with\textemdash that is what I am feeling right now.

A white wall shatters. I storm the house in a blur. I hear screams,
but I am in my happy place. A professor calling the liquid state a
`wet state'. The core of an apple, slowly oxidizing in my hand. A man
falling asleep in a conference and asking the presenter a question to
guiltily cover up that he was not paying attention. The warm purring
of a bus. A yellow car posing as a hotel on wheels. I open my eyes to
an aftermath of a slaughter, the whiteness replaced with blood
red. It's okay, I tell myself. I am a Sanitar. They were a disease
with no cure.
\end{flashback}

\hsep

I was a disease but I found my cure. Unfortunately, she is currently
the Schrödinger's cat at the back of my dingy ship. The cabin goes
dark and only the glow sticks clumsily taped to the floor illuminate
the space.

\hsep

\begin{flashback}
For the first time I am enjoying my assignment. The club is crowded,
but there is enough space to violently thrash my limbs around with the
bass reverberating through my body in tsunami waves. I know I am not
the best dancer, but I need to attract her attention somehow. The EDM
song changes to a slow indie tune. The change of beat throws me off
balance and I feel drawn towards the small private garden outside of
the club. I'm breathing in the cold Halean air and suddenly there is a
hand on my shoulder, a gentle touch that I wouldn't have sensed if not
for the neon green glow stick wrapped around her wrist that casts
unnatural light upon my chest. I'm sure my heart is still beating to
that EDM song just because this is the only exercise I've done in a
month. The hand with a glow stick is attached to a bare shoulder and
the shoulder is adjoined to a blemished neck which in turn is
connected to objectively the most beautiful head I've ever seen. There
is nothing wrong with appreciating the beauty of the specimens of the
same sex, I tell myself. Too bad I will probably have to kill
her. About 80\% of my assignments end up in a bloody mess. The
beautiful lips on the beautiful head now appear to be
moving.

`\textellipsis{} noticed you were dancing like a possessed person and
decided to teach you a few dance moves to save you from further
embarrassment. I'm Violeen,' giggles the creature. I have never heard
a voice this crystalline. Snapping out of my daze, I pretend to be
offended:

`Alixe. At least I was moving. Last time I looked in your direction,
you were soooo engrossed by the chocolate fountain, I thought you
would start making out with it.'

She erupts in giggles again.
\end{flashback}

\hsep

The altitude drops and my navigation A.I. announces that we are
approaching the atmosphere of Hale. I feel paralyzed by the artificial
air, the cabin is closing in on me, and all I hear is the song
\textit{Kamikaze,} with the chorus in a permanent loop.

\hsep

\begin{flashback}
`Attention cadets!' The electric voice penetrates the bleak
dormitories. What a lovely alarm clock. I have been in this shithole
for a year now. It feels normal. The commander's droning voice almost
puts me to sleep. Until we learn that any mission has to be completed
even if it results in your death. Today's lesson will be tested
tomorrow. Ten people will be assigned to their deaths randomly. They
\emph{will} die. If they succeed, they die as idols. If they fail the
mission, we will have to sanitize them. Anyone at the academy who
cannot fulfill their assignment is a parasitic creature. And every
Sanitar's duty is to keep the fleas away. Feelings are like fleas
too. You cannot catch them if you aim to survive. Clean of fear, clean
of love, clean of the dirt that floats in your mind just before you
fall asleep.

Except what if you don't fall asleep? What if you have
to hide every flash of panic in your eyes during the day and fight the
vivid nightmares that ambush all of your senses at night, leaving you
tingly in the worst sense?
\end{flashback}

\hsep

The hallucination of my childhood at the academy restores sharpness to
my thoughts. I've learnt to suppress my fears back then out of fear
that others would notice. The pilot's cabin was the only place where I
was ever truly alone and could let the usually dark feelings float
around me. At first it would start off with me crawling into the
cabin, the hot air so dense that I felt like drawing in breaths of
salty, boiling water. Then I would state my fears one by one while
strapping myself into the pilot's seat. I would imagine bubbles coming
out of my mouth with my feelings trapped inside. And then I would
accelerate the ship so rapidly that the bubbles would hit the back
wall of the cabin, bursting open and their contents would melt away in
that metallic tasting soup that was the cabin air. Everyone at the
academy praised me for being so brave and determined, rushing out to
complete my missions.

I haven't done this ritual today because it is the first time I am not
flying alone. Maybe that's why things have gone so wrong since
then. My shieldgun is already flickering as the spaceship is
desperately trying to use its last energy resources to stabilize
itself. I close my eyes, and squeeze a heavy metal sphere that I am
holding in my hand. There is nothing I can do anymore. The glow sticks
fade out.

\hsep

\begin{flashback}
Vantablack curtains are abruptly pushed to one side. They know. I
spring up from the bed, enveloped in my shieldgun. I can sense the
electromagnetic field that contains it trembling and
flickering. Violeen flinches at the sight of me, and panic numbs my
body toe to head. They don't know, but I am going to lose her anyway.

A lame `I can explain' escapes my lips. Strangely, she seems relaxed
now, as she inches towards me, my shieldgun disabled the moment I saw
her wine red hair and the disapproving look.

`I've found out you are a Sanitar two weeks ago,' my girl whispers
cautiously. Now it's my turn to flinch. `Why didn't you say something?
Or run away? Or kill me when I was sleeping?' I yearn for answers.

`Well, if I did, I'd have the whole fleet running after me. You're
actually an evil I can stand. Barely,' she sticks her tongue out at
me. I cannot comprehend how can she be this calm in a situation like
this. `Besides, I have a feeling you are not going to kill any more
innocent people. Now that you know you have been killing your own
kind.'

Well, she is wrong. I am not going to kill any more people because
that would mean losing Violeen forever.

We are both selfish, as I find out later, when she tells me her
plan. Running is not an option. Hiding? Violeen has been hiding her
whole life and that still brought a hound dog hungry for blood on her
doorstep. The hound dog has been tamed and agrees to sacrifice the
whole universe for one negligible probability to save the other
countless alternate ones preferably with her in one of them. We
objectively decide that this one is doomed. Not to mention it is a
threat to other universes too with all the spec-ops `Doctor' squadrons
roaming them to find the ones where people are allowed to love without
fear and destroying them with a press of a button.  We both sound
crazy shouting ideas at the top of our lungs in our soundproof bedroom
and the plan is done within an hour. Chocolate consumed in handfuls
for courage. `What does the B in Sanitar-150B stand for?'  A long kiss
before she disappears to the back of the ship to man the gamma
lasers. On the way to the Centre for Interverse Warfare hundreds of
Sanitar ships start tailing us. I can hear Violeen cursing on the
sound system. Until I can't. The first energy pulse disables our
communications. The second heats up the whole ship and it is
excruciating, considering that without any external help the cabin
already feels like a pot of boiling soup. The third attack is
chemically induced hallucinations. So here I am.
\end{flashback}

\hsep

I manage to peel my eyes open hoping to resist the delirium for a few
more minutes. Sanitar-150B is gliding at such a low altitude that I
can see the peaks of the Center for Interverse Warfare fortress. So
close that I could touch them with my hand. Instead of touching the
cold stone walls, I muster all of my strength and punching my fist
through the panorama window, I throw the metal sphere towards the
looming tower of evil. I just hope Violeen is alive and that she has
activated the teleportation cube. The sphere loses its metal casing as
it hurls through the air and the sound deafens me as it impacts the
wall.

White silence.

\hsep

\begin{flashback}
You can choose to stop here. In order to find out more, you have to complete this mandatory personality test:
Which character was your favourite?

\begin{itemize} \itemsep-0.5em
\item {\normalfont Alixe.} Proceed to \textbf{Ending A.}
\item {\normalfont Violeen.} Proceed to \textbf{Ending B.}
\item {\normalfont I hated them both.} Proceed to \textbf{Ending C.}
\end{itemize}
\end{flashback}

\hsep

\varending{A}{White silence gradually transforms into the dormitory at the
academy. My heart sinks once I try to remember Violeen's face and it
slips out of my memory like a swirl of mist. That does not mean I
cannot find her in another universe, better than this one. I am
stealing Sanitar-150B tomorrow, I tell myself, stuffing my pockets
with chocolate stolen from the canteen.}

\varending{B}{White silence in my hospital room. Violeen is lying next to
me in a bed with floral bedsheets. I still cannot believe we destroyed
a universe.  The teleportation cube worked. We set off the
anti-universe weapons with our little makeshift bomb. The thought
makes me throw up all of the `courage'. Chocolates that were made in a
universe that does not exist anymore.}

\varending{C}{White silence. If a universe falls in an infinity of universes and no
one is around to hear it, does it make a sound?}
