The conference was on. Mr Monday Thompson turned to the screen and
clicked on the video that appeared on it. Now, he was watching one of
the speakers list the reasons for his home planet, Earth, to be
catalogued as Number One in the Universal Cosmographic Atlas. The
recording lasted for about an hour, and after it ended, Mr Thompson
did not hesitate to click on the next clip in the list. In this video,
another speaker listed the reasons for his home planet, Earth, to be
catalogued as Number One in the Universal Cosmographic Atlas. The
video was identical to the previous one, and Monday got bored very
soon.

Mr Thompson lifted his eyes off the screen to observe the conference
room he was in. He saw a large, round and glaringly white table. There
were twenty-five chairs, evenly distributed around the table, and on
twenty-four of them sat twenty-four identical middle-aged men with
greying black hair, wearing identical striped suites and identical
horn glasses. The twenty-fifth chair was occupied by Mr Monday
Thompson himself and he knew that he looked exactly like the rest of
the people in the room, each and every of whom was also called Mr
Monday Thompson. The hall was radially symmetric, which meant that
there was no absolute system of coordinates to refer to,
though \emph{the} Mr Thompson had quickly worked out his way about the
problem by numbering his counterparts from 2 to 25 in counterclockwise
order, calling himself Number 1.

It was only natural that the first of the twenty-four introductory
videos Monday 1 watched was that of Monday 2. Monday 3 was now frozen
on the screen of his personal computer, whereas the clips made by
Mondays 4-to-25 were still waiting to be seen. There was no need to
watch them all, as Monday 1 deduced that they would be the same as the
two previous ones, and even worse, the same as the video he had sent
to the other twenty-four computers around the table. This was
insane. He stood up from his chair, and announced:

`I am sorry to interrupt, but I think I need to leave the hall to
reflect on my strategy in the future talks. I hope to see you all
tomorrow', he said, and headed to his personal quarters. As he made
his way to one of the twenty-four doors leading from the hall, he
noticed the other Mondays say the same words and head back to their
rooms, too. At least he was not the outlier.

\hsep

Back at home, and before it all began, generations puzzled over which
conditions could possibly give rise to sentient life on a given
planet. On the turn of the second and third millennia, right after man
first went to space, there were millions of optimists, adamant that
First Contact is just around the bend. Just a little longer, and the
beings from outer space will invite humanity to join the ranks
with all other developed species in the Space Federation, or the
Galactic Empire, or whatever best suits your political beliefs. But
years passed, and no one came to visit, nor did they respond to the
endless messages we kept sending into the equally endless void.

Then, just a couple of decades after, the answer to the `Where's
everyone?'  question was found at last. Using most advanced
mathematical models and almost half of the planet's computational
resources, the Extra-Terrestrial Intelligence Research Group finally
proved that with an overwhelming probability, only the \emph{exact}
conditions found on Earth in conjunction with the \emph{exact} series
of events that had happened to our planet could foster a civilisation
as advanced as the humanity.  This answer was somewhat sad, but also
comforting, as at least one could stop worrying about the chance that
murderous aliens are coming to the Solar System to enslave the poor
earthlings for eternity. What is more, there was now no chance of a
so-very-awkward situation of coming to colonise a planet already
inhabited by the locals who actually mind your arrival a lot. In the
centuries to come, the model only got more accurate, and science
fiction, now stripped of its vital wow-that-totally-could-happen
element, only got more boring. The answer was always the same: no
other combination of circumstances could ever allow an interstellar
race to appear.

What everyone failed to notice, however, was the simple observation
that in an infinite universe a certain series of events may well occur
in more than one place. And the invention of the wormhole technology,
which enabled one to get to a point in the universe with the same ease
no matter the distance, solved the only obstacle to the first contact
\textemdash{} the insurmountable distance between such identical
planets.

As a result, on June 1st 5031, twenty-five pioneer ships emerged in
the very same place chosen as a test destination. All of them were
called \emph{Harmony}, all of them were piloted by Captain James Simm
and all of them came from the planet the ship's crew called Earth.

Once the excitement of the discovery was slightly dulled, the United
Government of Monday 1's Earth realised that if the interaction with
the newly found brothers in mind was to be sustained, a universal
system of coordinates was vital to prevent the very possible confusion
of arriving at the wrong planet called `Earth'. The officials were
delighted to discover that all other twenty-four United Governments
were as fond of the idea, and had even also each put forward such a
proposition themselves. However, a problem arose when everyone
insisted that they keep the original planet name, not the least in
order to honour the glorious ancestors who had done so much for the
world they called `Earth'. Quite soon everyone settled on the idea of
calling all twenty-five Earths\textellipsis `Earth', but adding a
number after that. Then, of course, everyone insisted on being Number
One.

To solve this problem, the Conference Hall space station was
constructed in the place where the twenty-five Harmonies had met,
and each Earth was to send their best diplomat to sort the issue out
once and for all. Every single one of them chose their Mr Monday
Thompson, the renowned author of the treaty between the humanity and
the AI which ran the Proxima Centauri colonies before going
rogue. With such achievements, he was the obvious first choice when it
came to talks with an entity as unhumanlike as non-terrestrial
intelligence. Had they known that here, the problem would be exactly
the opposite\textellipsis{}

In his empty room, Mr Thompson moved as if he was about to sit down,
and in a finger's snap a quite comfortable armchair materialised right
under him. His neural signals had given away his intentions to the
housekeeping AI, which could restructure the matter itself to cater to
the user's needs. In a similar fashion, a Martian tobacco cigar and a
pocket-sized edition of \textit{Jane Eyre} appeared in Mr Thompson's
hands. Usually, Monday changed his own physical shape when relaxing,
opting to discard his legs, which tended to itch annoyingly, thus
ruining a would-be good rest, and sometimes modifying his fingers into
something more tailored to turning the pages of his favourite
book. However, tinkering with human flesh was illegal in some colonies
and, unsure of which laws (if any) are in place on this station, he
reasonably decided that it was not worth the risk.

And yet, he could not take his mind off the situation that was seeming
more and more desperate. Monday 1 stood up and launched into a
restless walk around the small cubicle, but no way to escape the
current ideal stalemate came to mind. All Mondays had the same way of
thinking, so every brilliantly structured argument the ambassador
could put forward was equally likely to come to mind of any other Mr
Thompson, and every rebuttal of the others' reasonings could be
applied to his own claims. In a situation where everyone is in the
same position the game is a zero-sum one by definition and no
trade-offs are possible, while achieving trade-offs is the meaning of
diplomacy… Was the solution not a diplomatic one at all?

With all the mind-reading sensors around, Monday 1 was very careful
not to develop the dangerous idea any further, not until wishing up a
pile of tin foil and making himself a cap out of it\textemdash of
course, in theory the system could easily penetrate this protection,
but the Tin Foil Cap Rule, passed hundreds of years ago to address the
public's privacy concerns, guaranteed most severe punishment to anyone
who designed a neural interface with such a function. Of course, the
very fact of ordering the foil meant that Mr Thompson had something to
hide, but sometimes making clear that you're up to no good is still
better than letting know what this no good exactly is.  With all
precautions taken, Monday 1 set his train of thought going, and soon
thanked himself warmly for having concealed his consciousness from the
system, as the concocted plan was as out-of-the-box as violent. The
idea admittedly had some serious ethical implications, but Mr Thompson
was already experienced on transcending human morality standards
\textemdash{} he developed the skill when trying to think like an AI
in order to understand the thinking of his Proxima Centauri
counterpart.

All he had to do was kill one of the other Mondays: the twenty-five
men had identical biometric data, and once the two of them start
fighting, the system would be unable to tell the attacker from the
victim in a cacophony of adrenaline-driven thoughts. Once the scramble
is over, the assailant would assume the other Mr Thompson's identity,
erase the recording, and then claim that Monday 1 was killed by
him. The Commission would surely be shaken and grant the victim's home
the honourable Number 1 as a compensation for the loss. There was a
non-zero chance that the murderer would get executed or worse, but Mr
Thompson had no close friends or relatives, while the prospect of
leaving such a remarkable impact on the history of the entire Universe
was worth the sacrifice.

Confident in his success, the diplomat entered the Conference Hall and
carefully made his way towards the room of the Monday whom he had
given the number 4 this morning. The cold night lighting of the hall
flickered ominously as he snuck into the apartment, trying to maintain
a peaceful look but ready to launch into attack as soon as the door
closes.

The tension in Monday 1's body was released as soon as he figured out
there was not a soul in the room. \textit{Even better}, thought the
negotiator, \textit{now I can pretend to be the resident who's come
back to his room, so that when I attack, the case for the supposed
Monday 4 being the aggressor would be even stronger.} He soon assumed
an ideal position for an offensive against the victim coming through
the door\textellipsis{} And then nothing happened, and this nothing kept
happening for at least an hour.

Mr Thompson even considered returning to his room and abandoning the
scheme altogether but was prevented from doing so by a thought that if
he could ambush his fellow negotiator then one of his counterparts
might well waiting for Monday 1 himself at his home.

There was no way back. The diplomat sighed and adjusted the tin foil
cap on his head, anticipating the long and tiresome night he was bound
to spend.

\hsep

Monday 1 was awoken by the loud sound of the alarm filling Monday 4's
room. He eventually had fallen asleep on his post, but luckily for
him, the real owner of the room never returned. Though at first Mr
Thompson was startled by the high-pitched humming, specifically
designed to fail-safely bewilder any human being to the point of
shaking off the deepest sleep, he quickly came to realise the
implications of his position. Letting anyone know that he was not
Monday 4 could uncover his last night's intentions, so the only way
out was to keep pretending to be the room's rightful owner all the way
through the talks. One thing not to worry about was the chance of
exposure by the real Monday 4, since him staying out of his quarters,
just as Monday 1 had never returned home, likely meant that he had a
similar malignant adventure in the night.

Monday 1 frowned at the idea of having to defend the competitor's
interests throughout the talks, but just as he sat behind his
not-to-be-victim's table, the diplomat realised that he didn't have
to. Why not play the situation to his own advantage, and claim that
Monday 4's home world, understanding the necessity of a compromise,
renounces its claims to the Number 1?

The conversation was, similarly to the past day's talks, conducted by
exchanging the videos between the Conference members (normal-life
talking meant someone was to make their point first, and was
unanimously declared unacceptable as it could rig the situations in
the first or last or whatever speaker's interest). This time, however,
the clips were much shorter and hardly lasted more than two minutes.

Monday 1 scrolled through the feed, and suddenly couldn't help
laughing – every single negotiator had become miraculously amenable
overnight and decided not to contest for the Number 1. Moreover, the
videos were absolutely the same once again.

This suspicion had crossed his mind before, but then he managed to
calm himself down, reasoning that yesterday's arguments were
pre-recorded, and it was only natural that his fellow diplomats
followed the same logic when filming their clips. However, this time
the videos had been made at the same time, yet they were
indistinguishable once again\textemdash and even worse, he could
hear the other Mondays' laughing in perfect unison with himself.
Twenty-five Mr Thompsons rose up to their feet and started walking
around the hall anxiously, then the twenty-five of them exclaimed,
`Everyone wanted to kill the Monday living four doors to his left,
everyone pretended to be the victim who never came and now everyone
wants to renounce the claims on his behalf!'

The pace of twenty-five pairs of feet accelerated.

`But that's not even the worst thing\textemdash we're talking now
and it's perfectly synchronous! It's not about coming up with the same
ideas, it's about coming up with the same ideas at the exact same
time!  Effectively, we are a single person just copied and pasted
twenty-four times!'

Then, the twenty-five Mondays came to a stop. They stood still around
the table, all facing the hall's centre and thinking about the
conclusion they'd come to. It all seemed too disappointing to be true,
and also\textellipsis ungrateful towards the generations of people
who dreamed about the first contact, especially those who never
stopped believing even in the thousands of years between the time
mathematics proved them wrong and the moment the reality shattered the
inexorable model to smithereens.

`But\textellipsis you don't consider your reflection in the mirror an
alien, do you? There's nothing a mirror can give you that you don't
already have, even if you could reach out through the looking glass
and take an object from there, your reflection will by definition
fetch the object's real-word prototype from your side, so the total
impact of the action is zero. This first contact does not, and will
not, result in more resources or new ideas for any of the sides; it is
simply pointless!

`And our negotiations are just as meaningless, for there is simply no
need either for a universal atlas nor for any further interaction
between our civilisations\textellipsis We have to return and explain
this once and for all. Hopefully, this'll save the others from the
intimidation we had to go through.'

Each Mr Thompson wondered if he should bid farewell to the others, but
then decided that there is no point in saying goodbye to your mirror
image.

The twenty-five Mondays turned around and went into the twenty-five
rooms, whose twenty-five AIs detected the intention to leave and
disintegrated the opposite walls reveal twenty-five identical boarding
bridges. In an hour, twenty-five spacecrafts took off and made a
wormhole jump to the twenty-five Earths.

\hsep

It took some incredibly hard work, but each of the negotiators
eventually managed to explain to the people at home why the other
Earths did not matter. The Twenty-Five Mondays' Conference had indeed
turned out to be humanity's last encounter with alien intelligence,
but a few generations passed, and people got distracted from the
disappointment, too busy exploring and colonising the endless Universe
that lay in a different direction from the other twin Solar Systems.

What remained unnoticed by everyone was the fact that, in the bitter
excitement of the discovery, the negotiators had confused the doors,
and each Mr Thompson actually arrived not to his home planet, but to
the Earth of the Monday who initially sat one chair to his left.
