\emph{This story was written collaboratively, where each writer added a paragraph based only on the previous two paragraphs and details they had previously written into the story. }

Captain Spectacular gazed out from the window of the Galactic Flagship. The Grand Armada was lined up in ranks before her, gleaming like little snowflakes on a starry night. She pulled the communicator to her lips and uttered the words of the Great Emperor to be heard by all the Star-Commanders of the fleet. 

“Alright you leeches, hopefully your bloozes are all in order. We need to show these cussing leeches that they can’t mess with the fricking Empire or those dolipods won’t know what shlreeping hit them. Make your custardly emperor proud you shinky drillbits.”

“62  billion kilometres away”, Shane Carr woke with a start. `No more late nights bashing on the screenplays’ he thought to himself. Carr had never been the ritualistic type, but it had become something of a morning custom to start the day by smacking the alarm clock across the room. `No more late nights bashing anything, ideally’, continued the train.

Nursing his headache, Shane downed a shlreeping bloozeburger. He wished the alarm would stop screaming. Frankly, the train wished it didn’t have to deal with such a violent dolipod aboard.

Snorting, bellowing its way through the carriage, the dolipod cried in fury at its cruel confinement. Its ruby pinpricks of eyeballs focussed on the sweeping landscape passing – a softening of stance, fury cooling. ‘Mother…’ it rumbled as it gazed, lost in memory. 

As the landscapes were changing, Shane was becoming more and more sleepy. After several hours of sleep he ended up in Soviet Russia. He got off the train in fancy leather jacket, high heels and pink dress. He had no idea what happened to him. He felt as if someone gave him drugs. People on the street were giving him odd looks. Someone called for the policeman; the Russians were disgusted by Shane. They yelled, ``Send Shane to the Gulag!'' At this point, the whole world started to drift apart and Shane lost his consciousness.

Shane had a serious case of narcolepsy apparently given how much time he spent unconscious in this story. You see, Shane, our sleepy misadventurer, found himself in a precarious situation, a Siberian Gulag being said situation. Our dear Shane woke up to see a purple dinosaur squatting up and down over a Call Of Duty\textsuperscript{tm} player, holding a Barack Obama action figure in his mouth while shouting “Harambe our saviour!” over and over again. Shane should not have accepted the mushrooms his captors had given him, and they were soon to have him babbling all his darkest secrets about the secrets of nuclear fusion, top secret missile systems, and the bra he stole from his crush in the 6th grade.

Upon the revelation that he stolen a bra from Mary James all those years ago, his captors visibly perked up. They began to question him about the specifics of how and why he stole it, where from, what colour it was, and so on for many hours. After he had told them everything he knew, the only thing he remembered before he woke up back in his cell was an image of Barack Obama and the taste of cherries.

Shane waited another year before the courts allowed him to take parole. In that time, he honed his karate skills and became an ultimate fighter. There wasn’t a single piece of wood he couldn’t break with his high-jump kick. When he got out, he decided to enroll in lumberjack camp to earn an honest trade roundkicking trees to shreds.

The Captain woke from her crypto-sleep with a jolt. What in the Heron’s name was a ‘Shane’, and how did one individual consume that many psycho-gens? Alas, that was the fleet; the frontier had never been kind to ideo-grunts. Thankfully, it was nothing a caffineoclast wouldn’t fix. Emperor’s mercy on anyone who tried to make it out here without that crutch. Everyone needs a little help sometimes. 

Donning her caffineoclast, Captain Heron shambled out of the bubble-pod, confident in the knowledge that the neuro-hyperwaves were unable to oscillate past the golden crown. She shuddered a little, the mago-rats were out in full force this morning.

The voice of her emperor, Sha-nei the Sumptuous, echoed down the halls of the refactoring lab. The mago-rats chirped, ears rotating to find this new sound, turning to the small box in the centre of the room which had begun to sprout out prehensile feelers and appraise the surroundings.  A single stray rat ventured too close. As Captain Heron watched, the tendril struck – plunging into the side of the rat.

As the tendril flung itself deep into the mago-rat’s heart, it let out an almighty squeal that would have made any normal vat-born flinch in terror. However Heron was no mere vat-born, and so looked on with eyes hardened by the Great Warp War as was her duty.

Meanwhile on Earth, Shane was really getting into the lumberjack business. He had gotten up to punching 1,000 trees into paper a day, and could use a shovel to shave chippings directly into printer paper. Suddenly, a rippling sphere appeared before the tree he was about to knee right in the branch. He heard a thrill voice from across the universe calling his name: ``Shane! Save me! Enter the portal before you and help us defeat Emperor Sha-nei!''. Shane didn’t have anything on that night so he said, ``k 1 min m8'', and jumped in.

He fell. And fell. Coruscating colour whipped around him as the tides of infinity lapped at his mind – the cackling laughter of Sha-nei sawed across his earnubs: \emph{FOOL! Did you really think it would be that easy?} Shane realised Sha-nei was a cheap bastardisation of his own noble name, and that there could only be one. Jaw tightening, he knew this would be the final confrontation. The portal ending approached, and he fell six metres onto solid concrete; the world went dark as his femurs shattered. He was lucky.

Shane had landed on his back and somehow the collection of assorted Celtic age femurs he kept in his backpack for good luck absorbed the brunt of the impact. He got up and looked around, noting the eclectic mix of architecture styles. Just as he got his bearings, he heard an authoritative, yet nasally voice out of the cloudless sky. “The Museum Planet will be closing in 10 minutes. Please make your way off planet, as trespassers after this time will be vaporised.”

The elder librarian, she surely would follow through with the threat. As he prepared to flee, he caught the eye of a hooded figure. It was Sha-nei, the scrumplous blelper was attempting to flee on a scabrous crawler.

Shane started throwing whatever he could pick up at Sha-nei, a fire extinguisher, the preserved teeth of the great competitive eater, Pacamen, a gigantic modern art sculpture made out of Styrofoam, but Sha-nei ran too fast and boarded the scabrous crawler successfully. With only five minutes left, Shane saw a vehicle. It was small, ancient and falling apart, and the owner was the most putrid smelling creature he’d ever met, with big nostrils and distressingly disturbing, tiny eyes on what would be a human’s chest. He had no option, and boarded it. ``Where'd ya wanna go?'' said the creature. Turns out he was a Space Uber driver. ``Umm, Earth?''

``With the nitrogen and oxygen based atmosphere? You mean all the way in the bleezing Solar System?'' Shane nodded aggressively and the driver seemed to understand. He floored the accelerator like he too knew the intensity of the situation. Shane looked to the back. "Sorry, but I really need to borrow your plasma cannon”. Without waiting for a reply, Shane immediately got into action; he powered up he cannon, aimed it, and fired at the crawler. Instant explosion and smithereens. Shane finally relaxed and felt as if his problems were at an end. ``Rest in pieces...''

The vehicle slowed to a stop, and Shane’s driver turned slowly. ``Hold on a minute. I let a stinkin’ head-eye into my shuttle and this is how you repay me? I may not care for Sha-nei, bu’ they got a right to freeze peach too, ya know!'' Shane watched the driver awkwardly, his hand drifting towards the micro-hatchet he stored on his left ankle. The horrid smelling being continued, so at a time deemed dramatically appropriate to interrupt the monologue, he struck. Commandeering the craft from the quickly-decomposing driver, Shane headed for low orbit, following a trail of crushed pills and pitted cherries. As he neared his destination, a giant yellow orb with a chomping, toothless maw turned 90 degrees around the Moon and engulfed the craft. The reverberating soundtrack shook open a previously hidden freezer compartment, and as the cabin slowly filled with defrosting apricots, Shane had one last cogent thought – ``If I were back in the gulags now, I’d be drowning in free speech!”