Miguel O’Hara sighed and contemplated how far he had come. He looked over to the large building in the distance, with the words ``ALCHEMAX'' illuminating the night sky. Alchemax was the company with multiple divisions, each designing products for different consumer needs. At its head was Tyler Stone, ruthless corporate head, as well as Miguel’s father. He was also the one responsible for getting him addicted to a potent drug. Miguel was able to rid himself of the addiction, and in the process, gave himself some powers.

Ever since then, he’d taken up the identity of his idol and had decided to take up the good fight. Helping civilians, fighting crime and doing what he could to try and clean up New York city. He did good work, and people noticed. News outlets talked non-stop about him while on the converse, Tyler Stone sent a number of masked freaks to take him down. Whatever obstacles may have arisen, he always gave it his all and came out on top.

And yet . . . he was starting to wonder whether it was all worth. Was it worth stopping one criminal when several others would take their place and still be at large? Large corporations were another matter altogether; they had too much power to be overthrown by taking down a couple of thugs and breaking up some shady deals in the docks. They had too much power, and too much influence. Just some words here and there, some money sent to the right pockets, and they were virtually invincible.

There was also the matter of Miguel himself. How many times had he been beaten, had his bones broken or had bruised his body? He healed quickly sure, but was it worth all the damage and beatings he took? He was an adult in the prime of his life; plus, he was working in one of the top research facilities of the country. He could stop and concentrate harder on his work, and maybe then he could come up with a better way to help people. Heroing was tough, maybe it was the time to quit while he still could.

He closed his eyes and sighed. How long until his luck ran out? One day he could end up crippled, or worse. And what if it wasn’t him but someone he loved and cared about. One slip of his secret identity and all his enemies would be after everyone in his life. There was also the damage control. How much of New York city had been caught in the crossfire of his battles? Not just property damage but civilians too. How many people had been injured; what if one day he wasn’t fast enough, would he be able to live with himself?

“Help!!”

Miguel immediately looked up, trying to locate where the scream came from. He tapped into his heightened senses, closed his eyes and tried to listened hard. His ears found where the scuffling sounds were coming from and he opened his eyes and zoomed in to get a better look. He caught sight of some thugs who were trying to steal a lady’s purse.

Miguel reacted instantly; he leaped into the air and began to glide towards the thugs. He shot some weblines to speed himself up. Almost instantly he landed right in front of them.

Two quick jabs disoriented the two nearest ones. A spinning quick dispatched the one running towards him.

“You know you guys really suck. Picking on someone weaker than you. All for a couple of hundred bucks?”

There were only two left who came at him together. Miguel moved swift and fast; he dodged the punch coming for him, grabbed the offender and threw him into his partner. He fired off some web bullets for good measure and stared down at all the thugs groaning in pain.

“You guys better scram! Because right now, I’m not feeling so friendly!”

They all ran off while he caught his breath. Suddenly something slammed into him from behind. Miguel tensed himself until he realized it the woman he had just saved was hugging him tightly. 

“Thank you! Thank you so much!”

She sounded a little tearful, and most definitely grateful. Miguel was confused, unsure how to react. He hugged her back lightly, as much as he could hug someone who was behind him. As soon as she relaxed her grip, he leaped up and shot a webline. Five minutes later he was standing on top of the tallest building in the city.

Maybe it wasn’t an overnight process, maybe he wouldn’t be able to make a dent on the crime rate. But he could keep on trying and fighting the good fight. If he could help and provide small happiness to even one person, one day at a time, then it would be at least be something. He fired a webline and swung off; one day the world wouldn’t have Spider-Man of the year 2099 protecting it. But that day was not today; the future was looking bright. 




