Hello all, and welcome to the 43rd year of the Imperial College
Science Fiction and Fantasy Society!  I’m Matthew, this year’s
Chair-Entity, and as such it falls to me to provide a snapshot of what
we get up to.

Firstly, Books! Over 10,000 of them! ICSF has an entire library full
of fantastic fiction situated in the not-so-secretive West Basement of
Beit halls, a mere pint glass’ throw\footnotemark[2]{} from the Union
Bar. Our collection comprises great reads from all across the sci-fi
and fantasy spectrum, all of which can be loaned out to our
members. We have an entire wall full of DVDs for your viewing
pleasure, and we keep our shelves regularly topped up with all the new
releases.

Secondly, Events! Whether it’s movie marathons, bar nights, or the odd
excursion out to bookshops and cinemas, there is plenty to enjoy with
your fellow bookworms and movie nerds. Soon approaching include our
annual freshers’ welcome event, Theme Fridays to celebrate the end of
the week, and our Halloween and Christmas parties. We even have our
own convention, Picocon: a day full of talks from published authors,
silly games, and the odd bit of merchandise destruction.

Lastly, People! The library is a lovely social space where you can go
and enjoy a relaxed lunchtime.  Every weekday from 12–-2pm you are
welcome to join us as we watch some of our extensive collection of TV
shows and films. Moreover, the society is full of friendly faces ready
to chat and hold lively discussions about their favourite works of
fiction. The society is very welcoming and inclusive --- a fact I have
known ever since I accidently walked in on an EGM back when I was a
fresher.

So, if you want to watch, read or discuss Pratchett, Potter, Trek,
Who, Sanderson or more, come and find our shelves! You may find a few
new favourites in the process.
