The days are getting shorter. You've put your summer clothes away. You
take a stroll on campus, and soon find yourself in possession of a
large pile of paper. Someone has gone and printed some words onto that
paper, and here's some of what those words say:

\textbf{Page 3.}
There's a library in the West Basement, and you head there at
lunchtime. (There is someone --- there is always someone in the West
Basement at lunchtime.) There is also a television screen, and the
moving images temporarily remove you from worldly ills.

\textbf{Page 4.}
The Librarian suggests that you put the title on the request list, or
grab it on the Book Crawl, but soon you realise that the story you
want to read is not in the Library because it does not yet exist. Left
without a choice, you sit down with your favourite writing
implement. Later, you electronic-mail the completed manuscript
to \texttt{icsfwyrmtongue@gmail.com}.

\textbf{Page 6.}
You are presented with a provisional map of the near future. It
includes a Halloween Party.

\textbf{Page 7.}
On a lovely day in February with a very memorable date, you sit in a
lecture theatre and listen intently to a talk about a fantastic
topic. You watch some miscellanea get obliterated with a
sledgehammer. Your writing appears in the \textit{Picocon Fanzine},
becoming part of a mythical, forty-year corpus of artwork and poetry
and short stories and essays. At sunset, no-one challenges you to a
duel.

\textbf{Page 1.}
The College welcomes you (back) into the beginning of a(nother) new
academic year, and the editor thanks you for picking up this issue
of \textit{Wyrmtongue}, the newsletter brought to you by ICSF, the
Imperial College Science Fiction and Fantasy Society. Come down and
join us in the West Basement Library sometime, yes? It's going to be a
splendid time.
