Greetings to all living things at Imperial: I’m Matt, ICSF’s acting
publicity and events officer, and I’m here to tell you about all of
the events we have lined up in the coming weeks for you to enjoy.

Expect a torrent of events for the first few weeks of this term, with
plenty of opportunities to meet fellow fans of sci-fi, fantasy,
horror, and who-knows-what-else.  Here are some of the regular events
you can expect from ICSF:

\textbf{Lunchtime Showings} ---
From noon to 2pm nearly every weekday, the library can be found filled
with people watching various TV shows and movies in our
collection. Perfect if you have an hour to spare in-between lectures!

\textbf{Cinema Trips} ---
Come along as we go out as a group to see the latest fantasy and
sci-fi hits in cinema, with tickets often discounted for members. This
term’s films of note include: \textit{Joker}, \textit{Zombieland:
Double Tap}, \textit{Maleficent: Mistress of Evil,}
and \textit{Jumanji: The Next Level.}

\textbf{Literary Lucky Dip} ---
Grab a free book! But with a catch: the mystery books will be wrapped
up, with only a cryptic phrase written on the package to hint at
what’s inside.

\textbf{Bar Nights} ---
First round’s on us as we discuss all things sci fi and fantasy with
the refreshing taste of your favourite (alcoholic or otherwise)
beverage on your lips.

\textbf{Book Crawl} ---
Where some societies have pub crawls, ICSF has book crawls! We’ll be
embarking on a journey around some of the best book and comic stores
in London to find out what hidden gems they have on offer.

\textbf{Halloween Party} ---
On the eve of Friday November 1st, come as you are or dressed as your
favourite character to our Halloween party!  With showings of
spooky(?) singalong classics like The \textit{Rocky Horror Picture
Show} and \textit{Dr Horrible’s Sing-Along Blog,} come along for a
night of singing, snacks, and even a fancy dress competition.

That should give you a taste of what kind of things we have in store
this term. For more information about upcoming events this freshers,
see the calendar on the opposite page.
