Hello, reader! My name is Sintija, and I’m the Head Librarian this
year. Unquestionably, the essence of the Science Fiction and Fantasy
Society is our library in the West Basement of Beit Quad.

Now, whether you’re new to Imperial, or a seasoned veteran, you will
undoubtably experience the dread of seeking an uncrowded, cosy space
to have your lunch throughout the year. We offer a unique social space
open from 12 to 2 in the afternoon every weekday where you can relax
during your lunch break and bring your friends to discuss movies,
books and anything even remotely related to science fiction or fantasy
– or better yet, you can watch something from our collection of 2000+
DVDs on our TV screen. The library is often open late into the evening
and some of our smaller events happen there, with the comfy darkness
enveloping the room and friends chatting to each other, illuminated by
the screen and fairy lights.

Even if you’re not a huge sci-fi fan, you should consider dropping by:
at the start of my first year, I had not yet seen a single Star Wars
movie (blasphemy, I know) and by the end, I have not only seen the
original trilogy and the prequels, but I was also roped into a
roleplaying game happening in the Star Wars Universe. Some of my most
treasured memories from my time at Imperial were made at the
library.

I love not having to worry about buying books to read, as the library
contains over 10,000 books and 600 graphic novels, all there for you
to borrow the moment you join the society.  We have a lot to offer and
in the unlikely case of you not finding what you were looking for –
you can always talk to me or put your suggestion on the request list,
and we’ll try to acquire it as soon as possible.

I hope to see you very soon!
