Welcome to what is likely to be the first of many Sofa Ramblings
\texttrademark{} this year. (Many of the following ramblings are
likely to occur exclusively within the Sci Fi Library, especially as
February arrives).

I am this years Picocon Sofa! If that makes no sense to you at all,
then you are likely very new to this society. Picocon is the annual
convention we run to raise money for charity and for the society,
while also to celebrate Science Fiction and Fantasy in all its forms!
The Picocon Sofa is the committee member most responsible for the
convention. This year’s Picocon will be the thirty-seventh.

Although --- unfortunately --- I am yet unable to confirm a date
currently due to a room booking system that is only mostly functional
on its best days, there is some good news on the way! I plan to run
this year’s convention a little differently to normal. For starters,
the theme this year will be “Pride”: I am going to be using this
Picocon as a way to celebrate LGBTQ+ stories and creators, as I myself
am asexual and have found quite the overlap between LGBTQ+ stories and
science fiction/fantasy stories. Of course, we will have Guests of
Honour to give speeches and presentations. In previous years, we have
hosted such fabulous names as Terry Pratchett and Iain M. Banks.

While the rest of the committee will be assisting me this year as they
have done in every previous year, the position of Picocon Beanbag, my
second in command, is presently unfilled. If everything I’ve said so
far interests you and you would like to be involved, please consider
running for this position at our EGM this term! For all announcements
+ useful information after this point, please do follow the Picocon
twitter account \texttt{@picocon}.

Hope to see you all there!
