Hello all! I have the honour and burden of being this year's Picocon Sofa. Picocon is our annual convention, which is organised and run completely by our illustrious society, aided, abetted and prodded into action occasionally by myself! \\
This year's Picocon has the theme of 'origins', where I am attempting to trace the origins of Picocon itself along with the Guests of Honour (see opposite spread) who will talk along this theme. However, because something in me feels this lacks some pretentiousness, we also have the tagline 'in media res', because what's an event without some dubious Latin! Signifying that we are exploring the origins of things how they are now, and also indicating the second theme I wish to explore in this year's Picocon - that of the interrelation between different types of media, where the genres seem to be indeed 'in media res' and provide a theme and story which can join the forms of media in the telling.\\
Picocon 33 will also continue our many traditions, some of which are a tradition of definitely not happening (feel free to ask about what definitely doesn't happen back in the library anytime!), and some of which are old classics like the destruction of dodgy merchandise and the turkey readings. I also hope to repeat the now proven principle of a cinema showing - but more details are yet to come! While Picocon 33 has a brief outline, it is still baking, so join us by mailing list and in person in the library at lunchtimes to find out more about Picocon 33 and our lovely society! Finally, I hope you have a lovely time at Imperial, and make the most of all the chances you get. You won't regret it.