I watched the storm system spiral below me from my spot in the ring, blues and greens in a great slow waltz. I could sit and gaze for hours, it's a good thing too - I had no idea how long I'd need to be staked out here, it had already been an entire sol. I was nestled in this planet's B ring, with its albedoflage up the Hyrm looked like any other old chunk of ice. I had the systems running on low, but there was still a faint heat exhaust if you looked in the infrared. It's a speck in a sea though, so it isn't normally an issue. 

I'd overheard a conversation in a dive bar at the spaceport the J{\"o}rmungandr was docked in a system over. They'd been water-mining in the rings when they noticed a ship drop out of subspace just below them, it had looked expensive. It had stuck around for a couple hours then disappeared back to wherever it had come from. The miner couldn't see what it was up to, his sensors had been way outmatched. But it seemed like it might have been a regular occurence; the mystery ship arrived again a week later and spooked the miner out of the area for good. I reckoned someone had themselves a nice little cache hidden up there in the rings. It'd take impossibly long to root through all the ice to look for it directly, the owner probably has the orbit down to a T. They'd know where it would be for thousands of years, that is, unless someone else got their hands on it. I thought it might be worth a small visit, before the 'Gandr left the quadrant.
\vspace{0.5mm}
\newline
---
\vspace{0.5mm}
\newline
I was staring at the shadows of the rings against the planet, trying to guess how many moons it might have from the gaps when I saw the flash in the corner of my eye. They'd finally dropped out and I'd been alerted by the mess of radiation that inevitably follows when spacetime desperately tries to claw itself back together at the end of a warp tunnel. Pretty ballsy dropping so close to the planet, guess they didn't expect there'd be anyone around to see. I pushed off from in front of the viewscreen and glided back to my chair. The Hyrm's own sensors had picked it up and were flashing at me on the command console. I strapped myself in and swivelled the ship's sensor array onto the newcomer. The miner hadn't been kidding, it was decked out in top quality stealth plating, after the initial flash I could barely keep a hold on it. Whoever owned that ship does not like to be bothered. 

I primed a tracker dart, this close it'd just be able to get a lock on the ship so that I could still follow it in case it broke line of sight. I launched it and watched it flit off, highlighted on my viewscreen, but small enough to be undetectable by them of course. It was good thinking, the ship dipped below the rings where I couldn't see it.  The dart beamed its infofeed back to me, just the location of our mutual friend, looks like they'd stopped. The cache was in the C ring, closer to the planet and a little ways around the disk from where I was hiding, let's hope they weren't emptying it. I put up my feet, at least I had an idea how long this wait would be.
\vspace{0.5mm}
\newline
---
\vspace{0.5mm}
\newline
Eventually, a movement on the infofeed caught my attention, they were leaving. I looked on as the ship crowned the disk,  arced up away from the planet and with another corresponding flash, was gone. I kicked my ship into gear and followed the dart's signal to my awaiting fortune. I moved slowly, hugging the ring in case anyone else had been around in that bar and had similar ideas. I got to the dart and the coast looked clear. I studied the viewscreen where it told me the ship had been. Aha! There, in a little cleared out void, a long thin case, maybe two and a half metres by one, silvered so that it doesn't stand out in the ice. I cruised over and stopped my ship a few metres out. Ugh, this is always the worst part, I unstrapped myself and kicked over to the airlock. I hate vacsuits, they always chafe. Once I was ready I activated the airlock and tethered myself, I felt the suit slowly puff as the air pressure gradually lightened. 

After what always feels like forever the red warning lights flashed above me, the chamber was finally empty and I could open the external hatch. I floated up and out and grabbed an exterior rung. I could be at the cache in just a single jump. I bent my knees, outstretched them again and was sailing through the vacuum of space to my prize. I approached it from underneath and arrested myself with a small jet from my thrusterpack. I surveyed the case: the bottom was blank, but when I peeked over the top I saw? Flowers? A bouquet of white tulips frozen stiff, fastened onto the case by a small wire poking out of the lid and back in again. I gained a bit of distance and looked down, there seemed to be a winged figure etched on the top, at its feet I spied what looked like writing. I thrusted back down to it and hovered just above the words. A medley of ice, dust and flower bits had glued themselves into the crevices. I took the plasma torch from my belt and turned it to its lowest setting, this wasn't how I had planned to use it but I was curious. I lightly blasted and sublimed the grooves clear of debris until the whole thing was clear. I read and felt my chest sink.
\vspace{0.5mm}
\begin{center}
{\it My Dearest Harmony,\\
Though I may travel the stars,\\
My heart will always lie here with you.}
\end{center}
\vspace{0.5mm}
A rogue such as myself doesn't often feel shame, but my head was hung as I drifted back to my ship.
