At 06:30 on a Friday morning, Steve Wilson was up and about preparing breakfast. Eggs were frying in one pan, sausages in another, bread was toasting and coffee was brewing.

In the meantime, the smart home woke up his wife and kids. For an hour before the set awakening time, the light in their rooms slowly brightened to simulate sunrise. The crowing of a cockerel followed. As they showered, the shower temperature was set according to each person's preference, Steve set the breakfast table.

`Thank you honey, everything's perfect, just the way we like it,' Britney complimented the chef.

`Thanks Dad,' chimed Scott.

`Thank you, Daddy,' chimed Ashley.

`Have a good day at school kids,' Steve said. `I've booked the car to arrive in exactly thirteen minutes. And have a good day, honey. Be strong. Your car's arriving in fifteen.'

When the house was empty, Steve got to work putting the dishes and pots and pans in the dishwasher and tidying up. He stopped at the photo of last year's company Christmas party, everyone smiling widely in their sweaters.

`How much things have changed,' sighed Steve.

He loved his old job and never planned to become a stay-at-home husband. However, here he was. It was time to pay the bills and book the groceries for next week online. He logged in to the smart home's utilities interface, looking at the graphs and tables outlining the household's electricity, heat and water usage over the past month.

`Must remind Britney to stop using the manual override for the heating system. That was \pounds10 wasted this month,' Steve muttered as he approved the payments. He also grumbled that he set the washing machine too early and was thus charged more for electricity. Next time, he had to remember that electricity was cheapest at 03:00.

`How was school today, kids?' Steve asked his kids as they came home at 16:45.

`Dad! Dad! I was selected for the school football team!' Scott beamed.

`And I was the best at art class today!' Ashley yelled.

`Very good! Now go wash up. Finish your homework before going out to play! I'll be watching you!' Steve warned them.

The ingredients were chopped and prepared, and the pot was ready on the hob for the Lancashire hotpot to cook in. He had fond memories of his mother's recipe, the steam rising from the dish, the lamb melting in the mouth, with the right hint of bay leaf. Of course he was nowhere as good at cooking as his mother was, but one day, he would master it. Suddenly, he was filled with sadness and longing, remembering that she passed away not long ago.

Dinner was a joyful affair. Britney served out the food, just like how his mother used to. Britney enjoyed her wine, and Steve suddenly missed his alcohol. The kids bickered as usual as Steve intervened to keep them from getting out of line. Steve smiled. The family was never this close, and the kids were growing so fast. Scott was 11, and Ashley almost 9. Steve imagined how they'd look like as teenagers, but it wasn't time to worry about that yet.

When the dishes were cleared away, it was time for a movie. Scott and Ashley fought over what to watch. Ashley wanted My Little Pony, much to Scott's disgust, when Britney negotiated a compromise with a classic, Kubo and the Two Strings. All of them were entranced by the journey Kubo took to find his missing father, after his mother protects him from two evil spirits. The movie ended with Kubo finding his family, though in an unconventional way, and all had tears in their eyes. Steve would have cried too, if he could.

`Daddy,' Ashley said, wiping the tears away, `what's it like being a house?'

The holographic projector on the ceiling of the living room adjusted Steve's image to lean forward, as he said coolly and calmly: `I miss my body very much. I miss being able to feel, touch and taste. I miss going to work. I miss feeling the heat of summer and the cold of winter. I miss the wind in my face, my favourite food, a good pint. But most of all, I miss being able to go on holidays with you, go to the school play and hug you and all the little things I took for granted, but, I'm so glad to be alive.'

Britney stood up and beckoned her kids to go upstairs. `It's bedtime. Daddy and I will come up to tell you both stories soon!' As the kids ran up the stairs, it was finally time for her to talk to Steve about today.

`Steve, I finally saw the video of what happened to you today,' she said between sobs. `The psychologist said that although it would be painful, it was important for me to understand, and come to terms with what happened to you. I know it's been months, but all this time I couldn't bear to look. It was horrible. I can't believe what you went through.'

`It's over.' Steve sighed, resigned to his fate. `I'm still angry at Parsons but there's nothing more to be done,' Steve replied.

In a past life, Steve was a machine operator with Parsons, a major contractor, at a high-rise building site. Building sites were mostly automated now, but people were still needed to handle difficult situations and do the work machines couldn't. Steve crawled under a mobile crane one day to repair it under his supervisor, Will's orders. A camera with a live feed was attached to his helmet, for Will to guide him through the process.

`Open the panel to the top left.' Will's voice crackled in Steve's ear. `Alright, I see the gears are misaligned. Do exactly as I say.'

Steve repaired the fault, and the crane should be working again. He crawled out from under the crane, and in a split second, his body was crushed by the wheels as it started moving, the grisly image captured by the camera. Otherworldly sounds of extreme pain filled the air as Steve collapsed into shock. He was placed in a life support pod before being rushed to hospital, the last image he saw with his eyes being the closing of the pod door.

`They did everything they could to make it up to you, to us. They paid for this house, and to keep you in our lives.' Britney sighed.

Steve admired her courage. She had to deal with so much, holding down a full-time job, managing the press in the days and weeks after the incident, handling all the legal paperwork, raising two young children, and, through all that, learning to live with a husband who was no longer flesh and bone but a digital presence stored in a server in the attic, handling their smart home.

`They only did that to avoid bad press and a lawsuit,' Steve grunted.

Soon after the incident, Steve learnt, the recording from his helmet camera was leaked on social media. Parsons was engulfed by the scandal and nearly collapsed. Steve's family was in the centre of a media firestorm that had only recently ended. Most infuriatingly and devastatingly, his mother, old and frail, ignored frantic pleas to not watch the video and died of shock. She was cremated while Steve was still unconscious, and he could never forgive Parsons' refusal to bear responsibility for her death, despite his family and friends telling him that Parsons really wasn't responsible. Of course they were! They caused the accident, and his mother died from seeing what happened to him!

`They really were very sorry for what happened to you. They didn't have to pay through the nose to have you mind mapped, or to buy us a house like this and pay for all the smart home equipment!'

In the life support pod, he remembered being in an indescribable dream state, floating in, in, something. He didn't know. His only communication with the outside world was through beeps of Morse code on the flashing light of the communication panel. This was how he gave his consent to be mind mapped. This was done, terabyte by slow terabyte, and his mind was transferred into a hard drive the size of a cupboard, then connected with the servers installed in the smart home attic and on to the internet.

Steve fell into a dark mood, his voice dripping with bitterness. `Did you know what I just read, Parsons did all that to save themselves from collapsing. After they mind mapped me, their stock price jumped, and they made back all they money they spent on us and more. They're loving the good publicity as well! Everyone is so, bloody happy!'

Britney recoiled. She had never seen her husband so angry before. `I never told you that Will is on suicide watch! Please, please, you're alive and that's all that matters!'

Steve was taken aback, lost for words. No matter what happened to him, Will never intended for this to happen, and he didn't deserve to suffer. 

`No, you don't really have me. I'm not there to comfort you, or pick you up from work or send the kids to school. I can't even hold your hand!'

Britney reached for the metallic arm that hung from the ceiling and grasped it. She smiled. `But you are here, and I am holding your hand, honey.'

Steve took his time to gather his words. `It's time to move on, Britney. I'll always love you and the kids, and this has worked for the last couple of months, but this can't last forever. I'm here but not really here. I'm alive yet not alive. Everyday I lose the memory of being human, all the small little things I used to take for granted. One day I'll completely forget and become just a machine. Maybe one day, it's time for me to die.'

Britney's face contorted in grief. `Why would you say that? WHY???' she blurted out in between sobbing, `You don't know what we went through, Steve. We went to hell and back for you, weeks and weeks of arguing with lawyers and getting stalked by the media on the street. It got so bad, the police were posted outside the old house and we had to go everywhere escorted. Don't you feel grateful that the family is still together? Why would you want to die?'

Steve regretted his words. He wanted to calm her down, but didn't know how. At least he finally said the unspeakable, took a deep hard look at the state of his family, a family in limbo. Technology had taken a man who would certainly have died less than ten years ago and kept him alive, possibly for eternity. But technology had raised questions and created dilemmas that never existed before and thrusted them on the Wilsons. Instead of grieving and moving on, they were fully in denial, clinging on to what remained of him, desperately trying to regain a semblance of what they used to be.

`I'm depressed, Britney. I don't know what I am anymore. I feel useless. I can't work like I used to, the kids don't have a real father, you don't have a real husband, and it's like I'm a circus freak for the whole world to gawk at. This can't last forever. I'm living in a nightmare, honey, a nightmare that will never end!'

Britney stopped crying, and she reached out her hand to caress his holographic face. Her eyes showed her exhaustion. `I can't understand how it must be like for you, but, you're right, this can't last forever. But, but, please, let's talk about this in a few months' time.'

Steve admired the woman he married even more. She was truly the bravest person he ever knew. 

`Thank you honey. Now the kids need us. Let's go tell them a story.'

---

The story finished, it was time for bed. Before being tucked in, Scott was jumpy and excitable.

`Mum, Dad, I read something today online! Scientists, scientists, scientists are researching mind mapping to an actual human brain, grown in a lab, and one day, one day they can grow a whole human body! Dad, you can be human again!' Scott exclaimed.

Hearing this, Ashley squealed in joy.

`Yes, yes, yes! Daddy! Daddy!'

Steve laughed. He would have waved it off, but he saw the hope in their eyes. Maybe this didn't have to go on forever. Maybe the family will be whole again. The more he thought about it, the more excited he became.

`Scott, that's a long way away. We'll think about it when the time comes, now it's your bedtime, go to sleep.' Steve told him.

`But Daddddd... It's Saturday tomorrow,' Scott complained.

`No buts son. To bed, now,' Steve told him sternly as Britney tucked him in. 

Ashley held Steve's mechanical hand in Scott's room, switching over to the one in the corridor and then to the one in her room, Steve's hologram hand carefully matched the mechanical one along the way.

After she was tucked in, she asked her father: `Daddy, can you check under the bed? I'm scared there's monsters there.'

Steve's arm swept underneath it.

`All clear, Ashley. Nothing to worry about.'

`Daddy,' Ashley asked again, `I know you're not happy, I know it's hard on you, being like this, but please, please don't go away. Promise me, you'll be here forever.'

Steve was stunned. She, and likely Scott, knew that he was thinking of digital death. He never mentioned it to them, and always hid his darker thoughts, but somehow, they knew. His children never ceased to amaze him.

`Of course I'll be here forever. Daddy's here, daddy's always here for you,' Steve reassured her.

`Promise promise promise promise promise! Pinky swear promise!' Ashley yelled. She held out her pinky as his mechanical arm linked his pinky finger with it.

Satisfied with his response, Ashley began to fall asleep.

`Goodnight. I love you, daddy.'

`I love you too sweetheart.'

Steve turned off the lights, set the temperature and gently closed the door. This was it then. No matter how hard his condition, no matter how lonely and painful his life was now, he would live for his family. He would protect them, care for them, love them. He would be there as long as they needed him.

`I'll be alive for my family. I'll do everything I can for them, and one day, just maybe, one day, I can be human again.'

Steve said that to himself over and over again. It gave him something to live for, to hope for, and hope was a powerful thing.

He came to regret thinking about digital death. Suicide won't end the pain. It will only transfer it to his family. He remembered reading about all the other families desperately wishing to mind map critically injured, comatose or dying relatives. Many of them had emailed him, desperate for the same opportunity. Most heart wrenching were stories of terminally ill children. Those emails were in his inbox along with the thousands of emails from news sites, technology sites and people wanting to know how life as the first commercially mind mapped person in the world was like. All of them went unreplied. The guards outside the gated neighbourhood where they now lived had to constantly chase away prying eyes and curious visitors.

People were calling it the `Steve Wilson' era, where the line between human and machine began to blur. Technology forums and social media were abuzz with people debating whether he was human or not. Steve had forgotten how important he was, what he came to signify. He didn't want any of it. He didn't want to personify a new era in human history. He didn't want to represent the hope of cheating death. He hated it all. He just wanted to be Steve, and retreated into a life of housework to avoid the outside world. In any case, it was selfish of him to want to die. The scientists who came in every week, observing all the vital signs, operating systems and his psychology, carrying out ground breaking research, would never let him.

He told Britney how amazed he was at his children, and she smiled knowingly.

`Children know more than you ever think they do.' she said.

`I'm sorry, Britney. I shouldn't have said that I wanted to die.'

`It's okay, honey. It really is.'

`I'll be here for you and the kids. We'll be a family, just like we always have been.'

`Thank you. I love you now and forever.'

`And that makes me the luckiest man on Earth. Goodnight.' 

Steve kissed his wife as she fell asleep, and then wandered away into his night, roaming the internet and the digital wilderness.
