Man, I was in deep trouble, just what I get for being a do-gooder. On the plus side, I'm pretty sure I had put a massive dent in the illegal drug usage going on in the city. On the other side, I had a trio of powerful wizards chasing me right now. Apparently, people really don't like it when you've been causing their profits to go down. In any case, there is no way I'd be able to take them down in my current state. I had to pull a desperate manoeuvre and I had to do it now. Panting, I finally arrived at my destination and made a request that would determine the outcome of the next hour.

`Two rounds of shots, now!'

I should probably back up a bit. I'm a wizard living in London, 2018. Magical skills and abilities weren't something I was born with, but they also weren't something that took a lot of effort to get. I happened to stumble upon a wizarding monastery of sorts during my holidays in the Scottish mountains. Yeah, I know, an odd place to train wizards, maybe that's why there are so few of them these days. They let me stay with them for a few weeks and taught me some basic spells while I was there. It might seem too good to be true but there was a big catch; doing something as simple as setting a piece of paper on fire would leave me exhausted for the rest of the day. They offered me the chance to hone my skills, to not get so fatigued and cast even more powerful spells. I declined; a degree in electrical engineering was more than enough work for me.

I didn't think much of it when my course started again. I didn't try to use magic much either; I charged my phone one time in the morning and it led me to miss an entire day's worth of lectures. One day however, when I was walking home after a bar night, I was feeling chilly and decided to use a spell to warm myself without really thinking about it. To my surprise, not only did I not pass out from sheer exhaustion, but I was noticeably warmer than when I had previously used the spell while training.

It took me a few weeks of experimenting but I finally worked it out. I could become less drained by my magic and make my spells even more powerful; the catch was that I had to be drunk. Well la dee da. Unfortunately I still got hangovers and I didn't want to become an alcoholic, so I resolved not to drink solely for the purpose of using my magic. But then I got the itch, I had the ability to use my magic without handicapping myself. Who cared if being a little tipsy was all it took.

I did what any nerd who fantasizes about superheroes would do. I decided to become a midnight crusader. It wasn't too bad at first. The night before a day with no morning lectures, I would drink two pints to get buzzed and go out on patrol. Not really a lot of crime to be honest; at least that I could find wandering around. But one day, I was able to spot some drug dealers and well, one thing led to another and I had advanced to destroying warehouses of drugs. It wasn't even that hard, just one carefully aimed fireball and thousands of kilograms of drugs gone. I could be in and out without anyone who was causing all the mess.

Until today of course. In my latest escapade, I found another warehouse; this was harder to find seeing as I was burning the rest. I snuck inside, quickly surveyed the area, and launched another classic fireball. Smiling to myself I turned to go back home, only to find myself face to face with three tall guys, all dressed in black leather. I could feel the power emanating from them and knew instantly that I was severely outmatched.

`You're the one who's been messing with our coke for the last few weeks, haven't you?'

I tried to say something but could only make pathetic, gargling noises in an effort to speak. Their hands immediately started to glow with power. I raised my hands in mock defeat and adrenaline finally gave me the ability to speak again,

`Don't suppose we could talk this out?'

I then launched as much of my power as I dared at them. Not enough to stun them, unfortunately, but enough to stun them momentarily while I used the last of my power on several teleportation spells. The trouble with the nature of the spell and my abilites was that I had to look at where I was going when using them. I ran out of magic only a few miles away and dashed into the nearest pub I could find. And that brings us back to the current scene.

It's not hard to find a wizard if you had the necessary skill. I knew it was only a matter of time before the other guys found me. In that time, I was able to down 2 rounds of shots, Andy's Purple Armageddon and half a glass of whisky. At this point, it was an effort of me to just stand on my feet. I was on one knee, holding the glass of whiskey, trying to stabilise myself when they barged in. Damn, I could not think straight. I was going to have to go on instinct alone. I downed the remaining whiskey in one go (gross!) as I got up and faced them.

One of the thugs launched a ball of lightning at me. I meant to dive out of the way, instead I just fell onto a table and pushed a couple's drinks to the floor.

`SSooorrrr.. . . . ' was all I could get out.

I found myself being lifted and slammed against the wall. The offender was of course, one of the rogue wizards. Up close, I saw he was tall, blonde and wearing sunglasses. Who the heck wears sunglasses at night?

`Well aren't you a scrawny runt,' he said, raising his hand.

`Yer fash ish a schrwany rant,' was all I could slur out in response.

I pointed my hand at him and fired an air blast. The force of my spell ripped him away from me and slammed him against the wall. There was a loud crack and he slumped to the ground. I, meanwhile, fell to the ground on all fours. For some reason, this was funny to me and I started giggling uncontrollably.

The other rogues were, understandably, very perturbed by this chain of events and were unsure of what to do. But not for long, I saw them make some hand movements and before I knew it, my clothes were on fire.

Well that got me to my feet.

`No! Nooo! My mum got me thish jacket!'

Water. I need water. Now!

I reached out for a nearby pitcher but in my current state, only managed to knock it to the floor, spilling its contents everywhere.

`Nooo!'

Because it seemed like the rational thing to do at the time, I decided to fall into the puddle of water. Unconsciously running my magic on autopilot, I duplicated it. A bit too much. I felt like I got knocked aside by some incredible and wet force. I let it just carry me until I came to a halt. I got up on my knees with great difficulty. Apparently, I reproduced so much water I caused a mini-stream to form from where I had knocked over the pitcher. The water was flowing outside now, and the level inside was steadily going down. Everyone had been knocked back by the flow but not enough to fall unconscious. The same was true, unfortunately, for the two wizards who had set me on fire. Before I knew it, they were right in front of me.

I immediately whipped up a magical shield around me. Powerful enough that they were pushed backward. Leaning against the wall, I forced myself to stand up.

`Hoooo booi. You guyz are in for it nowsh.'

I forced myself to try and concentrate. That was incredibly hard considering how fuzzy my mind was and the fact that the alcohol was blurring my vision. The two rogues threw a variety of spells at me, my shield held. They were clearly panicking now.

`What are you gonna do now?!' one of them managed to spit at me.

`Yo Mamma!' I screamed, raising my hand and firing a bolt of power at them. If only I wasn't drunk, I would've hit them. Instead I got some chairs metres away from where they were standing. They stared at the broken chairs in confusion. I shook my head.

`Well damn.'

It was now or never, I just started randomly firing power bolts in whatever direction I could. The air became filled with the buzz of power, flashes of light, and flying wooden chairs. I stopped to steady myself and looked at my results. Honestly? They were pretty terrible. I had pretty much demolished all the furniture in the pub. On the plus side, the remaining two rogues were squashed under a pile of broken chair legs. I teleported myself right next to them.

One of them was knocked out thankfully, but the other was still conscious and struggling to free himself. His eyes were glowing. I knew I had to do it now, the final blow.

I threw up on him.

He launched his power out in surprise. He missed me and managed to hit a painting on the wall which immediately fell and smashed onto his face. He was finally unconscious. At least I hoped he was. It would really suck to have some deaths on my hands. 

I pondered this thought for a few seconds before I promptly fell unconscious myself.  
