{\it T minus ten.}

General David Moore, the director of the Global Space Agency, stood with his hands folded neatly behind his back. Even in the privacy of his own office, he held himself straight and tall, his shoulders back and his expression inscrutable. His gaze was focused intently on the live footage of the rocket. Kyle Owens, his junior, stood beside him. A flicker of anxiety danced in his eyes, as his fingers fidgeted restlessly with the dog-eared corner of his notes.

{\it Nine.}

Moore spoke. `Of course, it's a noble mission. They'll go down in history.'

Owens bit his lip. `Yes, sir. The country's been rooting for them for a long time.'

Moore did not look away from the feed. `It's boosted morale across the world, to think of them winging their way towards the Proxima Centauri colony, delivering supplies to the first generation of colonists. Nobody likes to consider the worst-case scenario, but it will still ease everyone's anxiety, to know we're prepared for mass evacuation of Earth.'

{\it Eight.}

`How- I wonder how likely that is? An evacuation, I mean.'

Moore's eyebrows twitched microscopically. `We won't be able to maintain habitability on Earth indefinitely. Temperatures are still climbing, and pollution's reaching dangerous levels in many corners of the globe. People are becoming more desperate. They need this mission. They need some hope.'

`It's just...' Owens trailed off, seemingly unsure of whether he was overstepping his boundaries. `That kind of mass movement would take years, even decades, of planning. And I don't think we've really- we've really got anything, have we?'

{\it Seven.}

Moore's shoulders seemed, perhaps, to slump a little, before he quickly resumed his careful posture. `With our current resources... it wouldn't be feasible.'

`But- what does that mean?'

`We'd initially planned to begin preparing for evacuation before this crew even set off, but... new information came to light. But the people need hope. The only thing keeping them from panicking or rioting is having something to be believe in, and this is all they have. We had to go ahead.'

{\it Six.}

An uneasy feeling stirred in Owens' stomach. `Sir, if I have your permission to ask... what was the new information?'

Moore cast an appraising glance over him, and let out a quiet sigh. `We found out about a year and a half before launch.' He paused for a long moment. `Proxima Centauri is around 4.2 lightyears away from Earth. That means the signal we received from the colonists a year and a half ago was sent nearly six years ago now. It was far too late to do anything.'

{\it Five.}

Owens kept quiet, his eyes wide and fixed on Moore.

After what felt like an age, Moore spoke softly. `The planet was not as easy for settlers to cultivate as we'd hoped. The land was hard and infertile. Water was harder to come by than our unmanned missions suggested. The colonists sent out an SOS, a desperate plea for help.'

Owens let out a shuddering breath. `Six years ago...'

`They'll be long dead by now.' Moore's voice held steady.

{\it Four.}

`So the crew...' Owens spoke in no more than a whisper.

`Travelling at three quarters the speed of light, they'll reach Proxima Centauri in around five and a half years. There'll be nothing left for them when they arrive.'

`They're going to die.' His voice cracked on the sentence.

`They die here with the rest of us, or they die there. There's nothing that can be done.'

{\it Three.}

`We have to stop the launch!' Owens ran a trembling hand through his short, black hair. `It's not too late to stop it.'

Moore placed one hand lightly on his arm. `The mission has to go ahead. We've spent a year and a half trying to find some way around it, but we can't admit to the public that there's no hope in the colony. We can't destroy their illusion of the brave explorers of humanity, preparing a new planet for their arrival.'

Owens was hunched slightly where he stood. `I feel sick,' he whispered to himself, his eyes flitting nervously between Moore and the live feed of the rocket. `Do the crew know?'

`Of course not. They don't need to know.'

{\it Two.}

Owens took a shaky step towards Moore's desk and collapsed into a chair. His fingers combed through his hair again, his face pale as he blinked rapidly, still looking a little dazed. Moore spared him no more than a fleeting look, as he continued to peruse the screen on the office wall.

`It's for the good of the wider population. A few lives lost will save many from the crush of panic, and will at least prolong hope for many more. It's a necessary trade-off.'

`Oh, God...'

{\it One.}

`As I said, it's a noble mission. They'll be remembered for as long as there's life on Earth to remember them.'

{\it Lift off.}