Welcome one and all to Picocon 37: \emph{Pride!}

Why Pride, you might be asking? Well let me explain:

Picocon has always\footnote{
  [\underline{\textit{citation needed}}]
}
fallen within LGBT History Month in the UK. I myself happen to be
asexual, and have found a good number of my fellow ICSF members to
fall somewhere in the LGBTQ+ community. Science Fiction and Fantasy,
as genres, often seem to me to be about exploring our world, but
through the lens of a very different world: it is unsurprising then,
that these genres are used to tell the story of LGBTQ+ characters
more than other genres\footnote{
again, [\underline{{\textit{citation needed}}}]. I may be making this
up entirely!  
}. With this in mind, I decided (before Picocon 36 had
even occurred) that I wanted Picocon 37 to be about highlighting
LGBTQ+ characters and creators in the genres Picocon has always been
about celebrating.

Just over a year later, and that plan seems to have just about come
together! We have 3 truly brilliant Guests of Honour this year: I must
say a huge thank you to \textbf{Roz Kaveney, Juliet Kemp} and
\textbf{Tamsyn Muir,} as without them we would not have much of a
Picocon at all this year\textemdash and they'll certainly be far more
entertaining and interesting than I could hope to be!

Of course, we'll have many returning traditions and vendors! For
health and safety reasons, there will most certainly not be any duels
fought with fish, which means that the newly acquired safety gear (lab
coats \& paintball masks) will not be needed. This definitely will not
occur on the Queen's Lawn later in the day, as it never has.

We will of course also be employing liquid nitrogen to destroy some
merchandise that looks as though it shouldn't have been made, and
playing many of the silly convention games that we always do (I hear
this year we may be playing a large game of \emph{Mafia)} while
raising some money for some spectacular charities:
\textbf{Switchboard} and \textbf{Stonewall}.

Have fun!
