Hi all! For those of you who’re not yet familiar with our subterranean lair, or even some of our more occasional visitors, the eccentricities of our society may not be entirely apparent: please allow my introduction as Picocon Sofa to be the first taste of our particular brand of nonsense. We’re an old society, so we get silly names. Yes, I know, it’s great.

On 17th February 2018, we’re extending our tendrils into other parts of Imperial College to host invited guests with enlightening talks and panels, as well as an assortment of more esoteric activities. Since the early 1980s, we and our predecessors have run 34 of these literary conventions, making this the 35th annual Picocon. In previous years, we’ve hosted Terry Pratchet (GNU Pterry), Charles Stross, and Frances Hardinge, and with three guests already confirmed for this year, we hope to ensure this tradition continues into the far future by running a memorable event. Every year we raise large sums for the Raising and Giving scheme (RAG) by holding turkey readings (you pay us to stop torturing you with the worst modern literature we can dredge from the depths) and smashing tragic bootleg merchandise with liquid nitrogen and the hammer from a friendly fire engine.

Picocon 35 is broadly focussed around the theme of harmony: the unification of different elements to form a pleasing whole. The theme has coloured the choice of guests, which include a well-known collaborative duo, as well as an author who skilfully blends aspects of different genres into their works. Hopefully these hints have tantalised enough that you’ll keep up to date with the latest on the convention on our social media presence: search for \#Picocon on facebook or twitter for more information. As with any harmonious undertaking, it couldn’t be done without my trusty deputy, Kai Lawrence, who serves as Picocon Beanbag, as well as the support of the rest of the ICSF committee.

We’re also running an art competition --- design a logo for Picocon 35, and we’ll put it on all of this year’s promotional material. You’ll also get a shirt with your design on. Previous examples are available on our website, or on archived shirts and promotional material in the library, so drop by and ask a committee member! Please send entries or questions to icsf.picoconsofa@gmail.com.