% Anurag's Introduction
Welcome Guests!

So, it’s that time of the year again. Picocon is here, hurray! We didn’t mess it up and, thanks to all the hard work of our Sofa, Noor, it looks to be one of the best in recent years. (No offense ex-committees it’s just something I’m practically contractually obligated to say at this point. Although technically as chair, I suppose I could change that. Hmm, future Picocon ideas, erect a statue in my honour?) 
But I digress. The sofa and beanbag have gone to great lengths to ensure that you have a great time today and I hope you will. We’ve got some fantastic guests lined up for you; there’s Paul Cornell, author of the wonderful Shadow Police series, comic book-er extraordinaire, and Doctor Who writer. We have Michelle Paver; writer of the childhood defining Chronicles of Ancient Darkness series, and of course Carrie Hope Fletcher, author of the upcoming ‘On the Other Side’; currently performing Eponine in the West End production of Les Mis. You’re probably wondering why I’m selling you the guests when, if you’re reading this, you’ve clearly already bought a ticket. It’s a great way to fill up space to reach my word count (Don’t tell the editor. And Amelia, if you’re reading this, ignore that last sentence.\footnotemark[1]) 

Overall, it’s been a superb year for the society; we’ve had tons of new faces and successful events. As such, new faces, you’re probably wondering what to expect for your first Picocon. Well, there’ll be lots of running around, probably an awkward moment or two, a tank of liquid nitrogen and a mallet, and definitely no fish. You’ll no doubt see me around, chaperoning Paul, so feel free to approach me if you have any questions/complaints/urgent philosophical quandaries. Other than that, relax, take in the talks, play some Just Dance, and have a great day!

\footnotetext[1]{Editor's note: See crossword, 1 down.}