\lettrine[lines=3]{T}{o} the Freshers: Welcome to Imperial and to Imperial College Science Fiction Society! To everyone else: Welcome back! Now that your peaceful/busy/exciting (choose all that apply) summer has ended, and the inevitable tide of lectures and labs is beginning, we’re happy to be able to throw open our doors and provide you with a respite from all that stress. We’ll be open every single week day lunchtime and often for longer, watching something good (probably set in space or containing elves, sometimes both), socialising, reading, and just generally relaxing until we have to face the real world again. Everyone’s very friendly, newcomers are always welcome, and no-one bites.

What kind of Chair Entity would I be if I didn’t take this opportunity to mention our lending library of now over 10,000 books (I know, that number scares even me sometimes), and 2000 DVDs and comics? All of which, and I do mean all, are available to our members. And if somehow we don’t have a given book, just let us know and we’ll try and get it for you as soon as possible, too! In addition to your ability to access more media than you could physically get through in your time at Imperial \textemdash{} trust me, I’ve tried \textemdash{} we also run various events throughout the entire year. These include subsidised cinema trips to the latest sci-fi/fantasy blockbusters, bar nights for both drinkers and non-drinkers, and Themed Friday nights where we celebrate the weekend by watching the best films/tv of a given theme our Chair of Vice has come up with, while likely eating way too much.

We also run seasonal events, such as our Halloween party, which involves such complete and utter nonsense as the best sing-along horror films we can find, and an optional costume contest (usually of bizarre not-at-all-scary sci-fi/fantasy characters), plus pizza. We also run a Christmas event full of traditional holiday films, mince pies, and carols to the Old Gods slumbering beneath the oceans; the usual holiday things.

Last, but certainly not least: we run our own yearly convention, Picocon. Yes, this is a real, actual convention held at Imperial, with guests and panels and everything, but I’ll let our Picocon Sofa\footnotemark{} talk to you about that event. I hope this ‘zine of ours gives you all an idea about our society, and if I can end this with a few words to the Freshers among you: nitwit, blubber, oddment, tweak \textemdash{} and Don’t Panic. You’ll do fantastically.
