\lettrine[lines=3]{T}{he} riveting events from ICSF this upcoming year range from movie marathons of cheesy classics, to singing till you drop at \textit{Frozen} karaoke. Expect a torrent of events for the first few weeks of this term, with plenty of opportunities to meet fellow fans of sci-fi, fantasy, Monty Python, and who knows what else.

Here are some of the regular events you can be expecting from ICSF:

\textbf{Lunchtime Showings} \textemdash{}
From noon to 2pm nearly every weekday, the library can be found filled with people watching, various TV shows and movies that ICSF has to offer. For the first couple of weeks of term, we’ll be showing some of our favourite picks to give you an idea of what our collection has to offer, but after that, the selection is open to all.

\textbf{Literary Lucky Dip} \textemdash{}
Fancy a mysterious free book? Well, join us for this new take on a lucky dip, with books being wrapped up in packaging with subtle hints to the contents within.

\textbf{Bar Nights} \textemdash{}
Our monthly bar nights are a great opportunity to meet and catch up over a few drinks (alcoholic or otherwise) and discuss science fiction, fantasy, or whatever else catches your interest!

\textbf{Book Crawl} \textemdash{}
Where some societies have pub crawls, ICSF has book crawls! We’ll be travelling around the best book and comic stores in London to find out what they have to offer.

\textbf{Halloween} \textemdash{}
On Friday 27th October we will be having an all-singing all-dancing party with showings of Horror and singalong classics like \textit{The Rocky Horror Picture Show} and \textit{Dr Horrible’s Sing-Along Blog}. Come prepared for plenty of snacks, pizza, and even a fancy dress competition!

\textbf{Cinema Trips} \textemdash{}
Whether it may be discounted or not, come along as we go out in groups to see the latest fantasy and sci-fi hits in cinema. This term, be excited for: \textit{Venom, Fantastic Beasts: The Crimes of Grindelwald,} and \textit{Aquaman}.

For more information about upcoming events, see the calendar on the following page.
