\lettrine[lines=3]{H}{ello,} welcome and/or welcome back! My name is Matthew and I am the Head Librarian for the Science Fiction and Fantasy Society this year. If you are reading this you are more than likely interested in our little corner of Beit basement and the kinds of treasures it holds, so let me elaborate.

Firstly, Books! Over 10,000 of them! All available to be checked out of our database the moment you join our society. Likewise, we have over 2000 DVDs of all kinds of sci-fi TV and films, and over 600 graphic novels, all available to borrow. Can't find what you are looking for? Then simply write it on our request list or talk to a member of our committee and we will see what we can do about adding it to our collection.

Our library is also a lovely social space, where you can come and enjoy some television, meet friendly faces, hold lively and nerdy discussions or simply relax away from university life for a bit. The library will be open every weekday during term time from at least 12pm - 2pm (though it often stays open much longer), so feel free to pop around during a lunchtime and enjoy an episode or 2. On Fridays, we celebrate the end of the week by watching movies from some of our favourite genres and series. Keep up to date with these and many other fun events by connecting to our Facebook group.

If, after all that, you are bewildered by our collection and have no idea where to start, simply look overleaf and read some recommendations by members of our committee. I hope to see you among the shelves soon.
