\lettrine[lines=3]{G}{reetings!} I am this year’s Picocon Sofa \textemdash{} a more comfortable chair, you see. For those of you not acquainted with the oddities of our society, Picocon is our annual convention raising money for charity, and also for the society. I am in charge of running this fantabulous show, which hopefully will not crash and burn like a fresher’s attempt at sobriety.

The history of Picocon stretches back across many years, and the 36th annual Picocon will be held on 16th February 2019. At Picocon, there will be many, many things to be enjoyed, including the exciting sight of objects such as a delightfully cute Porg plushie being submerged into a vat of liquid nitrogen and then destroyed with a giant hammer, in a truly \textit{smashing} event known as the Destruction of Dodgy Merchandise. Another infamous event will be the Turkey Readings, in which the committee shall read to you modern “literature” until you pay us to stop \textemdash{} for charity, of course. We will have a number of Guests of Honour giving speeches and presentations: in previous years, we’ve hosted names such as Terry Pratchett, Charles Stross, and Peter F. Halmilton. Two guests are confirmed for this coming year, and with more in the pipeline, this year is sure not to disappoint!

I am not alone in organising this event. I am aided by the committee as a greater hive-like entity, most notably this year’s Beanbag, Harry Black. The theme for this year is not yet finalised at the time of writing, but will be announced shortly along with the artwork contest and a full list of guests and speakers. For announcements for useful things like our theme, our guests, and our art competition’s deadline, you can follow Picocon on Twitter at \texttt{@Picocon}.

Merry Universitying!
