Hi everyone. 
First things first, welcome back to ICSF and Imperial in general! To the Freshers, let me be one of the ever-increasing horde of people wishing you congratulations on making your way here, you deserve it. 

Now that your peaceful/chaotic/exciting (choose one or more) summer has ended, and the inevitable tide of lectures and labs is resuming, we are happy to be able throw open our doors and provide you with a lunchtime respite away from all of that stress. 
Without fail, we’ll be there watching something involving laser or swords, socialising, and just generally whiling the time away until we have to face the real world again. Everyone’s very friendly, newcomers are always welcome, and no-one bites. 

And what kind of Acting Chair Entity would I be if I didn’t take any opportunity possible to mention our lending library of over 9000 (yes, over 9000!) books, DVDs, and comics? All of which are available to our members - and if by some fluke of chance we don’t have a particular book just let us know and it’ll be in the library lickety-split (has anyone actually said lickety-split since the 1800s?). 

If our library, the size of which still staggers me, doesn’t convince you to join by itself then let me try and sweeten the deal.
In addition to your ability to be able to access more media than you could feasibly consume in over a decade, we also run various events throughout the year. Past events have included: subsidised cinema trips to see the latest blockbuster (read as: comic book/Star Wars/book adaptation movie), bar nights which are popular with both drinkers and non-drinkers, as well as more specialised events. 
We even get seasonal with a Halloween event full to the brim with cheesy costumes, cheesy pizza, and even cheesier sing-a-long nonsense, and a Christmas event full of mince pies, classic Christmas films, and assorted other Christmas-y things. 

Last, but certainly not least: we run a convention, Picocon. An actual, real, true-to-life convention with guests and panels and everything, but I’ll let our Picocon Sofa talk to you about that particular event. 

To the Freshers among you I hope this ‘zine gives you an idea about our society, and if I can end this with one piece of advice: Don’t Panic, you’ll do fantastically. Acting-Chair out.
