\vspace{1mm} 

As you may have gathered by now, the SciFi society runs loads of fun events over the year, involving everything from movie marathons to Cthulhu carols. There are many exciting events in the first few weeks, which you can find out more about on the timetable on the next page. The fun continues over the year so be sure to subscribe to the mailing list to stay updated. 

\vspace{1mm} {\Large Lunchtime Showings}

Most lunctimes (12 - 2pm) you will find the library full of people watching various TV shows and movies. For the first few weeks we will be showing some of the most well known movies and TV shows to give you an idea of the genre, but after that it's up to whoever gets there first. 

\vspace{1mm} {\Large Literary Lucky Dip}

Did someone say free books? Yes, we did! But there's a catch - the books will be wrapped up with only a few words on the front to describe what's inside. 

\vspace{1mm} {\Large ICSF Barnights}

Barnights are a great opportunity to meet and discuss everything SFF related, and many other things too!

\vspace{1mm} {\Large Book Crawl}

Forget pub crawls, ICSF has book crawls! Join us on a trip round London's best book and comic stores for a chance to discover where they are and what they have to offer.

\vspace{1mm} {\Large Halloween}

On Monday 31st October we will be having an all-singing all-dancing party in the library with showings of horror classics such The Rocky Horror Show and Dr Horrible's Sing-Along Blog. Also to look forward to are a fancy dress competition and a table in the bar!

\vspace{1mm} {\Large Cinema Trips}

Outings to see genre films are arranged throughout the year. This term we hope to go and see \textbf{Doctor Stange} and \textbf{Star Wars}.

Arrangements for tickets will be circulated using the \url{icsf-list} mailing list.
