\vspace{2mm} {\Large Mailing Lists}

ICSF maintains two mailing lists, which all members are welcome to subscribe to.
Like all official Imperial mailing lists, they use mailman.
%
\textbf{icsf-list} is the society's core mailing list, which contains
announcements of ICSF events and important news about the society.
This list gets quite a low volume of traffic, and \textit{is a must if
you want to hear about film trips and other events.}
%
\textbf{icsf-committee} is our `management' list --- but it gets used a
lot more widely that that. Here you'll be able to contribute your opinion
to the running of the society.
%
You can manage your subscriptions at \url{mailman.imperial.ac.uk/mailman}.

{\large Social Networks}

For those who welcome our social network overlords, we also have a Facebook
group, which is pretty much a continuation of the library into the
realms of cyber space --- \url{facebook.com/groups/ICSF.Imperial} (or search for
`Imperial College Science Fiction').

New this year is a library twitter account. Follow icsf\textunderscore librarian for updates on new additions and recommendations.

{\large EGM}

This year we also have three committee positions to be occupied: Chair, Editor and 
Tech Priest. The elections will take place on Wed 5th October at 6pm. So if you like making `zines, fixing the webcam or just generally bossing people around, now is your chance! 

If you don't intend to run, the meeting will still be a good way to get to know this year's committee and more about how the society is managed. 

\vspace{-10mm}