Hello and welcome, freshers and those slightly longer in the tooth. ICSF is a rather old society, which means positions get funny names. I am your Sofa, which means that I’m in charge of Picocon, our student run literary convention that’ll be held on the 18th of September 2017. 

This is the 34th one we’ve ever held, and they’ve been going on every year since the early 1980s.  In previous years, we’ve had Terry Pratchett, Michelle Paver, and Charles Stross as guests of honour, and will have another three guests this year. These authors each give an hour long talk, taking questions and discussing topics with the audience, before we have all of them together for a group panel session. Other events include turkey readings, where we regale you with the worst of modern literature until you pay us to stop, and the destruction of dodgy merchandise, where plastic abominations are shattered with the aid of liquid nitrogen and a large hammer. All the proceeds from these events go to the Raising and Giving scheme (RAG).  

The theme for this year is futurism – advances in artificial intelligence and robotics mean that the theoretical utopias/dystopias of fiction are becoming an increasingly relevant topic. While things are looking good for technology in areas such as driverless cars, organising events must sadly still be performed by less automated methods – and to help me with this we have our esteemed beanbag, Edward da Fonseca. 

We’re also running an art competition – design a logo for the convention and we’ll show the work on all our promotional material. You’ll also get a shirt with your design on. Previous examples can be seen on our website, or in the large box of old shirts if you ask any committee member. The deadline for entries is the 1st November, so please send these or any questions to icsf.picoconsofa@gmail.com. 