To give you some ideas about what to take out of the library, here are some recommendations from the committee members of books to borrow:

\newcommand{\bookrec}[4]{\noindent
  {#1}\newline
  \indent \textemdash{} \altfont{\textbf{#2}} by {#3}\newline
  \indent \textit{#4}
}

{ \bookrec
  {Henry Wild}
  {Kings of the Wyld}
  {Nicholas Eames}
  {Fantasy mercenary bands treated like musical bands.}
}

{ \bookrec
  {Connor Winzar}
  {
    Injustice: Gods Among Us\footnote{
      This is a comic. We have those.
    }
  }
  {Tom Taylor and Brian Buccellato}
  {A story of the corruption of Superman's morals and his descent into tyranny.}
}

{ \bookrec
  {Michael Figini}
  {The Simpsons and their Mathematical Secrets\footnote{
      This is a non-fiction book. We have those too.
    }
  }
  {Simon Singh}
  {Makes you want to re-watch the show just to find the mathematical secrets.}
}

{ \bookrec
  {Matthew Legg}
  {The Hitchhiker's Guide to the Galaxy}
  {Douglas Adams}
  {Earth has been demolished. Don't Panic, and please don't forget to bring your towel.}
}

{ \bookrec
  {Matthew Last}
  {Mort}
  {Terry Pratchett}
  {Death gets an apprentice. A strong introduction to the Discworld series.}
}

{ \bookrec
  {Edward Pickup}
  {The Red Knight}
  {Miles Cameron}
  {Fantasy Britain, but the Scottish are demons.}
}

{ \bookrec
  {Harry Black}
  {Speaker for the Dead}
  {Orson Scott Card}
  {Aliens, philosophy, and psychology?}
}

{ \bookrec
  {Jean Lo}
  {Schild's Ladder}
  {Greg Egan}
  {Differential geometry as a metaphor for character development.}
}

{ \bookrec
  {Sequoia Trevorrow}
  {
    The Songs of Distant Earth\footnote{
      Sequoia also recommends the album of the same name, by Mike Oldfield.
    }
  }
  {Arthur C. Clarke}
  {Earth is gone. God is dead. Life is still an emotion-filled rollercoaster.}
}

{ \bookrec
  {Timothy Davison}
  {Foundation}
  {Isaac Asimov}
  {The Empire is crumbling. Fight the chaos.}
}
