%\vspace*{\fill}
\renewcommand{\PuzzleNumberFont}{\tt\scriptsize}
\begin{Puzzle}{15}{15}
  | [1]H|   I| [2]S|     T|    O|    R|    Y|   *|    *|    *|       *|    *| [3]D|   *|   *|.
  |    I|   *|    W|     *|    *|    *|    *|[4]T|    *| [5]K|       L|    A|    A|   T|   U|.
  | [6]G|   R|    A|     B| [7]T|    H|    A|   R|    *|    *|       *|    *|    V|   *|   *|.
  |    H|   *|    L|     *|    E|    *|    *|   U|    *|    *|[8]    F|    R|    E|   E|   *|.
  |    G|   *| [9]L|     U|    N|    C|    H|   T|    I|    M|       E|    *|    *|   *|   *|.
  |    R|   *|    O|     *|    S|    *|    *|   H|    *|    *|       A|    *|    *|   *|   *|.
  |    O|   *|    W|     *|    I|    *|[10]J|   *|[11]C|    *|       R|    *|[12]S|   *|   *|.
  |[13]U|   H|    *|     *|    O|    *|    O|   *|    H|    *|       *|[14]F|    I|   N|   D|.
  |    N|   *|    *|     *|[15]N|    E|    U|   T|    R|    O|   [16]N|    *|    C|   *|   *|.
  |    D|   *|    *|     *|    *|    *|    R|   *|    O|    *|       O|    *|    I|   *|   *|.
  |    *|   *|    *| [17]R|    A|    I|    N|   *|[18]M|    O|       R|    A|    L|   S|   *|.
  |    *|   *|    *|     E|    *|    *|    E|   *|    E|    *|       T|    *|    I|   *|   *|.
  |    *|   *|    *| [19]D|    U|[20]T|    Y|   *|    *|[21]F|       H|    T|    A|   G|   N|.
  |    *|   *|    *|     *|    *|    R|    *|   *|    *|    *|       *|    *|    N|   *|   *|.
  |    *|   *|    *|     *|    *|    Y|    *|   *|    *|    *|       *|    *|    *|   *|   *|.
\end{Puzzle}
%
\newenvironment{cwclues}[1]{
  \ignorespaces
  \begin{minipage}[t]{0.44\textwidth}
    {\small \textbf{#1}}
    \footnotesize
    \begin{itemize}[leftmargin=*,topsep=0pt,itemsep=0pt]
      \newcommand{\cwclue}[6]{%
        % #1     - number
        % #2     - answer
        % #3     - format
        % #4, #5 - clue
        % #6     - source
      \item[\texttt{##1}]{##4}~\rule{2em}{.02em}~{##5}
        \textit{{##6}}~\texttt{(##3)}
      }
}{
    \end{itemize}
    %\end{PuzzleClues}
  \end{minipage}
  \ignorespacesafterend
}
%
\hspace*{\fill}
\begin{cwclues}{Down}
  \cwclue{1}{HIGHGROUND}{4,~6}{
    It's over, Anakin! I have the }{.
  }{Star Wars: Episode III \textemdash{} Revenge of the Sith}
  %
  \cwclue{2}{SWALLOW}{7}{
    What is the air-speed velocity of an unladen }{?
  }{Monty Python and the Holy Grail}
  %
  \cwclue{3}{DAVE}{4}{
    I'm sorry, }{. I'm afraid I can't do that.
  }{2001: A Space Odyssey}
  %
  \cwclue{4}{TRUTH}{5}{
    The past was erased, the erasure was forgotten, the lie became }{.
  }{1984}
  \cwclue{7}{TENSION}{7}{
  }{, apprehension, and dissension have begun.
  }{The Demolished Man}
  %
  \cwclue{8}{FEAR}{4}{
  }{ is the mind-killer.
  }{Dune}
  %
  \cwclue{10}{JOURNEY}{7}{
    Life before death. Strength before weakness. }{ before destination.
  }{The Way of Kings}
  %
  \cwclue{11}{CHROME}{6}{
    You will ride eternal, shiny and }{!
  }{Mad Max: Fury Road}
  %
  \cwclue{12}{SICILIAN}{8}{
    Never go against a }{ when death is on the line.
  }{The Princess Bride}
  %
  \cwclue{16}{NORTH}{5}{
    Bear Island knows no king but the king in the }{.
  }{Game of Thrones}
  %
  \cwclue{17}{RED}{3}{
    You've got }{ on you.
  }{Shaun of the Dead}
  %
  \cwclue{20}{TRY}{3}{
    Do ... or do not. There is no }{.
  }{The Empire Strikes Back}
\end{cwclues}
\hspace{1em}
\begin{cwclues}{Across}
  \cwclue{1}{HISTORY}{7}{
  }{. Read it and weep!
  }{Cat's Cradle}
  %
  \cwclue{5}{KLAATU}{6}{
  }{ barada nikto.
  }{The Day the Earth Stood Still}
  %
  \cwclue{6}{GRABTHAR}{8}{
    By }{'s hammer, by the suns of Worvan, you shall be avenged.
  }{Galaxy Quest}
  %
  \cwclue{8}{FREE}{4}{
    Dobby is a }{ elf!
  }{Harry Potter and the Deathly Hallows}
  %
  \cwclue{9}{LUNCHTIME}{9}{
    Time is an illusion. }{ doubly so.
  }{The Hitchhiker's Guide to the Galaxy}
  %
  \cwclue{13}{UH}{2}{
    Life, }{, finds a way.
  }{Jurassic Park}
  %
  \cwclue{14}{BIND}{4}{
    One Ring to rule them all, One Ring to find them; One Ring to bring them all and in the darkness }{ them.
  }{The Lord of the Rings}
  %
  \cwclue{15}{NEUTRON}{7}{
    Reverse the polarity of the }{ flow!
  }{Doctor Who}
  %
  \cwclue{17}{RAIN}{4}{
    All those moments will be lost in time, like tears in }{.
  }{Blade Runner}
  %
  \cwclue{18}{MORALS}{6}{
    Never let your sense of }{ prevent you from doing what is right.
  }{Foundation}
  %
  \cwclue{19}{DUTY}{4}{
    Death is lighter than a feather. }{, heavier than a mountain.
  }{The Wheel of Time}
  %
  \cwclue{21}{FHTAGN}{6}{
    Ph'nglui mglw'nafh Cthulhu R'lyeh wgah'nagl }{.
  }{The Call of Cthulhu}
  %
\end{cwclues}
\hspace*{\fill}
\vspace{1.5em}
\begin{center}
  \textit{
    Thanks to the library for suggesting these quotations.
  }
\end{center}
