Hi Everyone! 
Let me start off by welcoming you all to a new year at ICSF. Freshers, let me be the latest in a \textit{long} line, I’m sure, to congratulate you and welcome you to Imperial. Summer’s over and now the society can go back to doing what it does best; providing a lunch time respite from a hectic day of lectures/labs/whatever. Without fail, we’ll be in there watching something, socialising, and just having a great time in general. Everyone’s super friendly, newcomers are always welcome, and they don’t bite. I have ways of making sure.

 Now, as chair, I have the unenviable task of trying to entice you into joining with only these little paragraphs of writing. Unenviable, mind you, only because two years of technical lab report writing have flattened what little capacity for creative writing I had. I’ll start off by talking about our biggest draw, the lending library. We have a huge selection of movies, books, comics, even tapes (god, remember those?) available for members to borrow. I’ll let the librarian go into more detail about that. As for events, we have something for everyone. Subsidised cinema trips to go see the latest topical blockbusters, fantastic bar-nights which are popular with both drinkers and non-drinkers. Not to mention our Halloween and Christmas events. The former of these involves costumes, classic film and TV (both cheesy and otherwise), copious Pizza (both cheesy and otherwise), bad sing-a-longs, and Dr. Frank N. Furter. Really, I couldn’t possibly hope to do it justice here; you’ve should definitely see it for yourself. Similarly, the Christmas event involves more Christmas-y things. Mince pies, a Muppet Christmas Carol, etc…Like I said, more Christmas-y stuff. Again, just go see it. Finally, we have our huge in-house yearly convention. Yep, it’s a real convention, with famous guests and everything. Check out our leaflet for more information on that. Hopefully, this little booklet should give you a good idea of the societies’ activities and, as my predecessor put it, ‘philosophies’. I’ll finish with a classic; live long and prosper. Chair out.