Welcome to the Library!\\ 
Hi! I am the Head Librarian this year and as such I want to welcome all of you to our Science Fiction and Fantasy Library. \\
If you were at our stall during Fresher’s Fair you probably already know how to get to the Library but here are some brief instructions just in case: once you enter the Beit Quad turn left immediately and you’ll get to the entrance to the West Basement. You’ll need your student ID to gain entry. The Library is located down the corridor to the right. There is also a map at the back of this Wyrmtongue.\\
The Library is open every weekday from 12 to 2pm so you can come in your lunch hour to pick up a book or sit down with our excellent members to chat or watch an episode or two (or three…) of your favourite sci-fi series. If you find that only being in the Library during lunch hours is not enough, you are welcome to check our webcam (link on our web page: www.icsf.org.uk) to see if someone is in at some other time. You’ll find that this is mostly the case, especially on Friday evenings when we celebrate the end of the week with our favourite films and pizza. Occasionally we also leave the Library for events like Bar Nights or the ‘Bookcrawl’ (our version of a pub-crawl where we visit mostly bookshops and comic shops). \\
Our Library has an extensive collection of science fiction, fantasy and gothic horror (along with some other genres) including over 9000 books, over 200 DVDs and almost 600 graphic novels. In the improbable case that we don’t have a particular book you wanted to read you can add it to the wish-list and I will promptly add it to our shelves. To profit from this collection all you have to do is join our society on the union website and visit the Library when it is open. There should always be a Duty Librarian present if I am not there myself to help you take out books and DVDs. Don’t know what to read first? Check out the recommendations section of the Wyrmtongue for a selection of books handpicked by our members. \\
I look forward to meeting all of you and I am here for you if you have any questions.