The fun doesn't stop with Picocon! We have plenty of other events planned for the rest of the term, from movie marathons to laser battles. Whether you're a fully-fledged member of the society or you're here for the first time, we'd love to have you join us. 

\vspace{4mm} {\Large Themed Friday: Horror}

Join us on the evening of Friday 23\textsuperscript{rd} February, as we rediscover the `Gothic Horror' part of the society's title. 

\vspace{4mm} {\Large Laser Quest}

Because as much fun as it is to watch an epic sci-fi war on the big screen, it just can't compare to grabbing some laser guns and doing it ourselves! Join ICSF and Gaming for the battle of a lifetime.

\vspace{4mm} {\Large Book Club}

The long-awaited first meeting of ICSF's book club, at 6pm on 1\textsuperscript{st} March, will be a great opportunity to discuss some of the best science fiction and fantasy novels, and maybe get to know some new favourites. The first book will be `Left Hand of Darkness'.

\vspace{4mm} {\Large Firefly Marathon}

As tragic as it is that Firefly was cut so short, at least it means we can marathon the whole thing over one weekend! Come along on 3\textsuperscript{rd} and 4\textsuperscript{th} March for good television, good company, and perhaps even some good snacks.

\vspace{4mm} {\Large Unofficial Black Panther Trip}

Planning on seeing Black Panther? Who better to go with than a bunch of other nerds from ICSF!

\vspace{4mm} 
More details of events will be circulated on the \url{icsf-list} mailing list, so please do sign up to the mailing list or join our Facebook group if you're interested.