This time last year, a crack team of well-read and highly intelligent fans was hand-picked from Imperial College London's Science Fiction and Fantasy society's secret basement lair, to ensure that Picocon 35 would be planned and executed down to the last second - for the glory of the society. However, none of them could make it, so you're stuck with a pair of people named Ed with questionable taste in fiction and wildly varying senses of humour. Ah well, can't be helped!

Thankfully, our guests are much more interesting than we are, and we've inherited the knowledge of past conventions to make sure that fish duels definitely don't take place, and that liquid nitrogen is available to rid the world of its never-ending stream of dodgy merchandise.

Up first are the creative partnership of Paul Stewart and Chris Riddell, who will be speaking to you together for an hour, followed by half hour each about their writing and illustration respectively. At this point, we'll break for lunch in the h-bar. The aforementioned destruction of dodgy merchandise will occur about halfway through with help from Stuart Ashen, hopefully allowing enough time for everybody to recoup their energy. 

After lunch, we have the fantastic Emma Newman, who will talk to us about her work with audiobook narration. This is followed by our author panel, where you'll have the opportunity to put questions to all of our guests. Also joining us for the panel is Ben Aaronovitch, whose work includes two Doctor Who serials, several spin-off novels, and his best-selling series, Rivers of London. After the panel, there will be a chance to get books signed by all of the panellists.

This year's convention has been an interesting one to organise, and on a personal level, I have to extend my thanks to everyone who's volunteered their time to make sure that paperwork has been done, tables have been carried, and ideas have been floated. And to you, dear guests - some of you have been visiting this convention since before I was born, and I hope that Picocon continues to evolve and entertain.

Welcome to all of you,