Our vendors are located on the second floor of the Blackett foyer, and and would love to introduce themselves to you.

\vspace{5mm}

{\Large Paul Couper}

A reader/collector of SF/Fantasy, selling at Picocon to clear duplicates built up whilst collecting and upgrading. My collection is now over 12,000 paperbacks, but still has many gaps. Most wanted at present? Probably E Pluribus Unicorn, Theodore Sturgeon, Timescape paperback (i.e. 4th Pocket printing) to complete my timescape collection. So if anyone has a copy of that (or other collectables) for sale, wants to buy, or indeed just wants a chat, stop by during the day.

\vspace{5mm}

{\Large Clockwork Firebird Designs - Alex Locke }

Welcome to Clockwork Firebird Designs! I am a self-taught, ever-evolving tailor, leather worker and costume maker with a penchant for creating monsters. I attend Live Action Role-Play (LARP) events and Anime/Comic conventions as both a trader and attendee on a regular basis. I've been doing leather work since 2008, and selling since 2011. I recall learning to sew when I was 6 years old and I've not really stopped since. Within the shop you may find armour, masks, trinkets, painted artworks, soft toys... anything I bring to mind or feel like turning my hand to! I am still finding my feet, and I am always learning new techniques.

\vspace{5mm}

{\Large Blackwell Books }

This year, giving you an even greater selection of books to browse from, we will also be welcoming Blackwell's for the first time. For Picocon, they will primarily be stocking books by our Guests of Honour, so it will be a great chance for you to grab a copy of the books you've heard all about today!