It was high noon on the twelfth rotation of the seventy-ninth primary
phase when we arrived at the city of Torados on the planet Tost. The
near sun drifted lazily about the top of the sky, bathing the
yellow-brick buildings in a pleasant golden light. Our local contact
was a certain Rev. Toaster Pincuel K. Gallon, and they met us by the
shuttle landing zone.

Torados was, of course, the primary export hub of Tost, and we had
hitched a ride on a freighter that was inbound from our previous stop
at Stupandar. Excusing our dishevelled state thusly, we proceeded with
Pin \textemdash{} as I shall refer to him henceforth \textemdash{} to
the waiting vehicle. Our purpose on Tost being such as it was
\textemdash{} conducting a xenopological study of the Communion
\textemdash{} we had no time for typical luxuries associated with
tourist travel. This was well, for the entirely toast-based economy of
Tost had nothing in the way of facilities for tourists. In accordance
with this frugality, our local transportation to the lodgings we had
secured was a worker's bus carrying Tostians to and from their various
jobs at spaceport.

The Tostians were an interested bunch to observe: they seemed to
converse amicably amongst themselves rapidly in a local dialect of
Tostal, completely ignoring the presence of two foreigners
\textemdash{} such as my companion and I were \textemdash{} in their
midst. Pin, themselves a rather strange fellow who spoke little and
seemed amused by our smallest action, remarked that Tostians cared
little for life off Tost and that they were probably ignoring us on
purpose.

My companion Dr Alex Claythorn, a senior academic at The Institute on
Capita, remarked that it seemed strange to him that they should care
so little about the outside as an entirely exporting nation. Pin
replied, rather shortly (by my measure), that trading was done of
necessity, for Tost had no resources beyond the ability to grow grain.

Presently, we arrived at our lodgings: workers' quarters which had
been vacated for the purpose of our visit. The sun was still roaming
the high skies, despite the trip having taken a couple of standard
hours, so Alex and myself decided to explore the city for a while. Pin
insisted on joining us, though I should have liked to do some
exploration without a shadow from the provincial Government. And hence
we set off on foot from the outskirts towards the centre of Torados.

The road into the centre of town snaked its way through the
residential neighbourhood that contained our lodgings towards the main
square which hosted the rather grand looking municipal
headquarters. It was clear to us that the road had never been intended
to be the thoroughfare that it had become, thronging as it was with
Tostians. Pin elaborated that the roadway was originally a simple
footpath connecting the original landing site of the first colony ship
to the spaceport we had arrived at. As time had gone on, he explained,
the early Tostians settled on the roadway and began to build
dwellings.

`Of course, they're all allocated by the Board now,' he finished.

The Board, as anyone who has studied xenopolitics knows, is the head
of the Tostian `government', such as it is. Given the entire planet's
dedication to the single industry of wheat, bread, and toast
production, the state is naturally run more like a business than a
traditional government. In particular, this means that a Tostian's job
is allocated by the Board, and the job comes with benefits such as
lodging and board.

We proceeded along the road toward the square at the centre of town,
which had in it a fountain marking the landing spot of the first
colony ship to arrive on Tost. The square itself was rather large and
built up in a grand style, with the sides being lined by shops and
food outlets carrying all the necessities. One of the buildings on the
western side carried an impressive Tostian flag, and Pin confirmed for
us that this was, in fact, the municipal headquarters.

I shall save a detailed description of the centre of Torados and the
municipal buildings for the next instalment of this tour of Tost. For
now, let me leave you with this description of the Infinite Toaster we
found on a plaque beside a scale model:

\vspace{\baselineskip}
\begin{center}
    \parbox{0.7\textwidth}{\texttt{The Infinite Toaster is the industrial
      heartland of Tost. Imagine a land of vast discs, each several
      hundred metres across and carrying several thousand loaves of
      bread. Every disc is fed by a complex array of conveyors,
      carrying dough from the agricultural lands to the north of the
      Toaster, and is topped by large radiators. It is a magnificent
      sight that must be seen in person to be believed.}}
    \par
    \parbox{0.7\textwidth}{\texttt{Contact your sub-Board representative for
      job opportunities at the Infinite Toaster.}}
\end{center}

