General Director Anima had left the lights off to watch the endless
sand-blizzard scorch against the windows of the conference room. The
long-table in the centre of the atrium she couldn't move, it was
bolted down with the bronze company logo in its centre now black in
the limelight. The chairs had blocked her view of the sand-storm, and
after some time she managed to topple all of the heavy Earth-imported
teak to leave only hers remaining. The view was finally uninterrupted
and for the first and last time in her many years of stewardship she
was able to gaze at the entire length of the wall in all its
glory. The storm beyond her bunker never let up, and hadn't ever let
up in all history of their mining operations. There'd be windswept
dunes, shifting-shapes, but rarely a clear view for more than a few
dozen metres out. Only the halo-lights of mining-crawlers would
sometimes appear out of nowhere during a presentation and meander
through the gloom.

Quite how long she sat there staring like that she didn't know. For
the most part the sounds through the heavy crystal glass were muted
barring the occasional howl of grazing winds. Anima closed her eyes
and listened to the clocks in their different time-zones. Behind her
was New York, London was further up, Berlin and Beijing towards the
outer edges of the conference room counted out of sync with the rest,
and at the head of the table, irregular and low, ticked the Venusian
clock with its hundred-earth-day dial. \textit{How many times have I
 stared at each of you, waiting for the meetings to end and counting
 your time differences?} She hoped she might drift off before the
base started up for the final morning transit shuttles, but there was
no such luck and she got up restless to get a glass at the snack-table
in the far corner. Bless them, they'd kept it stocked with crisps and
drinks to the very end. She opened up the mini-fridge, found the
remnants of some bourbon and a can of Sarto, and returned to her place
with her dressing-gown stuffed full of home-grown peanuts. She rolled
her chair to the head of the table, and opened them all.

`Ladies and gentlemen if you turn your attention to figure 1 by the
projector here on the far end, you'll see your newly-redundant
director feasting and ignoring her keto diet.' She swivelled to the
projector screen and then back to her imaginary audience. `I'm glad
you asked that. Why do I do it manually and not just take slimming
supplements? Here at Redorine we're old-fashioned like that. We think
the old ways are best.' \textit{And that's why we're broke,} she
added. Anima threw a peanut up in the air and gave a bow from her
chair when she caught it in her mouth.

`And there's more party tricks than that. Just wait until the cocktail
evening.'

She could name who sat where, and wouldn't forget for the rest of
time. Jamie, Nicola, Jun, Lucy, thin Francis, Patana the Frenchman
(who would insist he'd only drink Patana-brand sparkling water and
nothing else) and all the others. Foreman Katie the brutish
drill-sergeant of quarry 4 would let her hair down and actually laugh
in this conference room and make terrible puns. Vinjal and Xiu would
prank her and go too far, and laugh like hyenas when they'd finally
tell her they'd given her decaf coffee for three months straight and
that's why she'd been so tired. Four-hundred and thirty-two
employees. That's how many it takes for this station to thrive. She
finished her peanuts. Vinjal and Xiu, Francis and Jamie were gone. All
who were left were a few of the security, core maintenance, catering
and herself to pack up the essentials. This place had served them well
with its art-deco halls and its burned sunset carpets, and Anima tried
and failed to reset all the chairs back to how they were before. This
time no-one would notice the disarray, she thought, and pushed open
the door to the main foyer.

Thin Francis had always called the main foyer the ‘missile silo', and
the name had spread across the crew far enough for her to order a
selection of brass signs from the machining department. She stood in
front of one now. ‘The Ernest Blendrek \textit{missile silo}
Foyer'. She remembered the quiet evening when she'd switched off the
spreadsheets to sneakily replace the boring signs around the base with
her own designs like this one. \textit{I did my best with morale, I
 really tried.} She ran her hand across one of them, this one with
arrows pointing to the respective wings of the bunker. West for
machining and administration, North was here, South and East for
accommodation, medical and catering. She leaned on the main railings
that ran around the central core of her missile silo. There were
bridges, the main loading dock at the far end, the corner to her left
was dedicated to the history and innovation of the company with sofas
and complementary coffee. And down below were the floors of rooms
quarried from the Venusian dark sands, full of industry and life and
home of friends.  The main skylight was still dark she noted
\textemdash{} dawn was breaking on Venus, and would be breaking for
another two Earth days. It would be at least four before they'd see
any difference through the sand-storm. \textit{I won't see the Sun
 rise here again.}

She wandered over to the complementary coffee corner and turned on the
lamps by the main reception desk \textemdash{} seldom used and
visitors were few, but the coffee went by the gallon each day
anyway. The jug was empty, and while it brewed she unwrapped the scale
display of the facility. Most things of sentimental value to Redorine
were wrapped and ready to ship back to Earth, or already had
been. Perishables like short-life food would be dumped once they were
sure they weren't needed. Furnishings stayed, essentials stayed and
they'd be worth far more here to whoever bought the place than
whatever price they fetched back home minus prohibitive shipping
costs. The wrappings of the display came free and she looked at the
cross-section of her bunker, the little model airships and quarries,
blasting-trawlers and mobile mechs. All the heavy equipment had gone
to other sites God knows where, or was in storage for the foreseeable
forever. Under her leadership they'd had time to open quarry six, and
leverage enough money to create the wind-power fields. The model
wasn't up to date, the quarries had expanded quite a bit since when it
was made, and the site marked here for quarry six wasn't
accurate. Either way, the main parts were right, and the essence was
there. The conference room showed plastic models having a field day
with a pie chart and she spotted what she supposed would be herself
staring intently at the little miniaturised board. There was the main
top-floor canteen, med-bay, the clean room, the research lab and all
the rest, even a miniaturised version of the reception and the scale
model before her. She hoped it would survive the transit.

Anima went to see how the coffee was doing, and was surprised to hear
the elevator doors open to break the silence. Out of them stepped a
figure she couldn't quite see from this distance without her glasses,
but resolved itself into someone familiar.

`I thought I'd come up here before they start packing for real,' they
said, and looked around the dark atrium.

`Me too,' replied Anima. `I went to watch the storm. It's nice in the
conference room, it still looks like it always has.'

`Calm before the storm doesn't quite fit, I don't think. Not
here. Here's always storm.' The woman who joined her poured herself a
cup of coffee and sat on one of the sofas.

`You should know.'

`Yah. Guess so,' said Katie. To think that it would be Katherine, the
great drill-sergeant of the quarry masses up at this hour, finally
sentimental. ‘Anima, these \textit{fuckers} are playing me up saying
the emulsion pump arrived broken.' ‘Anima, the combine drill on 4 is
\textit{corporate's problem.} Get on it or I'm gonna have to send a
ship empty and then they'll howl. Hell, so will you.' ‘Anima, get your
\textit{shit together,} we'll get through this, they can't shut us
down.'

`You think you'll ever come back?' asked Anima.

`No.'

There was a terrible finality about that which didn't mask the
truth. \textit{I tried to save it for as long as I could, Katie.}
She'd delayed the axe for a long time, and had been speaking to
corporate about improving viability for longer still.

`I'll miss this place.'

`Believe it or not, so will I. There's something satisfying about
making fresh miners shit their mechs early in the morning.'

`It's why you're the best safety officer.'

`Amen to that,' said Katie, and toasted her with the coffee. `No-one
died. Here we are, finally at the end in our slippers with our coffee
and at least we can say that. We didn't lose any under us.'

`Though it was close. Remember the time, oh' Anima struggled, `with
your favourite, that Tom Nagalniy?'

`Ah. How could you forget Tom? Built like Adonis, spoke like Adonis,
dumb as a post failing school.'

Anima's laughter echoed across the dark missile silo hall and made it
feel a little less final. Katie put on the Russian
accent. `Help. Foremaster Kaytiy. I'm out of poooweeer. To which I
said, ‘It's Foremaster Bayer or nothing'. Oh but really, I was a bit
shit-scared he might be hurt.'

`Don't lie and say Tom in the med-bay wasn't exactly what you would've
wanted.'

Katie didn't say anything to that, just narrowed her gaze and sipped
on the coffee.

`Is there any notice about what they want us to do with the mechs?'
she asked Anima.

`I got a notice after hours. Main management said to leave the main
casings behind and take apart the rest ready for shipping.'

Katie shook her head, `that's ridiculous, the casings are what make
them fifteen-million each.'

`I know, what am I going to do, though?'

`Idiots.'

`Are there any left working?' asked Anima.

`Yep, there should be about four still okay for refuelling ships
externally and making sure everything is nicely locked down. They're
prepped for a surface-walk.'

`I might go for a last spin in a mech then to say goodbye to this
planet,' she said. `I'll wave through the conference room
glass. There's peanuts still in there. You better be there to wave
back.'

`I will be,' said Katie.

And so she left Katie there, and went to the mechanics department to
say a final farewell to this place and see the building from the
outside in full glory before she headed to Earth for good.
