I was leaning against the bar in a speakeasy on 52nd Street, waiting
for things to clear up with Nora, when a girl got up from a table at
the far end of the room. She'd been sitting there with three others,
laughing and joshing around, and was now on her way to me. I tightened
my grip on my glass, swirling the contents as nonchalantly as I could
manage. Her long black hair hung in curls, curls which bounced as she
walked with comfortable determination. I could tell from the way she
moved that she was the kind who knew what she wanted and knew how to
get it, too. I straightened up a little, but regretted it
immediately. I should have played it cool for longer, but I haven't
been looking for a woman since I met Nora years ago.

I opened my mouth when she was just a few feet away, and \textemdash{}

She walked right past me.

`Could I have another Screwdriver, barkeep?' she said in a lower voice
than I'd expected. Her eyes twinkled in the dim lights.

He looked her up and down, his scruffy moustache twitching, as she
slid her empty glass towards him.

`Do you have the money for it, sunshine?' he asked, raising an eyebrow
at her.

`Come now, Winston, just put it on my tab,' she grinned, biting her
lower lip coyly and batting her lashes at him. A cheap trick anywhere.

`Your tab's as long as the Bible by now,' he grunted. `No more
Screwdrivers without payment.'

I couldn't help but watch their exchange, fascinated by the easy
rapport between them, almost like they'd known each other for a long
time \ldots but that couldn't be, could it?

She turned a little, picking up on my uncouth stare and her lips
quirked up.

`Can you believe Winston?' she smirked, leaning on the bar to face me
head-on. She sat down on the rundown, wooden barstool closest to me,
and showed off a toothy grin. I can't help but find that there's
something charming about it. Something familiar? Maybe. I'm not
sure. `He won't help out a lady in desperate need of a drink.'

`That's a real shame,' I somehow managed to get out without stumbling
through my words. You'd almost think that I'm a smooth
talker. Almost. But Nora would certainly argue otherwise. `It's nearly
like chivalry is dead, isn't it?'

`Almost,' she said, grinning, looking me once over. There was
something about that look which was domineering, possessive,
leering. But could it be \ldots ?

`What a waste,' I said, leaning just a little closer. Where was this
boldness coming from? I'd certainly never found it before at work or
at home. Could I maybe borrow some for day to day life?

`You know \ldots ' her tongue peaked out as it played with a sharp
looking incisor, `Chivalry might not be as dead as Winston makes it
out to be \ldots '

`Is that right?' I drawled, squinting at her eyes, trying to get a
better look. I felt like a fool, really, but I got an eerie sense that
this particular gal was the one that I needed to impress...That she
might just be the right one. After all, Nora always liked playing
little games.

`A tall, sweet gentleman could intervene, you know,' she smiled coyly
picking up her glass again. She tilted her head, and rest her hand
upon my wrist, pushing my sleeve up just a little. My number peaked
out, and she clicked her tongue. Approval?

`That's true,' I murmured, unable to believe myself. Nora would kill
me if I got this wrong.

`Could you be a doll,' she whispered in that alluring low voice, `And
help a girl out?'

I nodded, unable to control the chattering in my head. Damn it all. It
would be all right. Somehow. I couldn't explain it properly if I
tried, but she just had to be it, right?

 `Are you sure about this, new guy?' Winston asked, eyeing us
both. His wedding ring scratched the interior of the glass he was
drying. A scraping reminder to be careful.

I gulped and nodded, turning to pull my wallet out of my back
pocket. I saw a glimmer of something in her eyes.

`Thank you, sugar, you're a doll,' she drawled, handing the glass to
Winston again, as I set money onto the counter. He muttered something
under his breath about sirens and idiots, but I didn't pay him much
mind.

She giggled giddily and eyed me again, stepping closer.

`What brings a gentleman like you to a shoddy little establishment
like this?' she crooned. It was the same thing that brought everyone
else here, the same sense of adventure and reinvention and need to fix
or test things which might be broken. Or are in the process of
breaking.

`Just the usual,' I shrugged. It's all the same standard fare at the
end of the day. `How about yourself?' I asked, my breath hitching a
little bit. I'm a terrible actor, why was I even trying to act
otherwise?

`Just spending a nice evening out, having a laugh.'

She looked past my shoulder and winked at someone. I turned to check
who it was but there was no one looking our way. If she really had
come here with one of them then she wasn't the one. But then again she
could just be playing me real well.

Winston tapped the counter and pushed the Screwdriver towards her.

`Thanks, darling,' she beamed at him and took a sip.

Through all the theatrics I had completely forgotten about my drink. I
quickly gulped it down like a desperate man thirsting for the sweet
nectar of \ldots gin? Fine, maybe not sweet nectar, but I was still
parched. I grimaced as I swallowed.

She laughed gleefully, enthralled by my complete lack of cool. I don't
usually buy hard liquors but it seemed right to have something strong
during Prohibition. I didn't want to be a wimp next to all the tough
guys™.

`You shouldn't drink what you can't stomach,' she reminded me quietly,
placing her hand on mine, steadying my gently shaking glass. She led
it to the counter, and waited for me to let go, before placing her
hand in mine.

I felt a blush rising up my neck, and looked down at those intertwined
fingers that didn't quite feel like they were mine. The touch felt
off, though I could feel the weight of the contact. Her lips quirked
into a smile.

`What should I call you here?' she murmured.

Names. Shit. I hadn't come up with anything. James? No, I can't pull
off a James. John? Too standard. Mark? No.

`Luke,' I declared, more to myself than to her.

She snickered.

`I guess I'm lucky to have met you, Luke. You can call me Stella, in
that case.'

Stella. Wasn't that the name of the girl from Nora's favourite play? A
streetcar named something or other.

`So, where did you leave your missus?' she murmured, glancing
pointedly at the gold band on my ring finger. I hadn't even noticed
it.

`I-I'm not married,' I said immediately, blinking like the idiot that
she must take me for. `Just got engaged, though.' Moron. Why'd I
talked to her about reality?

Her smile didn't vanish, though. If anything, her grin had got wider.

`Tell me, sweet pea,' she drawled, eyes glittering with mischief,
`Where is she right now? What is it you've told yourself?'

I inhaled sharply.

`Surely you must have an idea or a story in the back of your head, or
you wouldn't be here with a shiny little ring,' she said relishing the
words.

`S-she's finishing the Christmas shopping,' I murmured, cheeks feeling
as hot as the stove back home. You could fry an egg on them at this
point.

`That's sweet,' she sighed, smiling absentmindedly at my neck, eyes
warm as the skin crinkled around the edges. A completely familiar
gesture. It was her after all. `Is she shopping just for you both, or
\ldots ?'

I paused, mid-breath, and my eyes flickered to our hands.

`For a future family,' I admitted my fantasy. We'd never had this
discussion before, but she had to know I wanted one \ldots

I shook my head, frowning.

`We shouldn't be talking about what's outside,' I whispered to her,
gripping her hand tightly, not wanting to let go, having found her
after all.

`We're not,' she whispered back, resting our hands on my heart. `We're
talking about what's inside. They won't mind.'

`They will,' I breathed so quietly that I wasn't sure whether she'd
even heard it.

From the corner of my eye I saw a man get up from the table she'd been
at, and caught him smirk at me. His walk was proud like a peacock's,
full of show and swagger. You could smell ‘alpha-male' from a mile
off.

`Sugar, aren't you coming back to us? It's not quite the same without
your \ldots ' he gave her a once over, revealing his pearly whites,
'Personality.' He signalled Winston for another drink and leant
against the bar right behind her, not even leaving a dream of space
between them.

She rolled her eyes and shifted slightly closer to me.

`Jeff, I'm in the middle of something important here,' she said not
turning away from me.

My eyes flickered back to him. Should I be saying something?

`More important than what we had going on?' he murmured, leaning down
to whisper into her ear. `Or do you prefer pussycats over real
tigers?' he chuckled eyeing my sharp business attire as his hands slid
over her hips.

That's when I saw it. The look I had seen a hundred times before. The
look that left no survivors. Her face went hard like it was made of
granite, and her hands dropped to grab his, angry claws digging into
prey. She pulled her head forward and swung it back, head-butting him.

`What the actual f \textemdash{}'

She turned in a split second, and pushed him hard against the
counter. Grabbing his arm, she flipped him, pinning his face onto the
bar with her elbow and yanking his hand between his shoulder blades.

`Don't touch me, dirt bag,' she hissed through gritted teeth. `Or I'll
break your hands.' She yanked his wrist harder as a not-so-subtle
demonstration. He howled.

`I'm sorry, I'm sorry!'

`That's enough now,' Winston said, visibly unimpressed, tapping the
revolver on his hip. `I don't want to be cleaning blood tonight.'

She glowered at Jeff again, and her skirts rustled against the bar as
she let him go.

`Fucking maniac,' he grunted massaging his shoulder. `You could have
just said that you're not Jenny.'

`And you could have just not grabbed me and been a lech,' she said
pointedly. `C'mon hon, let's go,' Stella said, taking my hand. I
looked between her and Jeff, who was flipping the bird at her back,
and smirked.

`Are you alright?' I asked, rubbing her back supportively as we walked
out through the doors.

A golden shimmer flickered over our skin, from head to toe, and we
were back in a grey room full of screens and techies. A man in a sharp
black cassock, the one who'd explained the wedding prep test to us,
came over from a screen which showed HD CCTV footage of the
speakeasy. He practically radiated. He clicked a button on his
earpiece, and clapped. The holo-lenses clicked out of existence and I
finally saw her again. Nora stood where Stella had been a second
before. Her brown hair was tied up in a ponytail and she wore her
flannel blouse and jeans again, not the frilly skirts and ruffles from
the little trip. She smirked at me with a knowing look, appraising my
return to a shirt and tie combo. She was probably missing the well-cut
suit already.

I looked down and saw that her hand was still in mine, and squeezed
it. She squeezed back and winked.

`That was wonderful,' Father Timothy beamed, slapping my back. `You
found each other very quickly, you managed to connect emotionally, and
you're fully willing to protect each other's dignity.'

`It was really more Nora than me,' I admitted sheepishly, and she
shrugged, but there was a hint of a smile playing on her lips. You
could take a field agent out of a mission, but you couldn't take
mission-training out of a field-agent. Jeff had never stood a chance.

`What can I say? I have zero tolerance for creeps,' she said, her
voice sounding normal again, without the lilts of a southern drawl.

`And that is a fine policy to have,' Father Timothy grinned, slapping
my back so hard that the pain radiated through my shoulders. Why did
he have to do this every single time? `Either way, you passed the
first test of the prep course with flying colours!'

`Not that anyone's surprised,' Nora said matter-of-factly, though a
familiar mischievous edge brightened her eyes.

`How did you recognise each other?' Father asked, leading us towards
the next doorway shimmering with gold. `Not counting that little bit
of cheating I saw there, Nora,' he amended, glancing at my wrist which
had sported her matching candidate number during the test. She grinned
sheepishly.

`The entire liquor interaction,' I said, quickly trying to think of
the first moment that could have given her away, not wanting to admit
how long it had actually taken me to be sure. She looked at me from
the corner of her eyes and smirked. She knew I was lying. `You know
I'm not keen on gin \ldots ' I pulled a face just remembering the
flavour. `What about you?' I asked, playing with my collar nervously.

She turned to me, and shifted her weight, giving me an amused
once-over.

`Well darling,' she said, returning to her honeyed
prohibition-drawl. She ran her eyes up the length of my crisp tie
before locking me down with a wicked grin. `No one ties a tie quite as
tight as you do.'
