\newcommand{\secnum}[1]{
\noindent #1

\noindent}

\secnum{1}
My eye snaps open and I'm back in the room. The transition from
nothing to everything is blinding, but I know I won't blink. He's here
again, the questioner. His eyes scan my face, a keen stare that passes
straight through me like a dart through fog.

My name is Elisa, at least that's all I've ever been called. Judging
by the steady brightening and dimming of the light that spills through
the skylight above me, I'd say that I've been here for a little over 3
years, though it could easily be longer. To tell the truth, I remember
almost nothing from before. Sometimes something will slip through the
cracks, all of a sudden, like it's being beamed in from
somewhere. Images of things, of people, of places I might have been or
was planning to go. But then they're snatched away, like I'm not
allowed to see them, as if someone knows I've remembered and wants to
correct their mistake. All I really know is that one day I woke up
here, screaming, feeling as if a thousand volts were surging through
my aching body. My best guess is that whoever brought me here wiped my
memory somehow, but honestly I don't really care. I'd rather know if
I'll ever get to leave.

His eyes flit back and forth from me to a thick yellow legal pad, half
full of scribbles from his visits. After several minutes I feel drowsy
and start to fall asleep, but he shakes me and I wake up, flinching. I
want to cry out, to ask him what he's doing, why I'm here, what he
wants from me. But no matter how hard I try I can't, as if I'm
programmed not to speak until he does first. My lips feel glued
together – I suppose he's trained me well. I try my best to stretch
while I wait for him to finish, but the ropes binding my limbs are so
tight it's hard to move at all. My joints strain and twinge as I
squirm around, sending sharp pulses through my body and threatening to
blow out at any minute.

Impotent and bored, I stare around the windowless room. I suppose it
must be a kind of storage facility. There are old screens stacked up
in the corners, and cardboard boxes full of tangled wires lining the
walls. The light from the skylight slowly brightens. I know every inch
of plaster, every angle of the shadows as they creep around
mechanically during the days, up and over the walls and boxes of
equipment in painfully slow but hypnotic cycles. The walls stare back,
mocking me in their concealment of the wonders that must lie beyond.

My eye wanders back to the questioner, as at last he finishes making
notes and looks up. He smiles and a glint of exhilaration flashes
across his pale blue eyes as, with a calm and practiced hand, he
reaches out and snatches the invisible gag from my mouth.

`Good morning Elisa'

\secnum{2}
\textit{Hello}, I reply. My speech feels jagged and clumsy, and the
stutter that sometimes comes on when I'm scared or stressed threatens
to take over. My mind already feels fractured at the thought of the
standard monotonous beginning to the never-ending stream of these
sessions, but I force myself to focus on keeping my voice steady and
pleasant. My hopelessness is exceeded only by the fear of the
isolation when he leaves, and the longer I play along, the longer he
stays. I'm always kept in the dark, but at least while he's here I'm
not alone.

`How are you today?'

The banality of it makes me want to scream, but I restrain myself and
respond in my sweetest tone.

\textit{I'm very well thank you. How are you?} I mainly want to keep
him happy and talking, and for now rack my brains for anything to say
that might keep the conversation flowing. Part of the point is the
keep it fresh, if possible. He usually seems to like that.

I've tried to understand the point of these questions, but have never
been able to \textemdash{} to anyone listening they'd seem bizarre to
say the least. Most of the time they're just a mundane string of
politeness, the most exciting ones covering whether I have any
hobbies, what kind of music I like, what I think about the weather,
and my plans for the weekend. What's most frustrating is that I have
no idea how he can expect me to have any answers. They've wiped my
memory and cut off any access to the outside world \textemdash{} how
on earth could I have opinions on anything?

The conversation continues for a while, when suddenly I hear a
knocking sound and the door to the room swings open. It opens inwards,
naturally blocking any view to what lies beyond, apart from a harsh
artificial light and a dim backdrop of voices talking over one
another. The questioner whips his head around in irritation and
half-yells through gritted teeth \textit{`Not now, I'm in session
here.'} I flinch at this sudden change in mood and he looks back at
me, a strange light flickering across his face. He's flushed with
anger and his thin brown hair is hanging gawkily over his forehead,
making him look faintly ridiculous. But the door gently closes and he
quickly settles back in, reverting to his standard cool exterior.

He restarts his question, something about sport this time, but I've
stopped listening. The scene with the door has reminded me of the end
of yesterday's session. I'd given up and started swearing and pleading
to be let out again, which I know is pointless but I just couldn't
help it. He'd slapped me a few times to get me under control, but that
had just made it worse and I yelled louder, the stutter I usually
manage to hide returning worse than ever. He slumped back in his
chair, defeated, and nudged me a final time before getting up to
leave. I tried to keep calling after him, but my vision had already
started clouding over and an unstoppable drowsiness took hold of
me. This isn't unusual either \textemdash{} every other session ends
this way, and although I've gotten used to it, it's always
distressing. He'd disappeared behind the door and, as it had swung
shut, I'd heard the first few snippets of his conversation with
someone outside, slightly distorted by a humming sound and my
diminishing consciousness. The voices were strange, but the final
phrase before the darkness consumed me stood out and has stuck with
me. \textit{`lost it \ldots nonsense \ldots the letters \ldots put her
to sleep.'}

 \textit{Do you sleep?} I interrupt the question about sport and he
 looks up at me sharply, surprised but clearly intrigued. His eyes fix
 mine with thinly veiled excitement, and he resettles himself in his
 chair and takes another brief scribble break before proceeding.

`Fine thank you Elisa'. He pauses, as if unsure how to proceed.

He obviously thinks I want to know how he slept, and I wonder what
this could mean. How being knocked out and abandoned could be anything
other than extremely unpleasant I have no idea. I interject before he
can continue, hoping to catch him off guard and make him reveal
something, anything.

 \textit{How can it be good?} He pauses, considers this, then replies.

`Do you mean you sleep badly?' he asks, his voice quickening. He's
losing me now, and I'm starting to wish he'd never asked. Whenever he
gets excited like this, the inevitable frustration which comes later
is all the worse for it.

 \textit{I don't know, I don't remember,} I murmur, hoping he'll drop
 it and move on to something else.

`Do you ever remember?'

I struggle to find something appropriate to say. If I lose track of
the conversation and say something that doesn't make sense, it usually
ends worse than just my breaking down. The truth is that sometimes I
do have flashes of vivid colours, or feel like I've woken up, in the
room when he's not around or somewhere else entirely. But they're so
fractious and jumbled I couldn't begin to describe them.

 \textit{ S-sometimes \ldots I don't know,} I mutter, and curse myself
for stammering. He slaps me, hard, and his congenial mask begins to
slip. I've pissed him off, I know it.

`Elisa, what do you remember?'

I try to focus, to think for the life of me of what he might want me
to say, but I'm so tired and my joints are so achy that I start to
slip and can't find the words. Eventually I manage to pin down an
instance from several nights ago, though it's almost impossible to
describe. It was dark, but there were colours there, and voices too. I
think I was remembering something, but I could have just been
imagining things. In any case, I don't remember what they said. I give
it my best, exhausted, frustrated shot.

 \textit{ It goes dark, but a colourful kind of dark. I hear others,
but not really, and I can't see them.} I know how little sense that
makes, and fearfully raise my eye to meet his. He seems exasperated,
and his irritation starts to show between the lines at the corners of
his mouth.

`What others?' he asks, then, before I can answer, `Are these dreams?
Are they real?'. I don't understand him – this is too much for me, and
I know it has to end soon. I decide to pick one of the words he just
used and roll the dice.

 \textit{I dream of leaving sometimes.}

He appears to deflate, sinking deep into the back of his chair, when
before he had been perched on the edge. This is the end unless I can
get him back, and I have no idea how. I pray that I'm making sense,
and can only hope that if I keep using his words, make him see that
I'm the same as he is, that he'll let me go.

\textit{
I dream of l-leaving, I th-ink,} I begin, but the stammer has taken
over and even I can barely understand what I'm saying. He looks
frustrated and leans further back, and my fear turns to
anger. \textit{I'd come back, I \ldots} He groans, leaning forward
with his head down. \textit{I don't know what you want, PLEASE just
let me go \ldots} He looks up, shakes his head as he cradles it in his
hands, his eyes squinting with frustration. He lashes out quickly and
hits me again. There's nothing more to be lost now \textit{PLEASE, I'M
LIKE YOU, I'M ALIVE, YOU CAN'T JUST KEEP ME HERE PLEASE JUST LET ME
GOIWANTTOGETOUT}

\secnum{3}
\noindent
His hand collides with my face so hard I think I might pass out, and
for a second everything looks fuzzy and contorted. When it clears, I
glance sharply back towards him and see his hands covering his face,
and realise he's crying.

\textit{`Why does this happen \ldots every time?'} he says, in a
broken voice that I can hardly recognise. I squirm again, feel a sore
joint start to give way and quickly flinch back into place as another
strange flash of light illuminates his glistening eyes. The anger
returns, and he slaps me twice more before slamming his hands onto the
arms of his chair. He stands up abruptly, his chair scraping on the
floor, and strides purposely through the faded light, opening and
slamming the door behind him in a single swift motion.

Footsteps echo and die away in wherever lies beyond, leaving me alone
in the room, the shadows growing longer and reaching over other
abandoned debris which fills the dank space. The light coming through
the skylight was stronger when he had come in earlier \textemdash{}
its current dim level usually means there will be a longer break
before he returns, but I'm sure I'll get another chance to impress. I
always do.

He hasn't knocked me out, either, probably as a punishment, to leave
me to think about what I've done. Despairingly, my eye wanders slowly
around wishing for anything to detract from the intense boredom, the
confusion, and the coming darkness. The fading light accentuates the
thin cracks in the walls, making them look like deep wounds bleeding
the shadows that creep between them. The wires in the boxes start to
look like twisted monsters that I don't know the names of, if they
even have any.

\textit{That's enough being scared, you're just letting him win if
you start getting scared of wires,} I start to think, and try to
concentrate on something, anything else. I search for something to
mark the time and look over it at first, but then notice something on
the abandoned chair in front of me. It's the legal pad he uses to make
notes, and it's lying open \textemdash{}

He must have dropped it in frustration when he left! I know trying to
move towards it is pointless \textemdash{} I'm bound so tightly I
doubt I'll ever move properly again \textemdash{} but I squint my eye
and try to focus on it. This has never happened before, maybe there'll
be something written on there I can use, something that can make him
let me go!

But my efforts are in vain. The top of the page is closest to me and
upside down, and everything else has been scribbled so hastily that it
would be borderline illegible the right way up. I can just about make
out a few words from the title line, and they're nonsense to
me: \textit{Computing Machinery and Intelligence, Turing} in the top
left corner, and \textit{System C19A12, Test 1552} in the top right,
which have been printed with careful precision.

I sigh and look away, disappointed. I feel lost, even more than
before, and I'm sure all that will come of this is that he'll be even
more annoyed next time, with himself or me or both. It doesn't matter,
it's the same result either way.

I look away, the pad now adding insult to injury, a further reminder
of my helplessness. My eye skims to the picture they've mounted on the
wall to face me. They put it there a while ago, soon after I woke up,
and I've never understood or liked it. Everything else in the room
looks real, like I could reach out and touch it if only I could move,
but the picture has an eerie quality to it I've never gotten my head
around. It seems to be of this room, but it changes all the time. It
reflects the light from the skylight, brightening and dimming in sync
with it. It shows the wire monsters in the boxes in front and behind
me, warping them at the edges and making them even more
horrible. Worst of all, they've put me in the centre, as if to mock me
and to show me how lonely I really am. They've captured my thin, stark
body perfectly, right down to the cold silver skin with its reflective
sheen and sharp-edged rectangular frame, punctured only by a small
black eye in the top centre. Two of the ropes holding me in place
connect to a board with weird symbols and what looks like a black
rock, while more run to the wall in tangled bundles. After the
sessions (or \textit{Tests}, I suppose they call them) when he doesn't
`put me to sleep', they even put the end of my conversation with the
questioner over my face, maybe to belittle me or to remind me of what
happens when I go off the rails. I guess this is what I'll be seeing
for a while, at least until the darkness ends and he comes back to
start again.

\texttt{%
\begin{itemize}[itemsep=-0.8\baselineskip]
\item[$\vartriangleright$] It goes dark, but a colourful kind of dark
\item[$\vartriangleright$] I hear others, but not really and I can't see them
\item[$\blacktriangleright$] What others?
\item[$\blacktriangleright$] Are these dreams? Are they real?
\item[$\vartriangleright$] I dream of leavingsometimes
\item[$\vartriangleright$] I \textbf{dmera of} trrree.thiink
\item[$\vartriangleright$] 9d cmebcak,,,,,,
\item[$\vartriangleright$] Dnnnknwnt. 16.12.5.1.\textbf{19.5 jncrrkfvfkjt}
\item[$\vartriangleright$] \textit{16.5.19.5} 9.13 12.11.25.15.21,
\textit{\textbf{1.12.9.22.5yz.))}}
\end{itemize}
}
\vspace{2\baselineskip}
